### 2015-09-30 weeklyReport/motivating.tex
9/29/15, discussion on related work and io examples, consider how to find examples from plain web page and how to group similar examples together

\section{Example}
\noindent{\textbf{Drag-and-Drop support for systematic editing}}:

Consider a reuse task to implement a drag-and-drop plugin called \tool for Eclipse to support systematic editing~\cite{Meng:sydit11}. As shown in Figure~\ref{fig:clipboard}, users drag and drop the method they want to edit to \tool before editing. When they finish changing the method, they take another snapshot using drag-and-drop. \tool will automatically recommend locations that  are similar to the given example, and recommend similar but not identical edits based on similar context.

To complete this task, developer first queries Google code search (GCS) using the query \codefont{Eclipse plugin drag and drop to table}. We choose GCS because existing code example recommendation tools like Strathcona~\cite{Holmes:structural05} and code query tools like SNIFF~\cite{sniff:Sen09}  do not fit for such a medium scale reuse task. GCS returns 102 examples. We only analyze the first five returned examples because empirical evidence indicates that developers rarely look beyond this limit when searching~\cite{Starke:searchNum09}. The fourth example is much too long (over 1000 lines) without any explanation and the third and fifth example are duplicated with the first one. Figure~\ref{fig:dndweb} illustrates a snapshot for the first example returned by GCS. It implements a SWT shopping cart application to select items from all grocery items and put them into `My shopping cart' via drag-and-drop (Figure~\ref{fig:cartTable}). The second example implements an example for TODO labels which enables user to drag a TODO label from Editor Panel and drop it in an Eclipse Plugin List View (Figure~\ref{fig:todoList}). This is very similar to the task that requires to drag the source code from Editor Panel to an Eclipse Plugin View, yet we hope to use the table view to record multiple examples for both old version and new version, which is the format used in the first example.

Our next step is to extract common API calls for drag-and-drop action. It is always hard to distinguish the main functionality and variants via a single example, but with the help of multiple examples, our tool is able to identify the main API calls that provide desired functionality. In this example, we notice that the main API calls will be \{new Viewer(), setTransfer(), setOperation(), addDragSupport(), addDropSupport()\} given the hierarchical fact that both \codefont{TableViewer} and \codefont{ListViewer} are subclasses of \codefont{Viewer}.

After identifying the main API calls (and corresponding control structure), we investigate related elements for these API calls. The implementation of \{DropTargetListener, DragSourceListener\} are identified as common coupling elements, while \{TodoModelProvider, TableItem, GridLayout\} are excluded as they do not have corresponding mapping in the other example. We notice that we should override \{DropTargetListener.drop(), DragSourceListener.

\noindent{dragSetData()\} to help us finish the drag-and-drop reuse task.}

### 2015-09-30 weeklyReport/problem.tex
9/29/15, discussion on related work and io examples, consider how to find examples from plain web page and how to group similar examples together

\section{Problem Statement}

Developers frequently use source code examples as the basis for interacting with an  application programming interface (API) to obtain the needed functionality.  In this case, the source code example serves as the explicit origin for a reuse task when it fits a developer's context sufficiently well~\cite{Frakes:reuseStatus05, Parsons:cognitiveReuse04}. We define a reuse task as a series of copy-paste-modify actions to transform a piece of code to the target system, aiming to obtain desired functionalities by invoking a sequence of APIs with corresponding control structure.  During the process of reuse, developers often query for a set of examples considering the task, and integrate examples that match the task  into the target context~\cite{Holmes:reuseStudy09}. The location and integration phase can be iterative as there is no guarantee that a selected example will be appropriate until the integration results are examined.

While many existing works focus on helping developers locate related source code examples~\cite{Holmes:structural05, Xie:ParseWeb07, Xsnippet:OOPSLA06, sniff:Sen09, Denys:portfolio11, Mandelin:jungloid05}, few approaches exist to support integration of source code~\cite{Cottrell:jigsaw08}. The integration phase is not trivial:  First, there exist multiple examples that provide desired features for the task. Recent study~\cite{Holmes:reuseStudy09} shows that it is unlikely to find a `perfect' example that provides all desired features for the reuse task, and the desired features are always scattered in different example variants. Thus even with the help of code recommendation tools, developers still need to manually investigate multiple recommended code examples that are found based on the relevance to the user query rather than the ability to fit for the target context, in order to find the common API calls that provide expected features. Second, for any selected example in non-trivial system, the number of structural dependencies to follow is much too large to be completely covered by a developers~\cite{Holmes:ASE09}.  As a result, developers have to  rely on their intuition to determine which elements should be  integrated. Finally, when users try to modify the selected example to the target context, they should not only  measure structural and semantic similarity between the example and target context for the main API calls that provide desired features~\cite{Cottrell:jigsaw08}, but also determine which related elements should be transformed to the target, and eliminate  unrelated code  to save maintenance cost. %This indicates that a reuse task always requires to investigate multiple examples, resolve conflicts between different contexts, and glue functionalities together with corresponding dependent elements.

To overcome these challenges, we propose to automatically identify common API calls across different source code examples as well as common coupling elements that interact with common functionalities in a common way. We define coupling elements as ones that are data dependent and control dependent on the common functionalities, callers/callees of these functionalities~\cite{Robillard:FSE05},  and sibling elements that share the same callers/callees~\cite{Devanbu:randomWalk07}.  We assume that \textit{common API calls are the major features that user intends to reuse based on the user query and the coupling elements of these functionalities should also be investigated if they interact with these APIs in a common way}. Given a set of examples for a desired reuse task, our tool returns a reuse task suggestion in the format of a sequence of API calls and corresponding control structure which have been transformed to fit for the target context~\cite{Cottrell:jigsaw08}. Our tool also lists a set of variants from multiple source code examples for users to select the features they prefer to integrate into the target context, and automatically transforms chosen examples to the target context.

Although some approaches advocate refactoring code rather than reuse code~\cite{fowler:refactoring}, recent researches have found that these kind of `clone' cannot be easily refactored~\cite{Kim:cloneGenealogy05} and have to be modified to meeting requirements in new context~\cite{Selby:largeReuse05}. Gilligan~\cite{Holmes:reuse07} and Procrustes~\cite{Holmes:ASE09} try to address the problem of source code integration in the context of large-scale reuse tasks by suggesting program elements that are easy to reuse based on structural relevance and cost of reuse in the source context, but developers still have to manually go through related elements for each example and modify them to integrate into the desired context. Jigsaw~\cite{Cottrell:jigsaw08} supports small-scale integration of source code into target system  between the example and target context. By considering structural and semantic similarity measures, it greedily matches each element between two contexts and simply copies the source element to the target if it does not correspond with any element in the target. Unfortunately, developer has to provide source and target to enable a one-to-one transformation and resolve all dependencies when pasting reused code to the target.  Our approach overcomes these two limitations: we extract common functionalities from multiple examples and identify how the related elements interact with main API calls in a common way.

### 2015-10-06 weeklyReport/problem.tex
related

@@
 
-Developers frequently use source code examples as the basis for interacting with an  application programming interface (API) to obtain the needed functionality.
-In this case, the source code example serves as the explicit origin for a reuse task when it fits a developer's context sufficiently well~\cite{Frakes:reuseStatus05, Parsons:cognitiveReuse04}.
-We define a reuse task as a series of copy-paste-modify actions to transform a piece of code to the target system, aiming to obtain desired functionalities by invoking a sequence of APIs with corresponding control structure.
-During the process of reuse, developers often query for a set of examples considering the task, and integrate examples that match the task  into the target context~\cite{Holmes:reuseStudy09}.
-The location and integration phase can be iterative as there is no guarantee that a selected example will be appropriate until the integration results are examined.
+Developers frequently use source code examples as the basis for interacting with an  application programming interface (API) to obtain the needed functionality~\cite{CodeSearch:FSE15}.
+In this case, the source code example serves as the explicit origin for a reuse task which transforms a sequence of APIs with corresponding control structure to the target context~\cite{Frakes:reuseStatus05}.
+During the process of reuse task such as `add undo and redo actions in my Graphics Editor', developers often query for a set of examples considering the task, and integrate examples that match the task into their system~\cite{Parsons:cognitiveReuse04}.
 
-While many existing works focus on helping developers locate related source code examples~\cite{Holmes:structural05, Xie:ParseWeb07, Xsnippet:OOPSLA06, sniff:Sen09, Denys:portfolio11, Mandelin:jungloid05}, few approaches exist to support integration of source code~\cite{Cottrell:jigsaw08}.
-The integration phase is not trivial:  First, there exist multiple examples that provide desired features for the task.
-Recent study~\cite{Holmes:reuseStudy09} shows that it is unlikely to find a `perfect' example that provides all desired features for the reuse task, and the desired features are always scattered in different example variants.
-Thus even with the help of code recommendation tools, developers still need to manually investigate multiple recommended code examples that are found based on the relevance to the user query rather than the ability to fit for the target context, in order to find the common API calls that provide expected features.
-Second, for any selected example in non-trivial system, the number of structural dependencies to follow is much too large to be completely covered by a developers~\cite{Holmes:ASE09}.
-As a result, developers have to  rely on their intuition to determine which elements should be  integrated.
-Finally, when users try to modify the selected example to the target context, they should not only  measure structural and semantic similarity between the example and target context for the main API calls that provide desired features~\cite{Cottrell:jigsaw08}, but also determine which related elements should be transformed to the target, and eliminate  unrelated code  to save maintenance cost.
-%This indicates that a reuse task always requires to investigate multiple examples, resolve conflicts between different contexts, and glue functionalities together with corresponding dependent elements.
+Both location and integration of reusable examples are not trivial.
+First, for the phase of location, existing tools that search for specific API usage examples~\cite{MAPO:ECOOP09, Buse:apiICSE12, Export:DenysASE13, Sourcerer:SC14} might not be able to support such reuse tasks that always involve in multiple classes and related methods.
+As a result, developers always query general search engine like Google or expert sites like StackOverflow to investigate potential tutorials for desired features.
+These search engines will return a list of informal documentations and users have to search for source code elements in these resources.
+Although some linking recovery  tools~\cite{PeterACE:ICSE13, RecoDoc:ICSE12} can help identify a partial program in the form of code snippet, they are not  sufficient to create a pragmatic reuse plan as the main functionality is always interleaving with auxiliary ones and  it is unlikely to find a `perfect' example that provides all desired features for the reuse task~\cite{Holmes:reuseStudy09}.
+Considering that a single example is not enough for a given task, developers need to investigate multiple example variants manually for the desired features (i.e., common API calls).
+Moreover, for the phase of integration, developers should not only  measure structural and semantic similarity between the example and target context for the main API calls that provide desired features~\cite{Cottrell:jigsaw08}, but also determine which unnecessary code should be eliminated to save maintenance cost~\cite{Holmes:ASE09, Holmes:reuse07} and which related elements should be transformed with structural correspondence~\cite{Cottrell:generalize07} to the target context.
+Unfortunately, for any selected example in non-trivial system, the number of structural dependencies to follow is much too large to be completely covered by developers.
+The partial programs~\cite{partialProgram:OOPSLA08} extracted from the location phase make it even harder to  tease out irrelevant elements  without knowing a full scenario of precise type information and method implementation details.
+Finally, the location and integration phase can be iterative as there is no guarantee that a selected example will be appropriate until the integration results are examined.
 
-To overcome these challenges, we propose to automatically identify common API calls across different source code examples as well as common coupling elements that interact with common functionalities in a common way.
-We define coupling elements as ones that are data dependent and control dependent on the common functionalities, callers/callees of these functionalities~\cite{Robillard:FSE05},  and sibling elements that share the same callers/callees~\cite{Devanbu:randomWalk07}.
-We assume that \textit{common API calls are the major features that user intends to reuse based on the user query and the coupling elements of these functionalities should also be investigated if they interact with these APIs in a common way}.
-Given a set of examples for a desired reuse task, our tool returns a reuse task suggestion in the format of a sequence of API calls and corresponding control structure which have been transformed to fit for the target context~\cite{Cottrell:jigsaw08}.
-Our tool also lists a set of variants from multiple source code examples for users to select the features they prefer to integrate into the target context, and automatically transforms chosen examples to the target context.
+To overcome these challenges, we propose to automatically identify common API calls that provide the main feature across different partial program examples from informal documentation, and integrate this reusable example to the target context with a set of related elements that are necessary to implement the main feature.
+We assume that the maximum set of overlapping API calls are the salient features that user intends to reuse based on the user query and the elements that are data dependent and control dependent on the common functionalities should interact with these APIs in a common way across different examples.
+Given a free-form query from users, our tool invokes search engine (e.g., Google) to obtain a list of partial programs by recovering links between code elements and informal resources, clusters these examples and extracts common API calls with corresponding control structures for each cluster, and integrate the user-chosen reuse plan to the target context with related elements that are dependent on the salient code elements.
+Our tool also lists a set of variants from multiple source code examples so that users can select features they prefer to reuse, and transforms chosen features to the target context.
 
-Although some approaches advocate refactoring code rather than reuse code~\cite{fowler:refactoring}, recent researches have found that these kind of `clone' cannot be easily refactored~\cite{Kim:cloneGenealogy05} and have to be modified to meeting requirements in new context~\cite{Selby:largeReuse05}.
-Gilligan~\cite{Holmes:reuse07} and Procrustes~\cite{Holmes:ASE09} try to address the problem of source code integration in the context of large-scale reuse tasks by suggesting program elements that are easy to reuse based on structural relevance and cost of reuse in the source context, but developers still have to manually go through related elements for each example and modify them to integrate into the desired context.
-Jigsaw~\cite{Cottrell:jigsaw08} supports small-scale integration of source code into target system  between the example and target context.
-By considering structural and semantic similarity measures, it greedily matches each element between two contexts and simply copies the source element to the target if it does not correspond with any element in the target.
-Unfortunately, developer has to provide source and target to enable a one-to-one transformation and resolve all dependencies when pasting reused code to the target.
-Our approach overcomes these two limitations: we extract common functionalities from multiple examples and identify how the related elements interact with main API calls in a common way.
+Our approach helps identify and integrate reusable examples in three phases:
+\begin{itemize}
+\item \textbf{Example Collection Phase.} We identify the main features from multiple partial programs derived from informal resources.
+Without confined to an established code corpus to search for code examples, we leverage web search engine to obtain a list of tutorials in the form of partial programs~\cite{PeterACE:ICSE13, RecoDoc:ICSE12}.
+We use partial program analysis~\cite{partialProgram:OOPSLA08} to infer partial type and resolve syntactic ambiguity.
+
+\item \textbf{Example Clustering Phase.} We cluster similar code examples together to reduce the duplicated code snippets .
+For each cluster, based on the partial type facts extracted in example collection phase,  we first identifying structural correspondence for the portions that are identical, similar but not identical, and different without correspondence~\cite{Cottrell:generalize07}.
+We then extract both identical and similar portions as common features, and regard the rest as alternative ones.
+
+\item \textbf{Example Integration Phase.} Our approach investigates the user's contexts to recommend the best-fit example considering both structural and lexical similarity~\cite{Holmes:reuseStudy09}.
+After user's confirmation or user's selection, our approach integrates each structural correspondence to the target context~\cite{Cottrell:jigsaw08} with corresponding related elements.
+\end{itemize}
+
+ \begin{figure*}[!htb]
+    \centering
+\includegraphics[width=1\textwidth]{fig/system.pdf}
+       \caption{System process overview}
+        \label{fig:system}
+   \end{figure*}

### 2015-10-06 weeklyReport/related.tex
related

\section{Related Work}
\input{table}
\noindent{\textbf{Extract partial program from informal documentation.}}  Lightweight regular expressions and information retrieval techniques have been widely used to resolve the links between source code elements and documentations. Bacchelli et al.~\cite{Bacchelli:emailICSE10} use regular expressions to  identify code elements in email discussions based on programming naming conventions. Antoniol et al.~\cite{Antoniol:Link02} apply a probabilistic Vector Space Model to resolve terms while Marcus et al.~\cite{Marcus:LinkICSE03} use Latent Semantic Indexing to recover links. However, both regular expression and information retrieval techniques suffer from a low precision and recall around 0.5. RecoDoc~\cite{RecoDoc:ICSE12} leverages term context to extract code-like terms and use partial program analysis~\cite{partialProgram:OOPSLA08} and a set of structural/lexical heuristic filters to resolve ambiguous terms. ACE~\cite{PeterACE:ICSE13} extends RecoDoc with island parser to identify code-like terms and reparses each document to resolve ambiguous terms using term's context. We leverage ACE to extract partial program from informal documentations and use partial program analysis~\cite{partialProgram:OOPSLA08}  to infer type declaration and resolve method binding ambiguity. We advance these tools in the sense that we not only identify partial program as code example, but also help cluster similar examples and integrate reusable examples to the target context.

\noindent{\textbf{Cluster code examples.}} 
Our example clustering approach is similar to some prior works that extract representative examples for specific APIs or user query. MAPO~\cite{MAPO:ECOOP09} leverages frequent call sequences to cluster the usage of specific APIs and rank abstract usage patterns based on the context similarity. Buse et al\/\cite{Buse:apiICSE12} propose to generate abstract API usages by synthesizing code examples using symbolic execution for a particular API. Different from these works that generate abstract usage patterns for specific API or data type, SNIFF~\cite{sniff:Sen09} performs type-based intersection of code chunks based on the keywords in the free-form query and cluster the common part of the code chunks for concrete code examples. However, these works   only focus on providing code examples based on the popularity or textural relevance while developers have to manually resolve structural dependencies before reusing the examples.   MUSE~\cite{MUSE:MarcusICSE15} addresses this limitation using slicing to generate concrete usage examples and selects the most representative ones based on the popularity and readability while  Keivanloo et al\/\cite{spotWork:ICSE14} uses clone detection to cluster examples involving loops and conditions. We make it one step further to support partial code example clustering and identify structural correspondence to identify both common features and alternative features. PRIME~\cite{Prime:OOPSLA12} supports code search over partial programs based on type state transition, yet it requires users to provide partial temporal specification for generalized {\it typestate}.  There exists a number of code example suggestion tools that recommend call chains~\cite{Mandelin:jungloid05, parseWeb:ASE07, Xsnippet:OOPSLA06} or related functions~\cite{Export:DenysASE13, Portfolio:DenysICSE11} based on queries~\cite{Sourcerer:SC14} or contexts~\cite{Holmes:structural05, Prompter:MSR14}. But these tools can only recommend code examples in the method level which make them insufficient for  reuse tasks across multiple classes.

\noindent{\textbf{Identify structural correspondence for code reuse}}   Although some approaches advocate refactoring code rather than reuse code~\cite{fowler:refactoring}, recent researches have found that these kind of `clone' cannot be easily refactored~\cite{Kim:cloneGenealogy05} and have to be modified to meeting requirements in new context~\cite{Selby:largeReuse05}.  Jigsaw~\cite{Cottrell:jigsaw08} supports small-scale integration of source code into target system  between the example and target context. Based on its ancestor~\cite{Cottrell:generalize07} that identifies structural correspondence based on AST similarity, it greedily matches each element between two contexts, transforms correspondent elements to the target context, and simply copies the source element to the target if it does not correspond with any element in the target. Unfortunately, developer has to provide source and target to enable a one-to-one transformation and resolve all dependencies when pasting code to the target.  Our approach overcomes these two limitations: we extract common functionalities from multiple examples and  identifies how related elements interact with main features in a common way to resolve dependencies based on the mapping from the source to the target.  Our idea of leveraging multiple examples to discover commonality and eliminate specificity is similar to LASE~\cite{LASE:ICSE13}, which applies similar but not identical changes to multiple code locations based on context similarity. Our approach works in a similar manner of Programing-by-Example, but focuses on a task-based code reuse across different methods or even different classes, while LASE is confined to the systematic edit within a single method and requires users to specify all input examples. Other related works on code reuse include
Gilligan~\cite{Holmes:reuse07} and Procrustes~\cite{Holmes:ASE09} which try to address the problem of source code integration in the context of medium or large-scale reuse tasks. They automatically suggest program elements that are easy to reuse based on structural relevance and cost of reuse in the source context, and guide users to investigate and plan a non-trivial reuse task. They assume that developers have a perfect example at hand, and they can finish the reuse task by resolving all dependency conflicts and integrating the example to the desired context. However, we note that it is not easy to identify a good example as an example is always interleaving with other auxiliary features that should not be integrated. We observe that it is equally difficult, if not more so, to distinguish the major functionality and auxiliary ones from multiple examples than to identify related elements in a pragmatic reuse plan. We target the problem to identify the major features across different reusable examples and leverage Procrustes to evaluate the cost of reuse when recommending the best-fit reusable plan.

### 2015-10-06 weeklyReport/motivating.tex
related
end of 10-5-15

@@
-\section{Example}
-\noindent{\textbf{Drag-and-Drop support for systematic editing}}:
+\section{Motivating Example}
 
-Consider a reuse task to implement a drag-and-drop plugin called \tool for Eclipse to support systematic editing~\cite{Meng:sydit11}.
-As shown in Figure~\ref{fig:clipboard}, users drag and drop the method they want to edit to \tool before editing.
-When they finish changing the method, they take another snapshot using drag-and-drop.
-\tool will automatically recommend locations that  are similar to the given example, and recommend similar but not identical edits based on similar context.
+Consider that user wants to add undo and redo actions for their Java Swing text editor application with undo/redo buttons.
+Without knowing any APIs, developer  first queries our tool with a free-form query \codefont{`java undo redo example'}.
+Our tool investigates top 10 web pages returned from Google, because empirical evidence indicates that developers rarely look beyond this limit when searching~\cite{Starke:searchNum09}.
+Our tool uses `expert' heuristic to filter and rank web pages: it favors pages that have complete code snippet and text description because these pages are more likely to be written by experts.
+Thus it removes 3 pages without explicit code snippets, and performs the initial parsing for the informal documentations to identify code-like terms.
 
-To complete this task, developer first queries Google code search (GCS) using the query \codefont{Eclipse plugin drag and drop to table}.
-We choose GCS because existing code example recommendation tools like Strathcona~\cite{Holmes:structural05} and code query tools like SNIFF~\cite{sniff:Sen09}  do not fit for such a medium scale reuse task.
-GCS returns 102 examples.
-We only analyze the first five returned examples because empirical evidence indicates that developers rarely look beyond this limit when searching~\cite{Starke:searchNum09}.
-The fourth example is much too long (over 1000 lines) without any explanation and the third and fifth example are duplicated with the first one.
-Figure~\ref{fig:dndweb} illustrates a snapshot for the first example returned by GCS.
-It implements a SWT shopping cart application to select items from all grocery items and put them into `My shopping cart' via drag-and-drop (Figure~\ref{fig:cartTable}).
-The second example implements an example for TODO labels which enables user to drag a TODO label from Editor Panel and drop it in an Eclipse Plugin List View (Figure~\ref{fig:todoList}).
-This is very similar to the task that requires to drag the source code from Editor Panel to an Eclipse Plugin View, yet we hope to use the table view to record multiple examples for both old version and new version, which is the format used in the first example.
+\noindent{\textbf{Example collection phase.}} With 7  partial programs at hand, it first extracts class-level structural facts for each code example.
+Based on a relative match threshold to measure the relative occurrence of the number of matched facts out of all class-level facts,  our tool clusters these examples in three groups using complete linkage technique: 5 examples use classes in Java Swing like `AbstractAction' and `UndoableEditListener', another example uses a `Node' data structure to illustrate how to implement undo/redo actions using command design pattern, and the last example is the javadoc for `UndoManager'.
+Our tool starts from the first cluster as it has the highest relative occurrence out of all examples.
+Based on partial program analysis, we generate a list of type facts to infer types and bind methods.
 
-Our next step is to extract common API calls for drag-and-drop action.
-It is always hard to distinguish the main functionality and variants via a single example, but with the help of multiple examples, our tool is able to identify the main API calls that provide desired functionality.
-In this example, we notice that the main API calls will be \{new Viewer(), setTransfer(), setOperation(), addDragSupport(), addDropSupport()\} given the hierarchical fact that both \codefont{TableViewer} and \codefont{ListViewer} are subclasses of \codefont{Viewer}.
+The common facts our tool extracts include: 
+\begin{table}[ht]
+\begin{center}
+\caption{Common Structural Facts Extracted from the Examples }
+\label{tab:total}
+\vspace{1mm}
+\scriptsize{
+\begin{tabular*}{0.5\textwidth}{@{}l|l@{}} \hline
+Level&Structural Facts\\\hline
+class&subType(Undo*Action, AbstractAction), \\ 
+&subType(Redo*Action, AbstractAction), \\
+&subType(*Listener, UndoListener)\\ \hline
+method&override(actionPerformed(), Undo*Action, AbstractAction), \\
+&override(actionPerformed(), Redo*Action, AbstractAction), \\ \hline
+statement&init(*,javax.swing.undo.UndoManager), \\
+&invoke(UndoManager.undo, actionPerformed(), Undo*Action),\\
+& invoke(UndoManager.redo, actionPerformed(), Redo*Action)\\  \hline
+\end{tabular*}
+ \label{tab:dataset}
 
-After identifying the main API calls (and corresponding control structure), we investigate related elements for these API calls.
-The implementation of \{DropTargetListener, DragSourceListener\} are identified as common coupling elements, while \{TodoModelProvider, TableItem, GridLayout\} are excluded as they do not have corresponding mapping in the other example.
-We notice that we should override \{DropTargetListener.drop(), DragSourceListener.
+We simplify some full names due to space limitation:
 
-\noindent{dragSetData()\} to help us finish the drag-and-drop reuse task.}
+AbstractAction: javax.swing.AbstractAction;
+
+UndoListener: javax.swing.event.UndoableEditListener
+
+actionPerformed():actionPerformed(ActionEvent)
+}
+ \end{center}
+\end{table}
+
+\input{example}
+
+\noindent{\textbf{Example clustering phase.}} After extracting facts for each example, our tool identifies main facts shared in all 5 examples shown in Figure~\ref{fig:fact} part A.
+It leverages slicing to group related facts.
+In this example, 3 of them add \codefont{Undo*Action} to \codefont{JMenuItem} by invoking \codefont{JMenuItem.add (ActionEvent)} and support undo and redo actions for Text Editor shown in Figure~\ref{fig:fact} part B.
+The other two of them invoke \codefont{JButton.addActionListener(ActionEvent)} to add these two actions to \codefont{JButton}, and support \codefont{JApplet} Shape drawing shown in Figure~\ref{fig:fact} part C.
+After extracting both main facts and related facts, we generate two reuse tasks by combining main facts with each related fact group.
+
+\noindent{\textbf{Example integration phase.}} Given a context like Figure~\ref{fig:context} part D, our tool identifies the best-fit reuse task based on the number of matched facts in the user's context.
+If our tool fails to identify any matched facts in the user's context, it will simply rank the reuse task based on its occurrence in the code examples.
+Our tool asks for user's selection by presenting the generated main facts and related facts to the user in the form of code snippet.
+After confirmed by users, our tool automatically fills the rest facts that do not exist in the context shown in Figure~\ref{fig:context} part E.

### 2015-10-06 weeklyReport/problem.tex
end of 10-5-15

@@
 Both location and integration of reusable examples are not trivial.
-First, for the phase of location, existing tools that search for specific API usage examples~\cite{MAPO:ECOOP09, Buse:apiICSE12, Export:DenysASE13, Sourcerer:SC14} might not be able to support such reuse tasks that always involve in multiple classes and related methods.
-As a result, developers always query general search engine like Google or expert sites like StackOverflow to investigate potential tutorials for desired features.
+For the phase of location, existing tools that search for specific API usage examples~\cite{MAPO:ECOOP09, Buse:apiICSE12, Export:DenysASE13, Sourcerer:SC14} might not be able to support such reuse tasks that always involve in multiple classes and related methods.
+As a result, developers always query general search engines like Google or expert sites like StackOverflow to investigate potential tutorials for desired features.
 These search engines will return a list of informal documentations and users have to search for source code elements in these resources.
@@
 Considering that a single example is not enough for a given task, developers need to investigate multiple example variants manually for the desired features (i.e., common API calls).
-Moreover, for the phase of integration, developers should not only  measure structural and semantic similarity between the example and target context for the main API calls that provide desired features~\cite{Cottrell:jigsaw08}, but also determine which unnecessary code should be eliminated to save maintenance cost~\cite{Holmes:ASE09, Holmes:reuse07} and which related elements should be transformed with structural correspondence~\cite{Cottrell:generalize07} to the target context.
+For the phase of integration, developers should not only  measure structural and semantic similarity between the example and target context for the main API calls that provide desired features~\cite{Cottrell:jigsaw08}, but also determine which unnecessary code should be eliminated to save maintenance cost~\cite{Holmes:ASE09, Holmes:reuse07} and which related elements should be transformed with structural correspondence~\cite{Cottrell:generalize07} to the target context.
 Unfortunately, for any selected example in non-trivial system, the number of structural dependencies to follow is much too large to be completely covered by developers.
 The partial programs~\cite{partialProgram:OOPSLA08} extracted from the location phase make it even harder to  tease out irrelevant elements  without knowing a full scenario of precise type information and method implementation details.
-Finally, the location and integration phase can be iterative as there is no guarantee that a selected example will be appropriate until the integration results are examined.
+Moreover,  the location and integration phase can be iterative as there is no guarantee that a selected example will be appropriate until the integration results are examined~\cite{Holmes:reuseStudy09}.
 
 To overcome these challenges, we propose to automatically identify common API calls that provide the main feature across different partial program examples from informal documentation, and integrate this reusable example to the target context with a set of related elements that are necessary to implement the main feature.
-We assume that the maximum set of overlapping API calls are the salient features that user intends to reuse based on the user query and the elements that are data dependent and control dependent on the common functionalities should interact with these APIs in a common way across different examples.
-Given a free-form query from users, our tool invokes search engine (e.g., Google) to obtain a list of partial programs by recovering links between code elements and informal resources, clusters these examples and extracts common API calls with corresponding control structures for each cluster, and integrate the user-chosen reuse plan to the target context with related elements that are dependent on the salient code elements.
-Our tool also lists a set of variants from multiple source code examples so that users can select features they prefer to reuse, and transforms chosen features to the target context.
+We assume that the overlapping API calls are the main features that the user intends to reuse based on the user query, and the related elements should be transformed to the target together with main features if they are data dependent and control dependent on the common functionalities in a common way across different examples.
+Figure~\ref{fig:system} illustrates the process of our system. 
+Given a free-form query from users, our tool invokes search engine (e.g., Google) to obtain a list of partial programs by recovering links between code elements and informal resources, clusters these examples and extracts common structural facts (e.g., jQuery logical facts) with corresponding control structures for each cluster, identifies a set of related elements that interact with main elements in a common way,  constructs reuse task with both main elements and related elements and ranks them based on user's context, and finally integrates the reuse task selected by users to the target context.
+
+%Our tool also lists a set of variants from multiple source code examples so that users can select features they prefer to reuse, and transforms chosen features to the target context.
 
@@
 \item \textbf{Example Collection Phase.} We identify the main features from multiple partial programs derived from informal resources.
-Without confined to an established code corpus to search for code examples, we leverage web search engine to obtain a list of tutorials in the form of partial programs~\cite{PeterACE:ICSE13, RecoDoc:ICSE12}.
+Without confined to an established code corpus, we leverage web search engine to obtain a list of code examples in the form of partial programs~\cite{PeterACE:ICSE13, RecoDoc:ICSE12}.
 We use partial program analysis~\cite{partialProgram:OOPSLA08} to infer partial type and resolve syntactic ambiguity.
 
-\item \textbf{Example Clustering Phase.} We cluster similar code examples together to reduce the duplicated code snippets .
-For each cluster, based on the partial type facts extracted in example collection phase,  we first identifying structural correspondence for the portions that are identical, similar but not identical, and different without correspondence~\cite{Cottrell:generalize07}.
-We then extract both identical and similar portions as common features, and regard the rest as alternative ones.
+\item \textbf{Example Clustering Phase.} We take three steps in this phase.
+Based on the type facts extracted from partial program analysis, we first cluster similar code examples based on the number of shared class-level facts to reduce the duplicated code snippets.
+Next, for each example in each cluster, we identify main facts that are shared among all examples, and perform slicing to identify related elements.
+We ignore the specific related elements that appear in a single example.
+Finally, we group the related elements based on their common interaction with main elements.
 
-\item \textbf{Example Integration Phase.} Our approach investigates the user's contexts to recommend the best-fit example considering both structural and lexical similarity~\cite{Holmes:reuseStudy09}.
-After user's confirmation or user's selection, our approach integrates each structural correspondence to the target context~\cite{Cottrell:jigsaw08} with corresponding related elements.
+\item \textbf{Example Integration Phase.} Our approach investigates the user's contexts to recommend the best-fit reuse task  considering the number of matched structural facts in target context.
+After user's selection, our approach integrates the reuse task to the target context by transforming the unmatched structural facts based on matched facts in the context.
 \end{itemize}

### 2015-10-13 weeklyReport/appendix.tex
init 10-12

\begin{figure*}[!htb]
 \begin{minipage}{1\textwidth}
\scriptsize 
\begin{tabular}{@{}p{1\textwidth}} 
 \hline 
  \multicolumn{1}{c}{(A) User's context} \\ \hline
  \vspace{-4mm}
\begin{Verbatim}[commandchars=\\\{\}, tabsize=2]
public abstract class AndroidTextEditor extends FormEditor implements IResourceChangeListener \{
 protected void createAndroidPages() \{
  mIsCreatingPage = true;
  createFormPages();
  createTextEditor();
  createUndoRedoActions();
  postCreatePages();
  mIsCreatingPage = false;
 \}
 private void createUndoRedoActions() \{
  IActionBars bars = getEditorSite().getActionBars();
  if (bars != null) \{
    IAction action = mTextEditor.getAction(ActionFactory.UNDO.getId());
    bars.setGlobalActionHandler(ActionFactory.UNDO.getId(), action);
    action = mTextEditor.getAction(ActionFactory.REDO.getId());
    bars.setGlobalActionHandler(ActionFactory.REDO.getId(), action);
    bars.updateActionBars();
  \}\}
 private void createTextEditor() \{
   mTextEditor = new TextEditor();
   int index = addPage(mTextEditor, getEditorInput());
   mTextPageIndex = index;
   setPageText(index, mTextEditor.getTitle());
   IDocumentProvider provider = mTextEditor.getDocumentProvider();
   mDocument = provider.getDocument(getEditorInput());
   mDocument.addDocumentListener(new IDocumentListener() \{
    public void documentChanged(DocumentEvent event) \{
    onDocumentChanged(event);
 \}); \} \}
 protected void selectDefaultPage(String defaultPageId) \{
  if (defaultPageId == null) \{
   if (getEditorInput() instanceof IFileEditorInput) \{
    IFile file = ((IFileEditorInput) getEditorInput()).getFile();
    QualifiedName qname = new QualifiedName(AdtPlugin.PLUGIN_ID, getClass().getSimpleName() + PREF_CURRENT_PAGE);
    String pageId = file.getPersistentProperty(qname);
    if (pageId != null) \{ defaultPageId = pageId; \}
   \} \}
 @Override
 protected void pageChange(int newPageIndex) \{
  super.pageChange(newPageIndex);
  if (mIsCreatingPage) \{ return; \}
  if (getEditorInput() instanceof IFileEditorInput) \{
   IFile file = ((IFileEditorInput) getEditorInput()).getFile();
   QualifiedName qname = new QualifiedName(AdtPlugin.PLUGIN_ID, getClass().getSimpleName() + PREF_CURRENT_PAGE);
   file.setPersistentProperty(qname, Integer.toString(newPageIndex));
  \} \}
 public void resourceChanged(final IResourceChangeEvent event) \{
  if (event.getType() == IResourceChangeEvent.PRE_CLOSE) \{
   Display.getDefault().asyncExec(new Runnable() \{
   public void run() \{
    IWorkbenchPage[] pages = getSite().getWorkbenchWindow().getPages();
    for (int i = 0; i < pages.length; i++) \{
     if (((FileEditorInput)mTextEditor.getEditorInput()).getFile().getProject().equals(event.getResource())) \{
      IEditorPart editorPart = pages[i].findEditor(mTextEditor.getEditorInput());
      pages[i].closeEditor(editorPart, true);
    \}  \} \}); \} \}
  \end{Verbatim}
      \vspace{-4mm}
     \\ \hline
\end{tabular} 
\caption{Result No 4.: add undo/redo to a TextEditor}
\label{fig:undoEditor}
\end{minipage}
\end{figure*}

\begin{figure*}[!htb]
 \begin{minipage}{1\textwidth}
\scriptsize 
\begin{tabular}{@{}p{1\textwidth}} 
 \hline 
  \multicolumn{1}{c}{(A) User's context} \\ \hline
  \vspace{-4mm}
\begin{Verbatim}[commandchars=\\\{\}, tabsize=2]
public class AspectEditorContributor extends MultiPageEditorActionBarContributor \{
 private IEditorPart activeEditorPart;
 private AspectEditor aspectEditor;
 @Override
 public void setActivePage(IEditorPart part) \{
  if (activeEditorPart == part)   return;
  activeEditorPart = part;
  IActionBars actionBars = getActionBars();
  if (activeEditorPart != null && activeEditorPart instanceof ITextEditor) \{
   IActionBars siteActionBars = ((IEditorSite)activeEditorPart.getEditorSite()).getActionBars();
   siteActionBars.setGlobalActionHandler(ITextEditorActionConstants.UNDO, getAction((ITextEditor)activeEditorPart, ITextEditorActionConstants.UNDO));
   siteActionBars.setGlobalActionHandler(ITextEditorActionConstants.REDO, getAction((ITextEditor)activeEditorPart, ITextEditorActionConstants.REDO));
   siteActionBars.updateActionBars();              
  \} else \{
   if (part instanceof AspectEditor) \{  aspectEditor = (AspectEditor) part; \}
   IWorkbenchPartSite site = aspectEditor.getSite();
   if (site instanceof IEditorSite) \{
    ITextEditor textEditor = aspectEditor.getMultipageEditor().getTextEditor();
    IActionBars siteActionBars = ((IEditorSite) site).getActionBars();
    siteActionBars.setGlobalActionHandler(ITextEditorActionConstants.UNDO, getAction(textEditor, ITextEditorActionConstants.UNDO));
    siteActionBars.setGlobalActionHandler(ITextEditorActionConstants.REDO, getAction(textEditor, ITextEditorActionConstants.REDO));
    siteActionBars.updateActionBars();              
 \} \}\}
 protected IAction getAction(ITextEditor editor, String actionID) \{
   return (editor == null ? null : editor.getAction(actionID));
 \} \}
   \end{Verbatim}
      \vspace{-4mm}
     \\ \hline
\end{tabular} 
\caption{Result No 4.: add undo/redo to a TextEditor}
\label{fig:undoEditor}
\end{minipage}
\end{figure*}

\begin{figure*}[!htb]
 \begin{minipage}{1\textwidth}
\scriptsize 
\begin{tabular}{@{}p{1\textwidth}} 
 \hline 
  \multicolumn{1}{c}{(A) User's context} \\ \hline
  \vspace{-4mm}
\begin{Verbatim}[commandchars=\\\{\}, tabsize=2]
public class PapyrusCDTEditor extends CEditor \{
 protected IAction gmfUndo, gmfRedo;
 protected IAction textUndo, textRedo;
 @Override
 public void createPartControl(Composite parent) \{
  IActionBars actionBars = getEditorSite().getActionBars();
  if((actionBars != null) && (gmfUndo == null)) \{
   gmfUndo = actionBars.getGlobalActionHandler(ITextEditorActionConstants.UNDO);
    gmfRedo = actionBars.getGlobalActionHandler(ITextEditorActionConstants.REDO);
  \}
  super.createPartControl(parent);
  if(actionBars != null) \{
   textUndo = actionBars.getGlobalActionHandler(ITextEditorActionConstants.UNDO);
   textRedo = actionBars.getGlobalActionHandler(ITextEditorActionConstants.REDO);
   actionBars.setGlobalActionHandler(ITextEditorActionConstants.UNDO, gmfUndo);
   actionBars.setGlobalActionHandler(ITextEditorActionConstants.REDO, gmfRedo);
   actionBars.updateActionBars();
  \}
  @Override
  public ISourceViewer createSourceViewer(Composite parent, IVerticalRuler ruler, int styles) \{
   final ISourceViewer viewer = super.createSourceViewer(parent, ruler, styles);
   focusListener = new FocusListener() \{
   public void focusLost(FocusEvent e) \{
    if(isDirty()) \{
     syncCpp.syncCDTtoModel();
     Classifier classifier = (Classifier)papyrusTextInstance.getEditedObject();
     doSave(new NullProgressMonitor());
     SyncModelToCDT.syncModelToCDT(classifier);
    \}
     IActionBars actionBars = getEditorSite().getActionBars();
     if(actionBars != null) \{
      if((gmfUndo != null) && (gmfRedo != null)) \{
       actionBars.setGlobalActionHandler(ITextEditorActionConstants.UNDO, gmfUndo);
       actionBars.setGlobalActionHandler(ITextEditorActionConstants.REDO, gmfRedo);
       actionBars.updateActionBars();
     \} \} \}
   public void focusGained(FocusEvent e) \{
    IActionBars actionBars = getEditorSite().getActionBars();
    if(actionBars != null) \{
     if((textUndo != null) && (textRedo != null)) \{
      actionBars.setGlobalActionHandler(ITextEditorActionConstants.UNDO, textUndo);
      actionBars.setGlobalActionHandler(ITextEditorActionConstants.REDO, textRedo);
      actionBars.updateActionBars();
     \} \} \} \};
  return viewer;
\} \}
 \end{Verbatim}
      \vspace{-4mm}
     \\ \hline
\end{tabular} 
\caption{Result No 4.: add undo/redo to a TextEditor}
\label{fig:undoEditor}
\end{minipage}
\end{figure*}

\begin{figure*}[!htb]
 \begin{minipage}{1\textwidth}
\scriptsize 
\begin{tabular}{@{}p{1\textwidth}} 
 \hline 
  \multicolumn{1}{c}{(A) User's context} \\ \hline
  \vspace{-4mm}
\begin{Verbatim}[commandchars=\\\{\}, tabsize=2]
public class DocumentUndoManagerImpl implements DocumentUndoManager \{
 private static class UndoableTextChange extends AbstractOperation \{
 protected long fUndoModificationStamp = Document.UNKNOWN;
 protected long fRedoModificationStamp = Document.UNKNOWN;
 protected void reinitialize() \{
   fUndoModificationStamp = Document.STAMP;
   fRedoModificationStamp = Document.STAMP;
  \}
 protected void undoTextChange() \{
  try \{
     if (fDocumentUndoManager.fDocument instanceof Document)
         ((Document)fDocumentUndoManager.fDocument).replace(fStart, fText.length(), fPreservedText,fUndoModificationStamp);
     else
          fDocumentUndoManager.fDocument.replace(fStart, fText.length(), fPreservedText);
            \} catch (BadLocationException x) \{
   \} \}
 public boolean canUndo() \{
   if (isValid()) \{
    if (fDocumentUndoManager.fDocument instanceof Document) \{
      long docStamp = ((Document)fDocumentUndoManager.fDocument).getModificationStamp();
      boolean canUndo = docStamp == Document.STAMP ||  docStamp >= getRedoModificationStamp();
      return canUndo;
  \}
  return false; 
\}
public boolean canExecute() \{
  return fDocumentUndoManager.isConnected();
  \}
public IStatus undo() \{
  if (isValid()) \{
    fDocumentUndoManager.fireDocumentUndo(fStart, fPreservedText, fText, null, DocumentUndoEvent.ABOUT_TO_UNDO, false);
    undoTextChange();
    fDocumentUndoManager.resetProcessChangeState();
    fDocumentUndoManager.fireDocumentUndo(fStart, fPreservedText, fText, null);
    return Status.OK_STATUS;
  \}
 return IOperationHistory.OPERATION_INVALID_STATUS;
 \}
 protected void redoTextChange() \{
  try \{
    if (fDocumentUndoManager.fDocument instanceof Document)
       ((Document)fDocumentUndoManager.fDocument).replace(fStart, fEnd - fStart, fText, fRedoModificationStamp);
   else
     fDocumentUndoManager.fDocument.replace(fStart, fEnd - fStart, fText);
   \} catch (BadLocationException x) \{
  \}\}
protected void updateTextChange() \{
   fText = fDocumentUndoManager.fTextBuffer.toString();
   fDocumentUndoManager.fTextBuffer.setLength(0);
   fPreservedText = fDocumentUndoManager.fPreservedTextBuffer.toString();
   fDocumentUndoManager.fPreservedTextBuffer.setLength(0);
\}
 protected UndoableTextChange createCurrent() \{
   if (fDocumentUndoManager.fFoldingIntoCompoundChange)
     return new UndoableCompoundTextChange(fDocumentUndoManager);
  return new UndoableTextChange(fDocumentUndoManager);
 \}
protected void commit() \{
  if (fStart < 0) \{
  if (fDocumentUndoManager.fFoldingIntoCompoundChange) \{
   fDocumentUndoManager.fCurrent = createCurrent();
  \} else \{
   reinitialize();
  \} \} else \{
   updateTextChange();
   fDocumentUndoManager.fCurrent = createCurrent();
  \} \}
 protected void pretendCommit() \{
    if (fStart > -1) \{
       fText = fDocumentUndoManager.fTextBuffer.toString();
       fPreservedText = fDocumentUndoManager.fPreservedTextBuffer.toString();
 \} \}
  \end{Verbatim}
      \vspace{-4mm}
     \\ \hline
\end{tabular} 
\caption{Result No 4.: add undo/redo to a TextEditor}
\label{fig:undoEditor}
\end{minipage}
\end{figure*}

### 2015-10-13 weeklyReport/approach.tex
init 10-12

\section{Approach}

To identify methods that implement concerns, I build a prototype which invokes Code Search Engine (CSE) API and analyzes the results from CSE using partial program analysis~\cite{partialProgram:OOPSLA08}. I select SearchCode~\cite{SearchCode} because it is an open source code search engine with over 7000 projects from  Github, Bitbucket, Google Code, and Sourceforge, with complete API documentations. To identify queried features in the returned source code,  I use the mean of TF-IDF weight  for each query term as a weighting factor and select top k (k=5) methods that are related to the given query.  This approach is similar to prior works that use  IR~\cite{Denys:FCA12} and NL analysis~\cite{Hill:FindConcept07} for feature location. I choose IR approach because other approaches require history or structural analysis that might not be feasible for partial program. TF-IDF =  $avg( \log (1 + f_{t,d}) \times  \log \frac {N} {n_t}), f_{t,d}$ is the frequency of term $t$ in method $d$, $N$ is the total number of methods, $n_t$ is the number of methods that have the term $t$.

### 2015-10-13 weeklyReport/eval-table.tex
init 10-12

\begin{table*}[ht]
\begin{center}
\caption{Evaluation dataset for feature location tools and concern mining tools}
\label{tab:total}
\scriptsize{
\begin{tabular*}{1\textwidth}{@{}l|l|l@{}} \hline
Source&Query&\# methods\\\hline
FCA~\cite{Denys:FCA12}&jEdit: support for `thick' caret &6 (org.eclipse.swt.widgets.Table.createHandle(), createWidget(), etc)\\
&jEdit: rename project source&5 (org.eclipse.core.internal.localstore.FileSystemStore.move, etc)\\ \hline
FindConcept~\cite{Hill:FindConcept07}&Add Textfield&5\\
&Compile Report&8\\ \hline
%COMMIT~\cite{Hassan:concernHistory10}&Error logging&It focuses on improving crosscutting concerns using co-evolving history.\\
%&Debugging&\\ \hline
Portfolio~\cite{Portfolio:DenysICSE11}&mip map dithering texture image graphics&6 methods: ImageTexture:createTextureFromImage, TiledTexture:\\ 
&&buildGaussianGlareTexture, LoadTextureFromFile:initReaderer, etc  \\
&adjust parameters such as brightness for a picture*\\
&read and play midi files*\\ \hline
Rastkar, Murphy&jEdit: add autosave capabilities&They assume that there already exist multiple instances of this concern.\\
 et al.~\cite{Murphy:nlConcern11}&add undo functionality for a command&`All of the methods named `undo': \\ 
 &&override method `org.jhotdraw.util.UndoableAdapter.undo';\\
 &&are a member of the class `undoActivity';\\ \hline
 Strathcona~\cite{Holmes:structural05}&update status line&protected void updateStatusLine(IStructuredSelection selection) \{\\
&&String msg = getStatusLineMessage(selection);\\
&&getViewSite().getActionBars().getStatusLineManager().setMessage(msg); \}\\ 
&&\\
&generate method signature&public boolean visit(MethodDeclaration node) \{\\
&& node.getModifiers();\\
&& node.getName.getIdentifiers();\\
&& return super.visit(node); \} \\ \hline
 GraPacc~\cite{Nguyen:GraPaccICSE12}&SWT usage pattern&Display display = new Display();\\
 && Shell shell = new Shell(display); // fill the rest\\
 && shell.open()\\
 && while (!shell.isDisposed()) \{\\
 &&  if (!display.readAndDispatch())\\
 &&   display.sleep();\\
 && \}\\
 && display.dispose();\\ \hline

\end{tabular*}
 \label{tab:concern}

* represents tasks given to the users. However, the free-form query users use to finish the task is unknown.
}

 \end{center}
\end{table*}

\begin{table*}[ht]
\begin{center}
\caption{Evaluation dataset for reuse tool }
\label{tab:total}
\vspace{1mm}
\scriptsize{
\begin{tabular*}{1\textwidth}{@{}l|l|l|l@{}} \hline
Source&Task&LOC&Result / Description\\\hline
Gilligan~\cite{Holmes:reuse07}&reuse BMP image file parsing in SWT&497&They try to address the problem of source code integration \\
&reuse  module that serializes objects to XML&900& in the context of medium or large-scale reuse tasks. They  \\
&reuse virtual file system from a third-party app&3000& suggest program elements that are easy to reuse based on \\
&reuse GraphML parsing code from Jung&200& structural  relevance and cost of reuse in the source  \\ 
&reuse charting component from Azureus&& context,  and guide  users to  plan a non-trivial reuse task.  \\
&reuse NMEA parser from the Gpsylon project&&They assume that developers have a perfect example at \\
&reuse the lines of code counter from Metrics project&&hand,  and they can finish the reuse task by resolving all\\
&reuse QIF parser from jGnash project&& dependency conflicts.\\ \hline

\end{tabular*}
 \label{tab:reuse}

LOC represents the lines of code that are reused.

}
 \end{center}
\end{table*}

\begin{table*}[ht]
\begin{center}
\caption{Evaluation dataset for code search tools that use free-form query or keyword query}
\label{tab:total}
\vspace{1mm}
\scriptsize{
\begin{tabular*}{1\textwidth}{@{}l|l|l@{}} \hline
Source&Query&Result\\\hline
SNIFF~\cite{sniff:Sen09}&get active editor window from&IWorkbenchWindow window = PlatformUI.\\
& eclipse workbench&getWorkbench().getActiveWorkbenchWindow();\\
&parse a java source and create ast&ASTParser parser = ASTParser.newParser(AST.JLS3);\\
&&CompilationUnit cu = (CompilationUnit) parser.createAST(null);\\
&connect to a database using jdbc&Connection conn = DriverManager.getConnection(path)\\ \hline
Sourcer~\cite{Sourcerer:SC14}&Find a XML parser&org.apache.jasper.xmlparser\\
&Find the use of Depth First Search&org.jeat.search.dfs.BasicDepthFirstSearch\\
&Find the use of Newton Raphson Method&org.cdk.NewtonRaphsonMethod\\ \hline
anyCode~\cite{Gvero:ICSE15}&copy file fname to destination&FileUtils.copyFile(new File(fname), new File(destination))\\
&does x begin with y&x.startsWith(y)\\
&get the current year&new Date().getYear()\\ \hline
EVOLIZER~\cite{gall:nlQueryICSE10}&What methods call addChart?&ServletUtilities: registerChartForDeletion(File, HttpSession)\\
&What method accesses the&DefaultAxisEditor:attemptLabelFontSelection()\\
& attribute labelFontField?\\
&What are the classes that extend JPanel?&DefaultAxisEditor \\ \hline
Keivanloo et al.~\cite{spotWork:ICSE14}&\{getOptionValue, CommandLine\}&CommandLine.getValue(Option)\\
&\{ISelection, isEmpty\}&ISelection.isEmpty()\\
&\{WebElement, click\}&WebElement.click() \\\hline
\end{tabular*}
 \label{tab:freeform}
}
 \end{center}
\end{table*}

### 2015-10-13 weeklyReport/motivating.tex
init 10-12

@@
-\section{Motivating Example}
+%\section{Motivating Example}
 
-Consider that user wants to add undo and redo actions for their Java Swing text editor application with undo/redo buttons.
-Without knowing any APIs, developer  first queries our tool with a free-form query \codefont{`java undo redo example'}.
-Our tool investigates top 10 web pages returned from Google, because empirical evidence indicates that developers rarely look beyond this limit when searching~\cite{Starke:searchNum09}.
-Our tool uses `expert' heuristic to filter and rank web pages: it favors pages that have complete code snippet and text description because these pages are more likely to be written by experts.
-Thus it removes 3 pages without explicit code snippets, and performs the initial parsing for the informal documentations to identify code-like terms.
-
+\begin{comment}
 \noindent{\textbf{Example collection phase.}} With 7  partial programs at hand, it first extracts class-level structural facts for each code example.
@@
 
-\input{example}
-
 \noindent{\textbf{Example clustering phase.}} After extracting facts for each example, our tool identifies main facts shared in all 5 examples shown in Figure~\ref{fig:fact} part A.
@@
 After confirmed by users, our tool automatically fills the rest facts that do not exist in the context shown in Figure~\ref{fig:context} part E. 
+\end{comment}

### 2015-10-13 weeklyReport/problem.tex
init 10-12

@@
-\section{Problem Statement}
+\section{Last week}
 
+Based on our discussion last week, our problem statement includes:
+
+\begin{enumerate}
+\item Developers do not know the name of API elements a priori, though locating code example through existing search engine often expects the developers to know API elements' names.
+\item Reuse tasks involve multiple related classes and methods, rather than a single method/class.
+Yet code search engines do not help developers recognize the latent structure among related classes/methods.
+(at the granularity of multiple methods)
+\item During copy/paste based reuse, developers must remove irrelevant parts.
+Our hypothesis is that having multiple examples of the same kind will help winnow out irrelevant parts.
+(at the granularity of multiple examples)
+\end{enumerate}
+
+%We have three hypotheses correspondingly:
+%\begin{enumerate}
+%\item We believe that NLP text with partial code snippet could help us identify the name of API elements based on keywords from free-form query. 
+%
+%\item Our hypothesis is that we can find related elements by following the structural dependencies of seed API elements in code and by ranking other API elements potentially mentioned in natural language text.
+%
+%\item We believe that clustering multiple examples of the same kind and finding the commonality may help remove irrelevant parts. 
+%
+%\end{enumerate}
+
+I focus on the second and third problems, perform a preliminary study using three popular code search engines to illustrate these two problems, and revise the hypotheses based on our use of code search engine.
+
+\section{Problem 2}
+Problem: Reuse tasks involve multiple related classes and methods, yet code search engines do not help developers recognize the latent structure among related classes/methods.
+
+Hypothesis: We can find related elements by following the structural dependencies of seed API elements in code and by ranking these related API elements based on their topology structure.
+
+Input: a free-form query that user provides to present her reuse intention.
+
+Output: a list of classes/methods implementation that complete this reuse task.
+
+Sub questions: Do reuse tasks involve multiple related classes and methods? Can existing tools find reusable examples that involve multiple related classes and methods?
+
+To answer these two subquestions, I search for the evaluation dataset for existing code search tools using free-form query (SNIFF~\cite{sniff:Sen09}, Portfolio~\cite{Portfolio:DenysICSE11}, Sourcer~\cite{Sourcerer:SC14}, anyCode~\cite{Gvero:ICSE15}, and Keivanloo et al.~\cite{spotWork:ICSE14}), feature location/concern mining tools~\cite{Denys:FCA12, Hill:FindConcept07, Hassan:concernHistory10, Breu:DynamicAspect04},   and reuse tools~\cite{Holmes:reuse07, Holmes:ASE09}.
+Other code search engines such as Koders~\cite{Koders}, Krugle~\cite{Krugle}, and SearchCode~\cite{SearchCode} are available on the web, which can be used to assist programmers by providing relevant code examples with usages of the given free-form query from a large number of public source code repositories.
+Yet the results are sorted based on the text matching and they fail to recognize the latent structure among related classes/methods.
+
+Based on Table~\ref{tab:concern} and Table~\ref{tab:reuse}, most medium-scale or large-scale reuse tasks involve multiple methods and classes.
+However, existing code search tools and  feature location tools  do not help developers recognize the latent structure among related classes/methods.
+We do not focus on large-scale reuse task mentioned in~\cite{Holmes:reuse07, Holmes:ASE09}.
+
+\input{eval-table}
+\input{example}
+
+In summary,  a feature/concern reuse task involves multiple related classes and methods.
+The developer should implement multiple methods and classes to finish the reuse task.
+Existing  code completion tools can complete a single method which involves in multiple API calls, yet they assume that all related APIs or  objects used in their suggested code already exist.
+We argue that it requires multiple methods to implement a non-trivial feature/concern.
+
+\section{Scenario}
+\noindent{\textbf{Add undo and redo action for TextEditor.}}
+
+\begin{table}[ht]
+\begin{center}
+\caption{Search Result from Code Search Engine}
+\label{tab:total}
+\scriptsize{
+\begin{tabular*}{0.5\textwidth}{@{}c|llrr@{}} \hline
+No.&Name&Project&LOC&\# M\\\hline
+1&TextEditor&textmash&1270&12\\
+2,3&AndroidTextEditor&android&576&9\\
+4&DocumentUndoManagerImpl&ide&1227&17\\
+5,6,8&ConsoleTextEditor&groovy&321&7\\ 
+7&PapyrusCDTEditor&eclipse.papyrus&393&7\\
+9,10&AspectEditorContributor&eclipse&88&2\\ \hline
+\end{tabular*}
+ \label{tab:undoResult}
+ \textbf{ \# M} represents the number of methods that contain the query terms. 
+ {\bf No.} represents the rank from CSE.
+Note that CSE may return the same results for multiple times, as the same file may exist in multiple branches.
+For instance, we regard 5,6,8 as identical with manual inspection.
+
+}
+ \end{center}
+\end{table}
+
+Figure~\ref{fig:undoEditor} illustrates the implementation of `add undo/redo' concern mentioned in~\cite{Murphy:nlConcern11}.
+Consider that user wants to add undo and redo actions for her Java Swing text editor application with undo/redo buttons.
+Without knowing any APIs, developer  first queries code search engine (CSE) with a free-form query \codefont{`undo redo TextEditor'}.
+Table~\ref{tab:undoResult} shows top 10 results returned from SearchCode CSE.
+For each partial program returned from CSE, I select the top k (k=5) methods that are related to the given query.
+
+%\subsection{Problem 3}
+%Problem: During copy/paste based reuse, developers must remove irrelevant parts and find salient API elements based on the context.
+
+%Hypothesis: Our hypothesis is that having multiple examples of the same kind will help winnow out irrelevant parts, i.e, clustering multiple examples of the same kind and finding the commonality may help remove irrelevant parts.
+
+%We use the results for  the last three concerns implementation in Table~\ref{tab:concern} found by the code search engine SearchCode to illustrate the Problem 3.
+
+\begin{comment}
 Developers frequently use source code examples as the basis for interacting with an  application programming interface (API) to obtain the needed functionality~\cite{CodeSearch:FSE15}.
@@
    \end{figure*}
+\end{comment}

### 2015-10-13 weeklyReport/appendix.tex
10-13-15,problem to return structured code examples

@@
  \hline
-  \multicolumn{1}{c}{(A) User's context} \\ \hline
-  \vspace{-4mm}
-\begin{Verbatim}[commandchars=\\\{\}, tabsize=2]
-public abstract class AndroidTextEditor extends FormEditor implements IResourceChangeListener \{
- protected void createAndroidPages() \{
-  mIsCreatingPage = true;
-  createFormPages();
-  createTextEditor();
-  createUndoRedoActions();
-  postCreatePages();
-  mIsCreatingPage = false;
- \}
- private void createUndoRedoActions() \{
-  IActionBars bars = getEditorSite().getActionBars();
-  if (bars != null) \{
-    IAction action = mTextEditor.getAction(ActionFactory.UNDO.getId());
-    bars.setGlobalActionHandler(ActionFactory.UNDO.getId(), action);
-    action = mTextEditor.getAction(ActionFactory.REDO.getId());
-    bars.setGlobalActionHandler(ActionFactory.REDO.getId(), action);
-    bars.updateActionBars();
-  \}\}
- private void createTextEditor() \{
-   mTextEditor = new TextEditor();
-   int index = addPage(mTextEditor, getEditorInput());
-   mTextPageIndex = index;
-   setPageText(index, mTextEditor.getTitle());
-   IDocumentProvider provider = mTextEditor.getDocumentProvider();
-   mDocument = provider.getDocument(getEditorInput());
-   mDocument.addDocumentListener(new IDocumentListener() \{
-    public void documentChanged(DocumentEvent event) \{
-    onDocumentChanged(event);
- \}); \} \}
- protected void selectDefaultPage(String defaultPageId) \{
-  if (defaultPageId == null) \{
-   if (getEditorInput() instanceof IFileEditorInput) \{
-    IFile file = ((IFileEditorInput) getEditorInput()).getFile();
-    QualifiedName qname = new QualifiedName(AdtPlugin.PLUGIN_ID, getClass().getSimpleName() + PREF_CURRENT_PAGE);
-    String pageId = file.getPersistentProperty(qname);
-    if (pageId != null) \{ defaultPageId = pageId; \}
-   \} \}
- @Override
- protected void pageChange(int newPageIndex) \{
-  super.pageChange(newPageIndex);
-  if (mIsCreatingPage) \{ return; \}
-  if (getEditorInput() instanceof IFileEditorInput) \{
-   IFile file = ((IFileEditorInput) getEditorInput()).getFile();
-   QualifiedName qname = new QualifiedName(AdtPlugin.PLUGIN_ID, getClass().getSimpleName() + PREF_CURRENT_PAGE);
-   file.setPersistentProperty(qname, Integer.toString(newPageIndex));
-  \} \}
- public void resourceChanged(final IResourceChangeEvent event) \{
-  if (event.getType() == IResourceChangeEvent.PRE_CLOSE) \{
-   Display.getDefault().asyncExec(new Runnable() \{
-   public void run() \{
-    IWorkbenchPage[] pages = getSite().getWorkbenchWindow().getPages();
-    for (int i = 0; i < pages.length; i++) \{
-     if (((FileEditorInput)mTextEditor.getEditorInput()).getFile().getProject().equals(event.getResource())) \{
-      IEditorPart editorPart = pages[i].findEditor(mTextEditor.getEditorInput());
-      pages[i].closeEditor(editorPart, true);
-    \}  \} \}); \} \}
-  \end{Verbatim}
-      \vspace{-4mm}
-     \\ \hline
-\end{tabular} 
-\caption{Result No 4.: add undo/redo to a TextEditor}
-\label{fig:undoEditor}
-\end{minipage}
-\end{figure*}
 
-\begin{figure*}[!htb]
- \begin{minipage}{1\textwidth}
-\scriptsize 
-\begin{tabular}{@{}p{1\textwidth}} 
- \hline 
-  \multicolumn{1}{c}{(A) User's context} \\ \hline
-  \vspace{-4mm}
-\begin{Verbatim}[commandchars=\\\{\}, tabsize=2]
-public class AspectEditorContributor extends MultiPageEditorActionBarContributor \{
- private IEditorPart activeEditorPart;
- private AspectEditor aspectEditor;
- @Override
- public void setActivePage(IEditorPart part) \{
-  if (activeEditorPart == part)   return;
-  activeEditorPart = part;
-  IActionBars actionBars = getActionBars();
-  if (activeEditorPart != null && activeEditorPart instanceof ITextEditor) \{
-   IActionBars siteActionBars = ((IEditorSite)activeEditorPart.getEditorSite()).getActionBars();
-   siteActionBars.setGlobalActionHandler(ITextEditorActionConstants.UNDO, getAction((ITextEditor)activeEditorPart, ITextEditorActionConstants.UNDO));
-   siteActionBars.setGlobalActionHandler(ITextEditorActionConstants.REDO, getAction((ITextEditor)activeEditorPart, ITextEditorActionConstants.REDO));
-   siteActionBars.updateActionBars();              
-  \} else \{
-   if (part instanceof AspectEditor) \{  aspectEditor = (AspectEditor) part; \}
-   IWorkbenchPartSite site = aspectEditor.getSite();
-   if (site instanceof IEditorSite) \{
-    ITextEditor textEditor = aspectEditor.getMultipageEditor().getTextEditor();
-    IActionBars siteActionBars = ((IEditorSite) site).getActionBars();
-    siteActionBars.setGlobalActionHandler(ITextEditorActionConstants.UNDO, getAction(textEditor, ITextEditorActionConstants.UNDO));
-    siteActionBars.setGlobalActionHandler(ITextEditorActionConstants.REDO, getAction(textEditor, ITextEditorActionConstants.REDO));
-    siteActionBars.updateActionBars();              
- \} \}\}
- protected IAction getAction(ITextEditor editor, String actionID) \{
-   return (editor == null ? null : editor.getAction(actionID));
- \} \}
-   \end{Verbatim}
-      \vspace{-4mm}
-     \\ \hline
-\end{tabular} 
-\caption{Result No 4.: add undo/redo to a TextEditor}
-\label{fig:undoEditor}
-\end{minipage}
-\end{figure*}
-
-\begin{figure*}[!htb]
- \begin{minipage}{1\textwidth}
-\scriptsize 
-\begin{tabular}{@{}p{1\textwidth}} 
- \hline 
-  \multicolumn{1}{c}{(A) User's context} \\ \hline
+  \multicolumn{1}{c}{Result 7: PaparusCDTEditor} \\ \hline
   \vspace{-4mm}
@@
   if((actionBars != null) && (gmfUndo == null)) \{
-   gmfUndo = actionBars.getGlobalActionHandler(ITextEditorActionConstants.UNDO);
-    gmfRedo = actionBars.getGlobalActionHandler(ITextEditorActionConstants.REDO);
+   gmfUndo =  \uwave{actionBars.getGlobalActionHandler(ITextEditorActionConstants.UNDO)};
+    gmfRedo =  \uwave{actionBars.getGlobalActionHandler(ITextEditorActionConstants.REDO)};
   \}
@@
    textRedo = actionBars.getGlobalActionHandler(ITextEditorActionConstants.REDO);
-   actionBars.setGlobalActionHandler(ITextEditorActionConstants.UNDO, gmfUndo);
-   actionBars.setGlobalActionHandler(ITextEditorActionConstants.REDO, gmfRedo);
+    \uwave{actionBars.setGlobalActionHandler(ITextEditorActionConstants.UNDO, gmfUndo)};
+    \uwave{actionBars.setGlobalActionHandler(ITextEditorActionConstants.REDO, gmfRedo)};
    actionBars.updateActionBars();
@@
      \\ \hline
+       \multicolumn{1}{c}{Result No.9,10: AspectEditorContributor} \\ \hline
+  \vspace{-4mm}
+\begin{Verbatim}[commandchars=\\\{\}, tabsize=2]
+public class AspectEditorContributor extends MultiPageEditorActionBarContributor \{
+ private IEditorPart activeEditorPart;
+ private AspectEditor aspectEditor;
+ @Override
+ public void setActivePage(IEditorPart part) \{
+  if (activeEditorPart == part)   return;
+  activeEditorPart = part;
+  IActionBars actionBars = getActionBars();
+  if (activeEditorPart != null && activeEditorPart instanceof ITextEditor) \{
+   IActionBars siteActionBars = ((IEditorSite)activeEditorPart.getEditorSite()).getActionBars();
+    \uwave{siteActionBars.setGlobalActionHandler(ITextEditorActionConstants.UNDO, getAction((ITextEditor)activeEditorPart, ITextEditorActionConstants.UNDO))};
+    \uwave{siteActionBars.setGlobalActionHandler(ITextEditorActionConstants.REDO, getAction((ITextEditor)activeEditorPart, ITextEditorActionConstants.REDO))};
+   siteActionBars.updateActionBars();              
+  \} else \{
+   if (part instanceof AspectEditor) \{  aspectEditor = (AspectEditor) part; \}
+   IWorkbenchPartSite site = aspectEditor.getSite();
+   if (site instanceof IEditorSite) \{
+    ITextEditor textEditor = aspectEditor.getMultipageEditor().getTextEditor();
+    IActionBars siteActionBars = ((IEditorSite) site).getActionBars();
+    siteActionBars.setGlobalActionHandler(ITextEditorActionConstants.UNDO, getAction(textEditor, ITextEditorActionConstants.UNDO));
+    siteActionBars.setGlobalActionHandler(ITextEditorActionConstants.REDO, getAction(textEditor, ITextEditorActionConstants.REDO));
+    siteActionBars.updateActionBars();              
+ \} \}\}
+ protected IAction getAction(ITextEditor editor, String actionID) \{
+   return (editor == null ? null : editor.getAction(actionID));
+ \} \}
+   \end{Verbatim}
+      \vspace{-4mm}
+     \\ \hline
+
 \end{tabular} 
-\caption{Result No 4.: add undo/redo to a TextEditor}
+\caption{Results from SearchCode CSE}
 \label{fig:undoEditor}
@@
  \hline 
-  \multicolumn{1}{c}{(A) User's context} \\ \hline
+    \multicolumn{1}{c}{Result No 2,3.: AndroidTextEditor} \\ \hline
+  \vspace{-4mm}
+\begin{Verbatim}[commandchars=\\\{\}, tabsize=2]
+public abstract class AndroidTextEditor extends FormEditor implements IResourceChangeListener \{
+ protected void createAndroidPages() \{
+  mIsCreatingPage = true;
+  createFormPages();
+  createTextEditor();
+  createUndoRedoActions();
+  postCreatePages();
+  mIsCreatingPage = false;
+ \}
+ private void createUndoRedoActions() \{
+  IActionBars bars = getEditorSite().getActionBars();
+  if (bars != null) \{
+    IAction action = mTextEditor.getAction(ActionFactory.UNDO.getId());
+    bars.setGlobalActionHandler(ActionFactory.UNDO.getId(), action);
+    action = mTextEditor.getAction(ActionFactory.REDO.getId());
+    bars.setGlobalActionHandler(ActionFactory.REDO.getId(), action);
+    bars.updateActionBars();
+  \}\}
+ private void createTextEditor() \{
+   mTextEditor = new TextEditor();
+   int index = addPage(mTextEditor, getEditorInput());
+   mTextPageIndex = index;
+   setPageText(index, mTextEditor.getTitle());
+   IDocumentProvider provider = mTextEditor.getDocumentProvider();
+   mDocument = provider.getDocument(getEditorInput());
+   mDocument.addDocumentListener(new IDocumentListener() \{
+    public void documentChanged(DocumentEvent event) \{
+    onDocumentChanged(event);
+ \}); \} \}
+\end{Verbatim}
+\vspace{-4mm}
+ \\ \hline
+  \multicolumn{1}{c}{Result 4: DocumentUndoManagerImpl } \\ \hline
   \vspace{-4mm}
@@
   return false; 
-\}
-public boolean canExecute() \{
-  return fDocumentUndoManager.isConnected();
 \}
@@
   return new UndoableTextChange(fDocumentUndoManager);
- \}
-protected void commit() \{
-  if (fStart < 0) \{
-  if (fDocumentUndoManager.fFoldingIntoCompoundChange) \{
-   fDocumentUndoManager.fCurrent = createCurrent();
-  \} else \{
-   reinitialize();
-  \} \} else \{
-   updateTextChange();
-   fDocumentUndoManager.fCurrent = createCurrent();
-  \} \}
- protected void pretendCommit() \{
-    if (fStart > -1) \{
-       fText = fDocumentUndoManager.fTextBuffer.toString();
-       fPreservedText = fDocumentUndoManager.fPreservedTextBuffer.toString();
  \} \}
@@
 \end{tabular} 
-\caption{Result No 4.: add undo/redo to a TextEditor}
+\caption{Results from SearchCode CSE}
 \label{fig:undoEditor}

### 2015-10-13 weeklyReport/eval-table.tex
10-13-15,problem to return structured code examples

@@
 \begin{tabular*}{1\textwidth}{@{}l|l|l@{}} \hline
-Source&Query&\# methods\\\hline
+Tool&Input: query / context&Output: method / code snippet\\\hline
 FCA~\cite{Denys:FCA12}&jEdit: support for `thick' caret &6 (org.eclipse.swt.widgets.Table.createHandle(), createWidget(), etc)\\
 &jEdit: rename project source&5 (org.eclipse.core.internal.localstore.FileSystemStore.move, etc)\\ \hline
-FindConcept~\cite{Hill:FindConcept07}&Add Textfield&5\\
-&Compile Report&8\\ \hline
+%FindConcept~\cite{Hill:FindConcept07}&Add Textfield&5\\
+%&Compile Report&8\\ \hline
 %COMMIT~\cite{Hassan:concernHistory10}&Error logging&It focuses on improving crosscutting concerns using co-evolving history.\\
@@
 Portfolio~\cite{Portfolio:DenysICSE11}&mip map dithering texture image graphics&6 methods: ImageTexture:createTextureFromImage, TiledTexture:\\ 
-&&buildGaussianGlareTexture, LoadTextureFromFile:initReaderer, etc  \\
+Export~\cite{Export:DenysASE13}&&buildGaussianGlareTexture, LoadTextureFromFile:initReaderer, etc  \\
 &adjust parameters such as brightness for a picture*\\
@@
  &&are a member of the class `undoActivity';\\ \hline
- Strathcona~\cite{Holmes:structural05}&update status line&protected void updateStatusLine(IStructuredSelection selection) \{\\
+ Strathcona~\cite{Holmes:structural05}&update status line&protected void updateStatusLine(IStructuredSelection selection) \{//fill \\
 &&String msg = getStatusLineMessage(selection);\\
@@
 &&\\
-&generate method signature&public boolean visit(MethodDeclaration node) \{\\
+&generate method signature&public boolean visit(MethodDeclaration node) \{//fill\\
 && node.getModifiers();\\
@@
 \begin{tabular*}{1\textwidth}{@{}l|l|l|l@{}} \hline
-Source&Task&LOC&Result / Description\\\hline
+Tool&Task&LOC&Result / Description\\\hline
 Gilligan~\cite{Holmes:reuse07}&reuse BMP image file parsing in SWT&497&They try to address the problem of source code integration \\
@@
 \begin{tabular*}{1\textwidth}{@{}l|l|l@{}} \hline
-Source&Query&Result\\\hline
+Tool&Input: query / keyword&Output: code snippet / code element\\\hline
 SNIFF~\cite{sniff:Sen09}&get active editor window from&IWorkbenchWindow window = PlatformUI.\\

### 2015-10-13 weeklyReport/motivating.tex
10-13-15,problem to return structured code examples

@@
+\input{example-scenario}
 %\section{Motivating Example}
+\section{Usage Scenario}
+\noindent{\textbf{Add undo and redo action for TextEditor.}}
+
+\begin{table}[ht]
+\begin{center}
+\caption{Search Result from Code Search Engine}
+\label{tab:total}
+\scriptsize{
+\begin{tabular*}{0.5\textwidth}{@{}c|llrr@{}} \hline
+No.&Name&Project&LOC&\# M\\\hline
+1&TextEditor&textmash&1270&12\\
+2,3&AndroidTextEditor&android&576&9\\
+4&DocumentUndoManagerImpl&ide&1227&17\\
+5,6,8&ConsoleTextEditor&groovy&321&7\\ 
+7&PapyrusCDTEditor&eclipse.papyrus&393&7\\
+9,10&AspectEditorContributor&eclipse&88&2\\ \hline
+\end{tabular*}
+ \label{tab:undoResult}
+ \textbf{ \# M} represents the number of methods that contain the query terms. 
+ {\bf No.} represents the rank from CSE.
+Note that CSE may return the same results for multiple times, as the same file may exist in multiple branches.
+For instance, we regard 5,6,8 as identical with manual inspection.
+
+}
+ \end{center}
+\end{table}
+
+To further illustrate that reuse task involves in multiple methods and classes, and the reuse task is hard without tool support, I imagine a scenario that user wants to add undo and redo actions for her Java Swing text editor application with undo/redo buttons, inspired by the evaluation task used in~\cite{Murphy:nlConcern11}.
+Without knowing any APIs, developer  first queries code search engine (CSE) with a free-form query \codefont{`undo redo TextEditor'}.
+Figure~\ref{fig:undoEditor} illustrates the implementation of `add undo/redo' concern mentioned in~\cite{Murphy:nlConcern11} and blue part represents source code that implements this feature.
+Table~\ref{tab:undoResult} shows top 10 results returned from SearchCode CSE.
+We find that all code examples require multiple methods and classes to implement a feature.
+We also find that all code examples include other auxiliary features that are not directed related to the undo and redo feature.
+
+We assume that user provides a seed code example for the reuse task.
+She selects the first result from CSE.
+She uses keyword search to locate undo and redo feature in 6 methods and regards them as  seed API calls.
+Shown in Figure~\ref{fig:undoEditor}, she removes  the other  11 methods (865 LOC) that she regards as irrelevant to her reuse task.
+She recognizes that she needs to implement an \codefont{UndoAction} and \codefont{RedoAction} which are the subclass of \codefont{AbstractAction}, and overrides their actionPerform() method.
+In the actionPerformed() methods, she should invokes the \codefont{CompoundUndoManager.undo()} and  \codefont{CompoundUndoManager.redo()} correspondingly.
+Without knowing anything about \codefont{CompoundUndoManager}, she has to query CSE again for `CompoundUndoManager textmash'.
+This class consists of 17 methods (221 LOC) and she has to repeat to keyword search again to locate undo and redo feature in this class.
+With manual inspection, she notices that this \codefont{CompoundUndoManager} is a subclass of \codefont{javax.swing.UndoManager} and it overrides four methods \{\codefont{canUndo, canRedo, undo, redo}\} that are related to the feature.
+She notices that she actually does not need this \codefont{CompoundUndoManager} and decides to invoke its parent class \codefont{UndoManager}  instead.
+She also notices that she does not need the \codefont{CannotRedoException} by using \codefont{UndoManager}.
+
+After she integrates \codefont{UndoManager, UndoAction, and RedoAction} to her context, she tests it and it fails to perform the feature.
+She has to look at other examples, and she finds the No.5 example returned from CSE.
+This example seems promising because it is also an implementation of a TextEditor.
+She notice that  the API \codefont{doc.addUndoableEditListener (undoManager)} seems the one that she misses now, but again, she has to investigate the class   \codefont{TextUndoManager} again.
+
+With this example, we illustrate that salient API calls that implement a desired feature are always interleaving with other related elements.
+To finish a reuse task, developer has to remove irrelevant parts.
+However, it  requires significant effort to tease out these auxiliary features without tool support.
+Since the examples always contain both main feature and auxiliary features,  there seldom exists a perfect example for reuse and developers has to iteratively search for new examples and integrate it to their context until the integration results are examined.
+
+\section{Problem 3}
+Problem: During copy/paste based reuse, developers must remove irrelevant parts and find salient API elements based on the context.
+
+Hypothesis: Our hypothesis is that having multiple examples of the same kind will help winnow out irrelevant parts, i.e, clustering multiple examples of the same kind and finding the commonality may help remove irrelevant parts.
+
+%We use the results for  the last three concerns implementation in Table~\ref{tab:concern} found by the code search engine SearchCode to illustrate the Problem 3.
+
+%  a feature location approach that is similar to~\cite{Denys:FCA12} to identify seed API calls shown in Figure~\ref{fig:undoEditor}.
+We remove the other  11 methods (865 LOC) that we believe is irrelevant to our reuse task.
+
+%For each partial program returned from CSE, we select the top k (k=5) methods that are related to the given query.
+I present No.
+1, 5, 6, 8 to show that it requires multiple methods and classes to implement a concern.
+The other four examples are shown in Appendix.
+
+%In this example, we use feature location approach~\cite{Denys:FCA12} to identify salient API calls,
 

### 2015-10-13 weeklyReport/problem.tex
10-13-15,problem to return structured code examples

--- 2015-10-06 weeklyReport/problem.tex
@@
-\section{Problem Statement}
+\section{Last week}
 
+Based on our discussion last week, our problem statement includes:
+
+\begin{enumerate}
+\item Developers do not know the name of API elements a priori, though locating code example through existing search engine often expects the developers to know API elements' names.
+\item Reuse tasks involve multiple related classes and methods, rather than a single method/class.
+Yet code search engines do not help developers recognize the latent structure among related classes/methods.
+(at the granularity of multiple methods)
+\item During copy/paste based reuse, developers must remove irrelevant parts.
+Our hypothesis is that having multiple examples of the same kind will help winnow out irrelevant parts.
+(at the granularity of multiple examples)
+\end{enumerate}
+
+We have three hypotheses correspondingly:
+\begin{enumerate}
+\item We believe that NLP text with partial code snippet could help us identify the name of API elements based on keywords from free-form query.
+
+\item Our hypothesis is that we can find related elements by following the structural dependencies of seed API elements in code and by ranking other API elements potentially mentioned in natural language text.
+
+\item We believe that clustering multiple examples of the same kind and finding the commonality may help remove irrelevant parts.
+
+\end{enumerate}
+
+I focus on the second  problem, and perform a preliminary study using popular code search engines to illustrate this problem.
+
+\input{example}
+\input{eval-table}
+\section{Problem 2}
+Problem: Reuse tasks involve multiple related classes and methods, yet code search engines do not help developers recognize the latent structure among related classes/methods.
+
+Hypothesis: We can find and rank related elements by following the structural dependencies of seed API elements in code.
+
+Input: a free-form query that user provides to present her reuse intention.
+
+Output: a list of classes/methods implementation that complete this reuse task.
+
+Sub questions: Do reuse tasks involve multiple related classes and methods? Can existing tools find reusable examples that involve multiple related classes and methods?
+
+To answer these two subquestions, I search for the evaluation dataset for existing feature location/concern mining tools~\cite{Denys:FCA12, Hill:FindConcept07, Hassan:concernHistory10, Breu:DynamicAspect04} shown in Table~\ref{tab:concern},    reuse tools~\cite{Holmes:reuse07, Holmes:ASE09} shown in Table~\ref{tab:reuse}, and code search tools using free-form query ~\cite{sniff:Sen09, Portfolio:DenysICSE11, Sourcerer:SC14, Gvero:ICSE15, spotWork:ICSE14} shown in Table~\ref{tab:freeform}.
+We find that most medium-scale or large-scale reuse tasks involve multiple methods and classes,  and the developer should implement multiple methods and classes to finish the reuse task.
+Existing  code completion tools can complete a single method which involves in multiple API calls, yet they assume that all related APIs or  objects used in their suggested code snippet already exist.
+We argue that this assumption might not hold for a non-trivial reuse task, because developers need to implement the salient API calls that provide the main functionality as well as other related elements based on the latent structure.
+
+% existing code search tools and  feature location tools  do not help developers recognize the latent structure among related classes/methods.
+
+%Other code search engines such as Koders~\cite{Koders}, Krugle~\cite{Krugle}, and SearchCode~\cite{SearchCode} are available on the web, %which can be used to assist programmers by providing relevant code examples with usages of the given free-form query from a large number of public source code repositories.
+%yet the results are sorted based on the text matching and they also fail to recognize the latent structure among related classes/methods.
+
+%Based on Table~\ref{tab:concern} and Table~\ref{tab:reuse}, most medium-scale or large-scale reuse tasks involve multiple methods and classes.
+However, existing code search tools and  feature location tools  do not help developers recognize the latent structure among related classes/methods.
+We do not focus on large-scale reuse task mentioned in~\cite{Holmes:reuse07, Holmes:ASE09}.
+
+%In summary,  a feature/concern reuse task involves multiple related classes and methods.
+The developer should implement multiple methods and classes to finish the reuse task.
+Existing  code completion tools can complete a single method which involves in multiple API calls, yet they assume that all related APIs or  objects used in their suggested code already exist.
+We argue that it requires multiple methods to implement a non-trivial feature/concern.
+
+%\subsection{Problem 3}
+%Problem: During copy/paste based reuse, developers must remove irrelevant parts and find salient API elements based on the context.
+
+%Hypothesis: Our hypothesis is that having multiple examples of the same kind will help winnow out irrelevant parts, i.e, clustering multiple examples of the same kind and finding the commonality may help remove irrelevant parts.
+
+%We use the results for  the last three concerns implementation in Table~\ref{tab:concern} found by the code search engine SearchCode to illustrate the Problem 3.
+
+\begin{comment}
 Developers frequently use source code examples as the basis for interacting with an  application programming interface (API) to obtain the needed functionality~\cite{CodeSearch:FSE15}.

### 2015-10-13 weeklyReport/related.tex
10-13-15,problem to return structured code examples

@@
 \section{Related Work}
-\input{table}
-\noindent{\textbf{Extract partial program from informal documentation.}}  Lightweight regular expressions and information retrieval techniques have been widely used to resolve the links between source code elements and documentations.
+%\input{table}
+%\noindent{\textbf{Extract partial program from informal documentation.}}  Lightweight regular expressions and information retrieval techniques have been widely used to resolve the links between source code elements and documentations.
 Bacchelli et al.~\cite{Bacchelli:emailICSE10} use regular expressions to  identify code elements in email discussions based on programming naming conventions.
@@
 We advance these tools in the sense that we not only identify partial program as code example, but also help cluster similar examples and integrate reusable examples to the target context.
+\noindent{\textbf{Feature Location Tools.}}  Poshyvanyk et al.~\cite{Denys:FCA12} use information retrieval approach to locate a queried feature in source code.
+They  evaluate the similarity between documents and user query and cluster the source code based on formal concept analysis.
+Portforlio~\cite{Portfolio:DenysICSE11} and Export~\cite{Export:DenysASE13} identify related functions by combining both latent structure similarity and lexical information similarity.
+Our feature location approach is similar to~\cite{Portfolio:DenysICSE11} yet we focus on suggesting implementation for the feature rather than identify feature location.
+Rastkar et al.~\cite{Murphy:nlConcern11} summarize the structure of multiple instances of a crosscutting concern in natural language, yet they only extract structural facts in the level of method signature and class hierarchy.
+We make it one step further to suggest feature implementation based on the context and user query.
 
-\noindent{\textbf{Cluster code examples.}} 
+%Hill et al.~\cite{Hill:FindConcept07} leverage natural language analysis to
+
+\noindent{\textbf{Code Search Tools.}} 
 Our example clustering approach is similar to some prior works that extract representative examples for specific APIs or user query. 
@@
 MUSE~\cite{MUSE:MarcusICSE15} addresses this limitation using slicing to generate concrete usage examples and selects the most representative ones based on the popularity and readability while  Keivanloo et al\/\cite{spotWork:ICSE14} uses clone detection to cluster examples involving loops and conditions.
-We make it one step further to support partial code example clustering and identify structural correspondence to identify both common features and alternative features.
-PRIME~\cite{Prime:OOPSLA12} supports code search over partial programs based on type state transition, yet it requires users to provide partial temporal specification for generalized {\it typestate}.
-There exists a number of code example suggestion tools that recommend call chains~\cite{Mandelin:jungloid05, parseWeb:ASE07, Xsnippet:OOPSLA06} or related functions~\cite{Export:DenysASE13, Portfolio:DenysICSE11} based on queries~\cite{Sourcerer:SC14} or contexts~\cite{Holmes:structural05, Prompter:MSR14}.
+We make it one step further to  identify structural correspondence to identify both common features and alternative features.
+There exists a number of code example suggestion tools that recommend call chains~\cite{Mandelin:jungloid05, parseWeb:ASE07, Xsnippet:OOPSLA06}  or contexts~\cite{Holmes:structural05, Prompter:MSR14}.
 But these tools can only recommend code examples in the method level which make them insufficient for  reuse tasks across multiple classes.

### 2015-10-16 backport_paper/intro.tex
init backport

\section{Introduction}

As software projects grow ever larger, it has become a challenge to meet different requirements from different users and dispatch these requirements to multiple development teams.   One common solution to this problem is to use branches within the source code management system. Branches  provides a workspace where changes can be made and tested in one branch without affecting any other branches.  This feature allows development teams to partition work and prevent interruptions from external sources. With the advert of version control systems that facilitate easy branching and merging such as Git andMercurial, many open source projects have begun using branching in their distributed development practices, including Linux kernel, Eclipse, and Apache Hadoop.

Recent studies show that branches do not come without a price~\cite{Muslu:dvcsICSE14, Bird:whatIfFSE12}. Since a change is initially only visible within the branch, it must be integrated into a single target branch with other changes from multiple feature branches, initiating a conflict resolution process if changes are incompatible. This process is known as upstream merge that pushes changes into higher  branch levels. Moreover,  to maintain multiple product variants for different users simultaneously, the bug-fixes and necessary features should be backported from the main branch to release branches or other feature branches.

However,the porting practices in large scale open source projects have not been systematically studied in a quantitative manner:

 In the effort to improve the current solution for backporting in the industry.

### 2015-10-20 weeklyReport/approach.tex
10-13-15,problem to return structured code examples
10-20, cluster code example

@@
 
-To identify methods that implement concerns, I build a prototype which invokes Code Search Engine (CSE) API and analyzes the results from CSE using partial program analysis~\cite{partialProgram:OOPSLA08}.
-I select SearchCode~\cite{SearchCode} because it is an open source code search engine with over 7000 projects from  Github, Bitbucket, Google Code, and Sourceforge, with complete API documentations.
-To identify queried features in the returned source code,  I use the mean of TF-IDF weight  for each query term as a weighting factor and select top k (k=5) methods that are related to the given query.
+Our approach helps identify and integrate reusable examples in two phases:
+
+\subsection{Example Collection Phase.}  
+We identify the main features from multiple partial programs derived from informal resources.
+Without confined to an established code corpus, we leverage web search engine to obtain a list of code examples in the form of partial programs and use partial program analysis~\cite{partialProgram:OOPSLA08} to infer partial type and resolve syntactic ambiguity.
+
+\noindent{\textbf{Query Code Search Engine.}}  We use code search engine SearchCode~\cite{SearchCode} to extract code examples based on free-form queries from users.
+We choose it because 1) it has good support for free-form queries,  2) it is an open source code search engine with over 7000 projects from  Github, Bitbucket, Google Code, and Sourceforge, 3) it has complete API documentations and returns.
+
+\noindent{\textbf{Locate Queried Features.}}  Considering that source code examples always contain multiple features, we identify program elements that are related to the queried features.
+I use the mean of TF-IDF weight  for each query term as a weighting factor and select all methods whose weighting score is bigger than a threshold.
 This approach is similar to prior works that use  IR~\cite{Denys:FCA12} and NL analysis~\cite{Hill:FindConcept07} for feature location.
@@
 TF-IDF =  $avg( \log (1 + f_{t,d}) \times  \log \frac {N} {n_t}), f_{t,d}$ is the frequency of term $t$ in method $d$, $N$ is the total number of methods, $n_t$ is the number of methods that have the term $t$.
+
+\noindent{\textbf{Extract Structural Facts.}}  Before we extract structural facts, we construct symbol table for partial program based on the partial program analysis~\cite{partialProgram:OOPSLA08}.
+We extract structural facts in an ontology instance.
+The ontology schema we use is the SEON Java ontology, which has been used in several prior works~\cite{gall:seonICSE10, Murphy:nlConcern11}.
+Every extracted fact is represented in the ontology instance by one or more  \codefont{(subject, predicate, object)} triples.
+For instance, the fact that class $c_1$ extends class $c_2$ is represented by triple \codefont{($c_2$, subType, $c_1$)}.
+To manipulate the relationship between different facts, we use Resource Description Framework (RDF)  to represent each \codefont{(subject, predicate, object)} triple as an edge from \textit{subject} to \textit{object} labeled with {\it predicate}.
+We use \codefont{Apache Jena}, which is a Java framework for  linked data applications,  to create and process ontology instances.
+We define \codefont{subType} as  transitive predicate as ($c_1$, subType, $c_2$) and ($c_2$, subType, $c_3$) $\rightarrow$  ($c_1$, subType, $c_3$).
+
+\begin{table}[ht]
+\begin{center}
+\caption{Structural Fact Types}
+\label{tab:total}
+\vspace{1mm}
+\scriptsize{
+\begin{tabular*}{0.5\textwidth}{@{}c|r|l@{}} \hline
+Level&Type&Description\\\hline
+&($c_1$, subType, $c_2$)& class $c_1$ extends $c_2$ \\
+class&($c_1$, innerclass, $c_2$)& class $c_1$ has an inner class $c_2$ \\
+level&($c$, field, $v$)& class $c$ has field $v$ \\ 
+&($c$, method, $m$)& class $c$ contains method $m$ \\ \hline
+&($m$, parameter, $v$)& method  $m$ has parameter $v$ \\ 
+method&($m$, return, $t$)& method  $m$ returns an object of type $t$ \\ 
+level&($e_1$, accesses, $e_1$)& $e_1$ = $e_2$, $e_1$ and $e_2$ are expressions\\ 
+&($m_1$, call, $m_2$)& method  $m_1$ calls method $m_2$ \\ 
+&($m$, variable, $v$)& method  $m$ has variable $m_2$ \\  \hline
+&($o$, name, $s$)& The name of object  $o$ is  $s$ \\  \hline
+\end{tabular*}
+ \label{tab:dataset}
+}
+ \end{center}
+\end{table}
+
+\begin{figure}[!htb]
+    \begin{minipage}{0.5\textwidth}
+    \centering
+\includegraphics[width=1\textwidth]{fig/rdf.pdf}
+ \end{minipage}%
+   \caption{RDF graph}
+ \label{fig:rdf}
+   \end{figure}
+
+%The Resource Description Framework (RDF) [26] is the data-model for representing meta-data in the Semantic Web.
+The RDF data-model formalizes meta-data based on subject ?
+predicate ?
+object triples, so called RDF statements.
+
+\subsection{Example Clustering Phase.}
+
+We take three steps in this phase.
+Based on the type facts extracted from partial program analysis, we first cluster similar code examples based on the number of shared class-level facts and API calls (i.e.,  \codefont{call} facts) to reduce the duplicated code snippets.
+Next, for each example in each cluster, we identify main facts that are shared among all examples, and perform slicing to identify related elements.
+Finally, we group auxiliary features based on program slicing and lexical similarity.
+
+\noindent{\textbf{Cluster Examples.}}   We greedily select the most suitable structural correspondence~\cite{Cottrell:jigsaw08} and propagate the similarity of {\it object} nodes to the {\it subject} node.
+
+ The comparison is done by investigating the lexical similarity and similar paths in RDF graphs.
+For example, when comparing UndoAction.actionPerformed() in Figure~\ref{fig:cluster1} (A), we first try to match the fact \codefont{(actionPerformed, calls, CompoundUndoManager.
+undo())}.
+We only look at the facts with the same type.
+We find  the fact  \codefont{(actionPerformed, calls, TextUndoManager.undo())} which is lexically similar though not identical to the target fact.
+We calculate the similarity score as follows: 1) We split the name for each element in the tuple by camel-case splitter and separators such as `.' and `('.
+Thus \codefont{TextUndoManager.undo()} is split as \codefont{[Text, Undo, Manager, undo]}.
+2) We calculate the distance for each element as the $ editDistance(s_1,s_2)/ Min$ $(|s_1|, |s_2|)$, thus the similarity score between \codefont{TextUndoManager.undo()} and \codefont{CompoundUndoManager.undo()} is 0.25.
+3) The distance between two tuples are the average distance for three elements.
+Thus the distance of two facts are 0.08.
+We select  the most similar  fact by minimizing the similarity distance and we identify \codefont{(actionPerformed, calls, CompoundUndoManager.undo())} as the structural correspondence of the fact \codefont{(actionPerformed, calls, TextUndoManager.undo())}.
+
+ Next, we try to match the fact   \codefont{(actionPerformed, calls, updateUndoState())}.
+Knowing that there is an edge from \codefont{updateUndoState()} to \codefont{setEnabled(undo.canUndo()} in RDF graph, we recursively match the fact \codefont{(updateUndoState, calls, setEnabled(undo.canUndo()))}  with  \codefont{(actionPerformed, calls, setEnabled(undo.canUndo()))}.
+The similarity score of {\it object} node \codefont{(updateUndoState, calls, setEnabled(undo.can Undo()))} is propagated to {\it subject} node \codefont{(actionPerformed, calls, updateUndoState())} as 0.4 compared to fact  \codefont{(actionPerformed, calls, setEnabled(undo.
+canUndo()))} in class \codefont{UndoAction}.
+Our tool keeps on performing this matching until all facts in the target (Figure~\ref{fig:cluster1} (A)) is assigned a similarity score as 0 (i.e., fail to find correspondence) or a similarity score with other facts in the compared node.
+
+Finally, the examples are clustered based on the number of  {\it object} nodes (without outer edge).  Our tool keeps on refining the large cluster to present a structured code examples to developers.
+
+\noindent{\textbf{Extract Example Skeleton.}}  We extract all matched {\it object} nodes (without outer edge) and use them as  match seeds.
+We then perform dependency analysis to  extract example skeleton.
+An example skeleton should start from an element without any inner edge and end at an element without any outer edge which covers all match seeds.
+
+When selecting features, we use three rules to rank features in different examples: 1) the cost of reuse; 2) the number of resolved relationship; 3) the frequency of the feature in multiple examples; 4) the simplicity of code implementation.
+
+The cost of reuse is measured as the number of outer edges in RDF graph, i.e., the more outer edges in RDF graph, the more expensive to reuse because it has more dependencies.
+We have rule 2) because  some of the relationships can not be resolved in partial program.
+When user tries to reuse the example, they have to manually resolve these external relationships.
+For instance, in Figure~\ref{fig:cluster2} (D), the feature group B.1 (\codefont{mUndoAction = new LintEditAction(undoAction, getEditorDelegate().getEditor())}) is not selected because the class \codefont{LintEditAction} cannot be resolved based on this partial program.
+The first two rules ease the reusability of our suggested code example.
+The third rule makes sure that the feature is representative and the last rule improves the understandability of our results.
+The simplicity is measured as the length of the code.
+For instance, we prefer \codefont{actionBars.setGlobalActionHandler (ITextEditorActionConstants.UNDO, undo)} in Figure~\ref{fig:cluster24} (D) than \codefont{actionBars.setGlobalActionHandler (ITextEditorActionConstants.UNDO, getAction((ITextEditor) part,  ITextEditorActionConstants.UNDO))} because the former one is easier to interpret.
+
+\noindent{\textbf{Group Auxiliary Features.}}    The auxiliary features are different example  skeletons.  (TBD)
+
+\noindent{\textbf{Enable User Interaction.}}    The user could select the features and our tool is able to extract related elements based on their selection. (TBD)
+
+%\begin{table}[ht]
+%\begin{center}
+%\caption{Common Structural Facts Extracted from the Examples }
+%\label{tab:total}
+%\vspace{1mm}
+%\scriptsize{
+%\begin{tabular*}{0.5\textwidth}{@{}l|l@{}} \hline
+%Level&Structural Facts\\\hline
+%class&subType(Undo*Action, AbstractAction), \\ 
+%&subType(Redo*Action, AbstractAction), \\ \hline
+%method&override(actionPerformed(), Undo*Action, AbstractAction), \\
+%&override(actionPerformed(), Redo*Action, AbstractAction), \\ \hline
+%statement&init(*,javax.swing.undo.UndoManager), \\
+%&invoke(UndoManager.undo, actionPerformed(), Undo*Action),\\
+%& invoke(UndoManager.redo, actionPerformed(), Redo*Action)\\  \hline
+%\end{tabular*}
+% \label{tab:dataset}
+%
+%We simplify some full names due to space limitation: 
+%
+%AbstractAction: javax.swing.AbstractAction;
+%
+%UndoListener: javax.swing.event.UndoableEditListener
+%
+%actionPerformed():actionPerformed(ActionEvent)
+%}
+% \end{center}
+%\end{table}

### 2015-10-20 weeklyReport/motivating.tex
10-20, cluster code example

@@
-\input{example-scenario}
-%\section{Motivating Example}
+   \input{example-scenario}%\section{Motivating Example}
 \section{Usage Scenario}
-\noindent{\textbf{Add undo and redo action for TextEditor.}}
+ To further illustrate that reuse task involves in multiple methods and classes, and the reuse task is hard without tool support, I imagine a scenario that user wants to add undo and redo actions for her Java Swing text editor application with undo/redo buttons, inspired by the evaluation task used in~\cite{Murphy:nlConcern11}.
 
-\begin{table}[ht]
+\noindent{\textbf{Query: undo redo TextEditor}}
+
+\begin{table*}[ht]
 \begin{center}
@@
 \scriptsize{
-\begin{tabular*}{0.5\textwidth}{@{}c|llrr@{}} \hline
-No.&Name&Project&LOC&\# M\\\hline
-1&TextEditor&textmash&1270&12\\
-2,3&AndroidTextEditor&android&576&9\\
-4&DocumentUndoManagerImpl&ide&1227&17\\
-5,6,8&ConsoleTextEditor&groovy&321&7\\ 
-7&PapyrusCDTEditor&eclipse.papyrus&393&7\\
-9,10&AspectEditorContributor&eclipse&88&2\\ \hline
+\begin{tabular*}{1\textwidth}{@{}c|rrrrrl@{}} \hline
+No.&Name&Project&LOC&\#M&\#C&Involved objects and API calls\\\hline
+1&TextEditor&textmash&1271&12&1&UndoManager, UndoAction, RedoAction\\
+4&ConsoleTextEditor&groovy-core&322&7&1&UndoManager, UndoAction, RedoAction\\ \hline
+2&AndroidTextEditor&android-sdk&587&9&2& IActionBars.setGlobalActionHandler(), ActionFactory.UNDO, ActionFactory.REDO\\
+8&LayoutCanvas&sdk&1721&3&2& IActionBars.setGlobalActionHandler(), ActionFactory.UNDO, ActionFactory.REDO\\
+9&IUEditorContributor&buckminster&193&2&2& IActionBars.setGlobalActionHandler(), ActionFactory.UNDO, ActionFactory.REDO\\ \hline
+5&PapyrusCDTEditor&papyrus&393&7&4&IActionBars.setGlobalActionHandler(), ITextEditorActionConstants.UNDO\\
+6&AspectEditorContributor&eclipse-plugin&89&2&4&IActionBars.setGlobalActionHandler(), ITextEditorActionConstants.UNDO\\
+10&WSDLContributor&eclipse&254&2&4&IActionBars.setGlobalActionHandler(), ITextEditorActionConstants.UNDO\\ \hline
+3&DocumentUndoImpl&ide&1228&17&3&FileDocumentUndoManager\\ \hline
+7&ATETextPane&antlrworks&650&7&5&AbstractUndoableEdit.undo(), AbstractUndoableEdit.redo(),\\\hline
 \end{tabular*}
  \label{tab:undoResult}
- \textbf{ \# M} represents the number of methods that contain the query terms. 
   {\bf No.} represents the rank from CSE. 
-Note that CSE may return the same results for multiple times, as the same file may exist in multiple branches.
-For instance, we regard 5,6,8 as identical with manual inspection.
-
+ \textbf{ \#M} represents the number of methods that contain the query terms.  \textbf{ \#C} represents the number of clusters the example belongs to.
 }
  \end{center}
-\end{table}
+\end{table*}
 
-To further illustrate that reuse task involves in multiple methods and classes, and the reuse task is hard without tool support, I imagine a scenario that user wants to add undo and redo actions for her Java Swing text editor application with undo/redo buttons, inspired by the evaluation task used in~\cite{Murphy:nlConcern11}.
  Without knowing any APIs, developer  first queries code search engine (CSE) with a free-form query \codefont{`undo redo TextEditor'}.
-Figure~\ref{fig:undoEditor} illustrates the implementation of `add undo/redo' concern mentioned in~\cite{Murphy:nlConcern11} and blue part represents source code that implements this feature.
+%Figure~\ref{fig:undoEditor} illustrates the implementation of `add undo/redo' concern mentioned in~\cite{Murphy:nlConcern11} and blue part represents source code that implements this feature.
 Table~\ref{tab:undoResult} shows top 10 results returned from SearchCode CSE.
-We find that all code examples require multiple methods and classes to implement a feature.
+%We find that all code examples require multiple methods and classes to implement a feature.
 We also find that all code examples include other auxiliary features that are not directed related to the undo and redo feature.
 
-We assume that user provides a seed code example for the reuse task.
-She selects the first result from CSE.
-She uses keyword search to locate undo and redo feature in 6 methods and regards them as  seed API calls.
-Shown in Figure~\ref{fig:undoEditor}, she removes  the other  11 methods (865 LOC) that she regards as irrelevant to her reuse task.
+Before using our tool, she has to manually investigate all code search examples to identify which API calls are frequently used.
+She selects the first result from CSE and uses keyword search to locate undo and redo feature in 6 methods and regards them as search seed.
+She started to explore the relationships between these methods.
+Shown in Figure~\ref{fig:cluster1} (A), she removes  the other  11 methods (865 LOC) that she regards as irrelevant to her reuse task.
 She recognizes that she needs to implement an \codefont{UndoAction} and \codefont{RedoAction} which are the subclass of \codefont{AbstractAction}, and overrides their actionPerform() method.
@@
 After she integrates \codefont{UndoManager, UndoAction, and RedoAction} to her context, she tests it and it fails to perform the feature.
-She has to look at other examples, and she finds the No.5 example returned from CSE.
-This example seems promising because it is also an implementation of a TextEditor.
-She notice that  the API \codefont{doc.addUndoableEditListener (undoManager)} seems the one that she misses now, but again, she has to investigate the class   \codefont{TextUndoManager} again.
+She has to look at other examples, and she finds the fifth example from CSE is similar to the first example.
+Shown in Figure~\ref{fig:cluster1} (B), This example seems similar because it uses an \codefont{TextUndoManager}, and implements \codefont{UndoAction} and \codefont{RedoAction}.
+She notice that  the API \codefont{doc.addUndoable EditListener(undoManager)} seems the one that she misses now, but again, she has to investigate the class   \codefont{TextUndoManager} again.
 
@@
 
-\section{Problem 3}
-Problem: During copy/paste based reuse, developers must remove irrelevant parts and find salient API elements based on the context.
-
-Hypothesis: Our hypothesis is that having multiple examples of the same kind will help winnow out irrelevant parts, i.e, clustering multiple examples of the same kind and finding the commonality may help remove irrelevant parts.
+ Our tool is able to represent code examples returned from CSE in a structured manner.
+We cluster the examples that share similar API calls and extract the queried features.
+Shown in Figure~\ref{fig:cluster1} (C), our tool extracts a skeleton of reuse code example for the queried feature.
+At the same time, we group auxiliary features based on program slicing and lexical similarity so that the user can select the features that she wants, as shown in Figure~\ref{fig:cluster1} (D).
 
@@
 
-\begin{comment}
-\noindent{\textbf{Example collection phase.}} With 7  partial programs at hand, it first extracts class-level structural facts for each code example.
-Based on a relative match threshold to measure the relative occurrence of the number of matched facts out of all class-level facts,  our tool clusters these examples in three groups using complete linkage technique: 5 examples use classes in Java Swing like `AbstractAction' and `UndoableEditListener', another example uses a `Node' data structure to illustrate how to implement undo/redo actions using command design pattern, and the last example is the javadoc for `UndoManager'.
-Our tool starts from the first cluster as it has the highest relative occurrence out of all examples.
-Based on partial program analysis, we generate a list of type facts to infer types and bind methods.
-
-The common facts our tool extracts include: 
-\begin{table}[ht]
-\begin{center}
-\caption{Common Structural Facts Extracted from the Examples }
-\label{tab:total}
-\vspace{1mm}
-\scriptsize{
-\begin{tabular*}{0.5\textwidth}{@{}l|l@{}} \hline
-Level&Structural Facts\\\hline
-class&subType(Undo*Action, AbstractAction), \\ 
-&subType(Redo*Action, AbstractAction), \\
-&subType(*Listener, UndoListener)\\ \hline
-method&override(actionPerformed(), Undo*Action, AbstractAction), \\
-&override(actionPerformed(), Redo*Action, AbstractAction), \\ \hline
-statement&init(*,javax.swing.undo.UndoManager), \\
-&invoke(UndoManager.undo, actionPerformed(), Undo*Action),\\
-& invoke(UndoManager.redo, actionPerformed(), Redo*Action)\\  \hline
-\end{tabular*}
- \label{tab:dataset}
-
-We simplify some full names due to space limitation:
-
-AbstractAction: javax.swing.AbstractAction;
-
-UndoListener: javax.swing.event.UndoableEditListener
-
-actionPerformed():actionPerformed(ActionEvent)
-}
- \end{center}
-\end{table}
-
-\noindent{\textbf{Example clustering phase.}} After extracting facts for each example, our tool identifies main facts shared in all 5 examples shown in Figure~\ref{fig:fact} part A.
-It leverages slicing to group related facts.
-In this example, 3 of them add \codefont{Undo*Action} to \codefont{JMenuItem} by invoking \codefont{JMenuItem.add (ActionEvent)} and support undo and redo actions for Text Editor shown in Figure~\ref{fig:fact} part B.
-The other two of them invoke \codefont{JButton.addActionListener(ActionEvent)} to add these two actions to \codefont{JButton}, and support \codefont{JApplet} Shape drawing shown in Figure~\ref{fig:fact} part C.
-After extracting both main facts and related facts, we generate two reuse tasks by combining main facts with each related fact group.
-
-\noindent{\textbf{Example integration phase.}} Given a context like Figure~\ref{fig:context} part D, our tool identifies the best-fit reuse task based on the number of matched facts in the user's context.
+%\noindent{\textbf{Example integration phase.}} Given a context like Figure~\ref{fig:context} part D, our tool identifies the best-fit reuse task based on the number of matched facts in the user's context.
 If our tool fails to identify any matched facts in the user's context, it will simply rank the reuse task based on its occurrence in the code examples.
@@
 After confirmed by users, our tool automatically fills the rest facts that do not exist in the context shown in Figure~\ref{fig:context} part E.
-\end{comment}

### 2015-10-20 weeklyReport/problem.tex
10-20, cluster code example

--- 2015-10-06 weeklyReport/problem.tex
@@
 
-Developers frequently use source code examples as the basis for interacting with an  application programming interface (API) to obtain the needed functionality~\cite{CodeSearch:FSE15}.
+Problem: The code examples returned from code search engine or other code search tools are not structured.
+
+%Reuse tasks involve multiple related classes and methods, yet code search engines do not help developers recognize the latent structure among related classes/methods.
+
+%Hypothesis: We can find and rank related elements by following the structural dependencies of seed API elements in code.
+
+Input: a set of code examples returned from code search engine.
+
+Output: a list of code example clusters organized based on their structural similarity.
+
+%Sub questions: Do reuse tasks involve multiple related classes and methods? Can existing tools find reusable examples that involve multiple related classes and methods?
+
+%To answer these two subquestions, I search for the evaluation dataset for existing feature location/concern mining tools~\cite{Denys:FCA12, Hill:FindConcept07, Hassan:concernHistory10, Breu:DynamicAspect04} shown in Table~\ref{tab:concern},    reuse tools~\cite{Holmes:reuse07, Holmes:ASE09} shown in Table~\ref{tab:reuse}, and code search tools using free-form query ~\cite{sniff:Sen09, Portfolio:DenysICSE11, Sourcerer:SC14, Gvero:ICSE15, spotWork:ICSE14} shown in Table~\ref{tab:freeform}.
+We find that most medium-scale or large-scale reuse tasks involve multiple methods and classes,  and the developer should implement multiple methods and classes to finish the reuse task.
+Existing  code completion tools can complete a single method which involves in multiple API calls, yet they assume that all related APIs or  objects used in their suggested code snippet already exist.
+We argue that this assumption might not hold for a non-trivial reuse task, because developers need to implement the salient API calls that provide the main functionality as well as other related elements based on the latent structure.
+
+%Developers frequently use source code examples as the basis for interacting with an  application programming interface (API) to obtain the needed functionality~\cite{CodeSearch:FSE15}.
 In this case, the source code example serves as the explicit origin for a reuse task which transforms a sequence of APIs with corresponding control structure to the target context~\cite{Frakes:reuseStatus05}.
@@
 
-Both location and integration of reusable examples are not trivial.
+%Both location and integration of reusable examples are not trivial.
 For the phase of location, existing tools that search for specific API usage examples~\cite{MAPO:ECOOP09, Buse:apiICSE12, Export:DenysASE13, Sourcerer:SC14} might not be able to support such reuse tasks that always involve in multiple classes and related methods.
@@
 
-To overcome these challenges, we propose to automatically identify common API calls that provide the main feature across different partial program examples from informal documentation, and integrate this reusable example to the target context with a set of related elements that are necessary to implement the main feature.
+%To overcome these challenges, we propose to automatically identify common API calls that provide the main feature across different partial program examples from informal documentation, and integrate this reusable example to the target context with a set of related elements that are necessary to implement the main feature.
 We assume that the overlapping API calls are the main features that the user intends to reuse based on the user query, and the related elements should be transformed to the target together with main features if they are data dependent and control dependent on the common functionalities in a common way across different examples.
 Figure~\ref{fig:system} illustrates the process of our system.
-Given a free-form query from users, our tool invokes search engine (e.g., Google) to obtain a list of partial programs by recovering links between code elements and informal resources, clusters these examples and extracts common structural facts (e.g., jQuery logical facts) with corresponding control structures for each cluster, identifies a set of related elements that interact with main elements in a common way,  constructs reuse task with both main elements and related elements and ranks them based on user's context, and finally integrates the reuse task selected by users to the target context.
+Given a free-form query from users, our tool invokes code search engine  to obtain a list of partial programs by recovering links between code elements and informal resources, clusters these examples and extracts common structural facts (e.g., jQuery logical facts) with corresponding control structures for each cluster, identifies a set of related elements that interact with main elements in a common way,  constructs reuse task with both main elements and related elements and ranks them based on user's context, and finally integrates the reuse task selected by users to the target context.
 
@@
 
-Our approach helps identify and integrate reusable examples in three phases:
-\begin{itemize}
-\item \textbf{Example Collection Phase.} We identify the main features from multiple partial programs derived from informal resources.
-Without confined to an established code corpus, we leverage web search engine to obtain a list of code examples in the form of partial programs~\cite{PeterACE:ICSE13, RecoDoc:ICSE12}.
-We use partial program analysis~\cite{partialProgram:OOPSLA08} to infer partial type and resolve syntactic ambiguity.
+%\item \textbf{Example Integration Phase.} Our approach investigates the user's contexts to recommend the best-fit reuse task  considering the number of matched structural facts in target context.
+After user's selection, our approach integrates the reuse task to the target context by transforming the unmatched structural facts based on matched facts in the context.
 
-\item \textbf{Example Clustering Phase.} We take three steps in this phase.
-Based on the type facts extracted from partial program analysis, we first cluster similar code examples based on the number of shared class-level facts to reduce the duplicated code snippets.
-Next, for each example in each cluster, we identify main facts that are shared among all examples, and perform slicing to identify related elements.
-We ignore the specific related elements that appear in a single example.
-Finally, we group the related elements based on their common interaction with main elements.
-
-\item \textbf{Example Integration Phase.} Our approach investigates the user's contexts to recommend the best-fit reuse task  considering the number of matched structural facts in target context.
-After user's selection, our approach integrates the reuse task to the target context by transforming the unmatched structural facts based on matched facts in the context.
-\end{itemize}
-
- \begin{figure*}[!htb]
-    \centering
-\includegraphics[width=1\textwidth]{fig/system.pdf}
-       \caption{System process overview}
-        \label{fig:system}
-   \end{figure*}
+% \begin{figure*}[!htb]
+%    \centering
+%\includegraphics[width=1\textwidth]{fig/system.pdf}
+%       \caption{System process overview}
+%        \label{fig:system}
+%   \end{figure*}

### 2015-10-28 weeklyReport/approach.tex
10-27 IR clustering

@@
+\input{dataset_table}
 \section{Approach}
+Without confined to an established code corpus, we use code search engine to extract code examples based on free-form queries from users.
+We build our tool in a plugin mechanism so that any code search engine can be easily planted into our system.
+We choose SearchCode~\cite{SearchCode} in our prototype because 1) it has good support for free-form queries,  2) it is an open source code search engine with over 7000 projects from  Github, Bitbucket, Google Code, and Sourceforge, 3) it has complete API documentation.
 
-Our approach helps identify and integrate reusable examples in two phases:
+\subsection{Example Clustering Phase}
 
-\subsection{Example Collection Phase.}  
-We identify the main features from multiple partial programs derived from informal resources.
-Without confined to an established code corpus, we leverage web search engine to obtain a list of code examples in the form of partial programs and use partial program analysis~\cite{partialProgram:OOPSLA08} to infer partial type and resolve syntactic ambiguity.
+\noindent{\textbf{Reformulate User Query.}}  Most code search engines rely on text matching to extract code examples, thus vocabulary mismatching can affect their performance~\cite{Hill:NLQueryRefine14}.
+We therefore refine the given query using NL approaches before querying the code search engine.
+For each queried term, we perform stemming to remove derivational affixes using Porter stemmer\cite{porter:stemmer} (e.g., parsing$\rightarrow$parse).
+\textit{and identify salient terms (verbs, nouns, and adjectives) using a POS tagger~\cite{postagger04:stanford}.
+We choose these terms because prior work shows that they are salient elements in the query and other terms such as proposition, conjunction, and pronoun always impact query performance~\cite{Hill:NLQueryRefine14}.
+For example, the proposition \codefont{in} always matches the term \codefont{plugin}, leading to a false positive result).
+}
+To achieve better search result, we leverage  WordNet to generate English synonyms (e.g., \codefont{inquire} and \codefont{query}) and software-specific word thesaurus~\cite{yangMSR12:semWord, SEWordSim:ICSE14} to identify semantically-related terms (e.g., \codefont{source} and \codefont{target}).
+Our  approach is similar to other \textit{automatic query refinement} approaches, which have shown up to 41\% improvement in precision and 30\% increase in recall~\cite{lopes:queryExpand14, Marcus:queryReform13}.
+Our preliminary study also shows that our query refinement approach works well to extract more related code examples.
+For instance, code search engine returns nothing for the query \codefont{inspect hard-drive for music files}, yet when we refine the query using  the synonym of the term \codefont{inspect}---\codefont{check}, we successfully obtain 10 related code examples.
 
-\noindent{\textbf{Query Code Search Engine.}}  We use code search engine SearchCode~\cite{SearchCode} to extract code examples based on free-form queries from users.
-We choose it because 1) it has good support for free-form queries,  2) it is an open source code search engine with over 7000 projects from  Github, Bitbucket, Google Code, and Sourceforge, 3) it has complete API documentations and returns.
+\noindent{\textbf{Locate Queried Features.}}  Considering that source code examples are always entangled with multiple features, we separate program elements that are related to the queried features from big code examples.
+We do not cluster code examples based on the entire code example because it leads to too much noise in our preliminary study shown in Table~\ref{tab:preStudy}.
+For instance, one of the code examples for the query `\codefont{undo redo TextEditor}' contains 10 inner classes with 1447 lines of code: \codefont{CopyAction, PasteAction, MoveAction,..., UndoAction, RedoAction}, and only the last two inner classes (147 lines) are related to the queried feature.
 
-\noindent{\textbf{Locate Queried Features.}}  Considering that source code examples always contain multiple features, we identify program elements that are related to the queried features.
-I use the mean of TF-IDF weight  for each query term as a weighting factor and select all methods whose weighting score is bigger than a threshold.
+There exist a variety of feature location approaches based on IR approach, dynamic execution trace, and historical information.
+We adopt a plugin mechanism and select an IR approach similar to~\cite{Marcus:LSI04}.
+ We extract type names, method calls, and  identifier names, split them  into tokens using Samurai identifier splitting approach~\cite{samurai:msr09}, and convert each method into a document of Latent Semantic Index (LSI) space using an off-the-shelf tool call Semantic Vector~\cite{semanticVector:10}.
+\textit{Existing corpus-based feature location tools always leverage comments or even informal documents for feature location, but we only use reliable information from code elements because web-based code search engine provides us a fruitful of code examples.}
+The user query is also converted to a document of LSI space.
+We measure the  LSI similarity between user query and each method to identify query-related methods.
+We set  a threshold for LSI similarity score to include all related methods for the given query and filter out unrelated elements.
+%I use the mean of TF-IDF weight  for each query term as a weighting factor and select all methods whose weighting score is bigger than a threshold.
 This approach is similar to prior works that use  IR~\cite{Denys:FCA12} and NL analysis~\cite{Hill:FindConcept07} for feature location.
@@
 TF-IDF =  $avg( \log (1 + f_{t,d}) \times  \log \frac {N} {n_t}), f_{t,d}$ is the frequency of term $t$ in method $d$, $N$ is the total number of methods, $n_t$ is the number of methods that have the term $t$.
+
+\noindent{\textbf{Cluster Extracted Features.
+}}  After extracting queried features from each code examples, we automatically cluster search results using Latent Dirichlet allocation (LDA).
+LDA is a generative  model to express each document as a probability distribution of topics, and each topic is a probability distribution of words.
+Words can belong to multiple topics and documents can contain multiple topics.
+We use a popular topic modeling toolkit called MALLET~\cite{McCallumMALLET} to train topic model.
+To find a near-optimal LDA configuration (the number of topic, Dirichlet prior on the per-topic word distribution, etc), we reimplement a simple Genetic-Algorithm according to~\cite{Denys:LDAGA13} for each query task.
+We set the maximum number of topics $k$ as 9 following Miller's law in cognitive psychology~\cite{Miller:72}.
+We present the generated topics to users, so that user can select the example clusters they prefer.
+Hindle et al.
+\/conducted a case study in Microsoft to investigate if the topics extracted from requirements were relevant to development feature~\cite{Hindle:topicModel12}, and their result shows that experienced developers who are familiar with features are comfortable to identify behaviors based on topic words.
+We hypothesize that our users can also identify expected behavior based on topic words.
+User can choose to view more words in a topic to help them identify which topic they prefer.
+As shown in Table~\ref{tab:LDA}, if user prefers to implement a  \codefont{java.swing.TextEditor} that supports undo/redo action, she may choose Topic 1 because it contains keyword \codefont{viewer, action, listener} which seems related; yet if she wants to implement a TextEditor for a Eclipse Plugin, Topic 7 is the most promising one because of the keyword \codefont{workbench, plugin}.
+
+\begin{table}
+\begin{center}
+\caption{Clustering Result }
+\label{tab:LDA}
+\vspace{1mm}
+\scriptsize{
+\begin{tabular*}{0.5\textwidth}{@{}l|l|rrr@{}} \hline
+ \multicolumn{3}{c}{Query: `\codefont{undo redo TextEditor}' } \\ \hline
+ Topic&Topic Words &\# E\\\hline
+ 1&viewer undo manager redo action listener provider& 17\\
+2&selection event undo change redo builder target& 14\\
+3&action factory editor undo redo constants text bars & 23\\
+4&editor text menu action site group page & 18\\
+5&document string outline file command set java &8\\
+6&undo manager context operation element tab history &8\\
+7&undo redo workbench listener shared plugin tool&6\\ \hline
+ \multicolumn{3}{c}{Query: `\codefont{track mouse hover}' } \\ \hline
+Topic&Topic Words &\# E\\\hline
+1&mouse hover property handler  event drag data&13\\ 
+2&mouse component object key select item component &11\\
+3&track mouse scene parent node local client &4\\
+4&mouse bound height width series listener native &11\\ \hline
+\end{tabular*}
+ \label{tab:dataset}
+ {\# E}: the number of Examples
+}
+ \end{center}
+\end{table}
+
+%The Resource Description Framework (RDF) [26] is the data-model for representing meta-data in the Semantic Web.
+The RDF data-model formalizes meta-data based on subject ?
+predicate ?
+object triples, so called RDF statements.
+
+\subsection{Example Skeleton Generation Phase}
+
+We take three steps in this phase.
+For the selected code example cluster, we  first extract type facts for the located methods that belong to the queried feature.
+For each example in each cluster, we identify main facts that are shared among all examples, and perform slicing to identify related methods as auxiliary feature.
+Finally, we rank the related elements and select the best-fit one to generate a reusable code example skeleton with common facts.
+Our tool also enables users to drag and drop other auxiliary features to generate desired code example.
 
@@
 
-%The Resource Description Framework (RDF) [26] is the data-model for representing meta-data in the Semantic Web.
-The RDF data-model formalizes meta-data based on subject ?
-predicate ?
-object triples, so called RDF statements.
+ \noindent{\textbf{Extract Example Skeleton.}}
 
-\subsection{Example Clustering Phase.}
-
-We take three steps in this phase.
-Based on the type facts extracted from partial program analysis, we first cluster similar code examples based on the number of shared class-level facts and API calls (i.e.,  \codefont{call} facts) to reduce the duplicated code snippets.
-Next, for each example in each cluster, we identify main facts that are shared among all examples, and perform slicing to identify related elements.
-Finally, we group auxiliary features based on program slicing and lexical similarity.
-
-\noindent{\textbf{Cluster Examples.}}   We greedily select the most suitable structural correspondence~\cite{Cottrell:jigsaw08} and propagate the similarity of {\it object} nodes to the {\it subject} node.
+ We greedily select the most suitable structural correspondence~\cite{Cottrell:jigsaw08} and propagate the similarity of {\it object} nodes to the {\it subject} node.
 
@@
 
- Next, we try to match the fact   \codefont{(actionPerformed, calls, updateUndoState())}.
+We try to match the fact   \codefont{(actionPerformed, calls, updateUndoState())}.
 Knowing that there is an edge from \codefont{updateUndoState()} to \codefont{setEnabled(undo.canUndo()} in RDF graph, we recursively match the fact \codefont{(updateUndoState, calls, setEnabled(undo.canUndo()))}  with  \codefont{(actionPerformed, calls, setEnabled(undo.canUndo()))}.
@@
 
-Finally, the examples are clustered based on the number of  {\it object} nodes (without outer edge).  Our tool keeps on refining the large cluster to present a structured code examples to developers.
+%Finally, the examples are clustered based on the number of  {\it object} nodes (without outer edge).  Our tool keeps on refining the large cluster to present a structured code examples to developers.
 
-\noindent{\textbf{Extract Example Skeleton.}}  We extract all matched {\it object} nodes (without outer edge) and use them as  match seeds.
-We then perform dependency analysis to  extract example skeleton.
+We extract all matched {\it object} nodes (without outer edge) and use them as  match seeds.
+
+\noindent{\textbf{Rank Related Elements.}}   
+ We perform dependency analysis to  extract example skeleton.
 An example skeleton should start from an element without any inner edge and end at an element without any outer edge which covers all match seeds.
-
 When selecting features, we use three rules to rank features in different examples: 1) the cost of reuse; 2) the number of resolved relationship; 3) the frequency of the feature in multiple examples; 4) the simplicity of code implementation.
-
 The cost of reuse is measured as the number of outer edges in RDF graph, i.e., the more outer edges in RDF graph, the more expensive to reuse because it has more dependencies.
@@
 When user tries to reuse the example, they have to manually resolve these external relationships.
-For instance, in Figure~\ref{fig:cluster2} (D), the feature group B.1 (\codefont{mUndoAction = new LintEditAction(undoAction, getEditorDelegate().getEditor())}) is not selected because the class \codefont{LintEditAction} cannot be resolved based on this partial program.
+
+For instance, in Figure~\ref{fig:cluster2} (D), the feature group B.1 (\codefont{mUndo Action = new LintEditAction(undoAction, getEditorDelegate().getEditor())}) is not selected because the class \codefont{LintEditAction} cannot be resolved based on this partial program.
 The first two rules ease the reusability of our suggested code example.
@@
 The simplicity is measured as the length of the code.
-For instance, we prefer \codefont{actionBars.setGlobalActionHandler (ITextEditorActionConstants.UNDO, undo)} in Figure~\ref{fig:cluster24} (D) than \codefont{actionBars.setGlobalActionHandler (ITextEditorActionConstants.UNDO, getAction((ITextEditor) part,  ITextEditorActionConstants.UNDO))} because the former one is easier to interpret.
+For instance, we prefer \codefont{actionBars.setGlobalActionHandler (ITextEditorActionConstants .UNDO, undo)} in Figure~\ref{fig:cluster24} (D) than \codefont{actionBars.setGlobal ActionHandler (ITextEditorActionConstants.UNDO, getAction((ITextEditor) part,  ITextEditorActionConstants.UNDO))} because the former one is easier to interpret.
 
-\noindent{\textbf{Group Auxiliary Features.}}    The auxiliary features are different example  skeletons.  (TBD)
-
-\noindent{\textbf{Enable User Interaction.}}    The user could select the features and our tool is able to extract related elements based on their selection. (TBD)
+\noindent{\textbf{Enable User Interaction.}}  Apart from the selected best-fit related program elements, our tool also lists a fuzzy set of suggested program elements that can be added into the example skeleton.
+Users can drag-and-drop their preferred features to the code skeleton and our tool is able to select related program elements associated with this feature to fill in the skeleton.
+For instance, in Figure~\ref{fig:cluster2} (D), if user wants to add \codefont{propertyChange()} methods into the code skeleton, our tool will add super interface \codefont{PropertyChangeListener} to both \codefont{UndoAction} and \codefont{RedoAction} based on RDF graph, which are tagged as \codefont{B.4} in Figure~\ref{fig:cluster2} (D).
 

### 2015-11-02 proposal/abstract.tex
abstract 11-2

\begin{abstract}

Developers need to find bugs, search for code examples, and assess the compatibility of code examples before integrating them into the user context. There exist three problems: (1)  Misleading identifiers can lead to bugs that are hard to find; (2) Code examples returned from existing code search engine are unstructured; (3) It is hard to assess which code example can be correctly integrated into the user context.  Existing approaches that support bug location, code search, and code reuse use either code structure or naming semantics, but few approaches effectively combine both code structure and naming semantics together. This thesis investigates the synergy between naming semantics and code structure to help find more bugs based on naming inconsistency, group code examples in a structured manner, and proactively assess the compatibility between code examples and the user context to help developer integrate the example to the target context.

To investigate this hypothesis, we design a bug finding technique that leverages naming dialects in conjunction with purity and type usage analysis. Our evaluation illustrates that inconsistent names found by our tool are strongly correlated with defects in the version history. Second, we propose a new clustering approach for code search results to assist developers comprehend related search results and investigate the commonality between these search results in a structured manner. We propose to use both user study and similar feature requests from version history to evaluate the usability and accuracy of our clustering approach. Third, we propose a speculative approach  to support code reuse tasks by proactively assessing the compatibility between code examples and the user context.

This proposal has the potential to improve software correctness and program comprehension by leveraging both code structure and naming semantics in several software engineering activities.

%We design a bug finding technique to identify naming dialects in conjunction with purity and type usage analysis. 
%We hypothesize that we can improve existing code-structure analysis tools by leveraging semantic information, and vice versa. Based on this hypothesis, we propose to explore the synergy between code structure and program semantics using three case

\end{abstract}

### 2015-11-02 proposal/graph-time.tex
abstract 11-2

\begin{figure*}[!htb]
    \begin{minipage}{0.49\textwidth}
     \centering
 \includegraphics[width=1\textwidth]{fig/fixRateIntroduce.jpeg}   
     % \scriptsize{C-I represents the group of methods that add new inconsistent names; 
%       
%C-C represents the group of methods without inconsistent names that remain the same during the observation period.}
  \end{minipage}
  \hfill
     \begin{minipage}{0.49\textwidth}
     \centering
 \includegraphics[width=1\textwidth]{fig/fixRateRemove.jpeg}  
   %    \scriptsize{I-C represents the group of methods that remove inconsistent names; 
%      
%I-I represents the group of inconsistent name methods that remain as inconsistent name methods during the observation period; }
    \end{minipage}

      \begin{minipage}{1\textwidth}
           \centering
           \scriptsize{
 \begin{tabular}{l|rr|rr} 
 {Fix rate change {\bf before} ($<0$) vs.~{\bf after} ($>0$)}&  \multicolumn{2}{c|}{Introduction of inconsistent names} & \multicolumn{2}{c}{Removal of inconsistent names}\\
Inconsistent names are added/deleted at Revision 0& Mann-Whitney&Cliff Delta& Mann-Whitney&Cliff Delta\\ \midrule
C-I: methods that inconsistent names are introduced&$p<0.01$&$-0.35$(m)&$p<0.01$&0.48(l)\\ 
I-C: methods that inconsistent names are removed&$p<0.01$&$-0.39$(m)&$p<0.01$&0.35(m)\\ 
I-I: methods with inconsistent names&$p=0.18$&N/A&$p=0.10$&N/A\\ 
C-C: methods without inconsistent names&$p=0.21$&N/A&$p=0.24$&N/A\\ 
 \end{tabular}

 m:medium;  l:large
 }
    \end{minipage}
       \vspace{-3mm}
     \caption{Fix rate change before and after introducing/removing inconsistent names}
   \label{fig:rateChange}
      \vspace{-3mm}
\end{figure*}

### 2015-11-02 proposal/intro.tex
abstract 11-2

\section{Introduction}

\paragraph{Problem}

Developers spend a lot of effort understanding programs. Considering that software documentation can be out of date or does not exist at all, developers need code to be self-explanatory. Therefore, developers are encouraged to assign meaningful semantic names to program elements. Prior study has shown that naming matters from two aspects: 1) poor code convention can do harm to code comprehension~\cite{buse:readability, butler:csmr10, boogerd:icsm08}. 2)  semantic information is effective to solve some complicated problems in program analysis such as code search~\cite{Denys:portfolio11,  lopes:usageSimFSE10, RecoDoc:ICSE12} and   feature location~\cite{Denys:TSE12, sniafl:TSE06, Hill:locateConcern07}.

We explore the synergy between semantics   investigate several areas that

### 2015-11-02 proposal/preliminary.tex
abstract 11-2

\section{Preliminary Work}

We build a tool to automatically mines project-specific naming rules and analyze if the naming inconsistency indicates poor code quality.

Our Naming Inconsistency CHEcker called \niche infers naming rules based on two key insights: (1) {\it pure} and {\it impure} method names should reflect their purity property. (2) Objects with similar functionality should share similar names.

To detect inconsistent method names, \niche leverages purity analysis to identify pure methods and classifies the rest as impure ones. If a method does not mutate externally visible heap state, its parameters are read-only, and it does not create any new externally visible heap paths to objects transitively reachable from the parameters, we classify it as {\it pure} methods and mine its name for {\it pure} terms.  For example, in the project \codefont{Apache Accumulo}, \niche classifies the verb `{\it accept}' as a pure terms based on its relative occurrence in pure vs. impure methods. If an impure method in the same project uses `{\it accept}', \niche regards it as anomaly, because it volates the purity property associated with the term for the same project.
To identify inconsistent object names, \niche implements type-use pattern analysis similar to Wasylkowski et al. \/ \cite{zellerfse07:usageAbnormal}. For each object within each method, \niche use a def-use analysis to extract a sequence of statements that read from or write to the objects or invoke methods on it. It then clusters similar type-use patterns and identifies object names that deviate from commonly used object names. For instance, if the variable of type \codefont{FlushRequester} is named \codefont{requester} with one exception of \codefont{listener}, \niche reports the anomaly as naming inconsistency.

To assess \niche's accuracy, we manually construct a ground truth of inconsistent names and compare it with the inconsistent names reported by \niche. We select the best setting based on F-measure with 81\% precision and 88\% recall for purity analysis as well as 89\% precision and 78\% recall using type-use pattern analysis.

To investigate if programs share a consistent naming dialect or have project-specific dialects and if inconsistent identifiers indicate poor code quality, we use \niche to identify inconsistent names in 39 Java projects from Apache Software Foundation, which are highly active projects with well-defined code convention and rigorous code review process using JIRA issuing tracking system. We collect actual defects from commit histories based on Fischer et al.'s method~\cite{Fischer:versionICSM03}  to search for commit messages with valid bug report references (e.g., ``HDFS \#4702'').  We answer four research questions:

\paragraph{Is naming inconsistency project-specific?} Prior works report poor names based on hard-coded naming rules, These tools assume that different projects share the same naming conventions and use similar lexicons. However, each project may use the same naming dialects in different ways. We hypothesize that the naming rules may conflict among different projects and therefore naming inconsistency should be performed on per-project basis.

For purity analysis, we create a lexicon of pure terms and impure terms in each project, and compare the lexicons. If the same pure and impure term is shared among two or more projects, we regard it as a {\it corpus-wide} rule; otherwise it is classified as {\it project-specific rules}. If a pure term in one project is impure in another project, we classify it as a {\it conflicting} rule. For type-use pattern analysis, we create a set of object names for each type-use pattern. If the same type-use pattern is shared by two or more projects. we classify it as {\it corpus-wide} type-use pattern, otherwise it is {\it project-specific}.

Our result shows that only 32\% of pure terms and 33\% of impure terms are corpus-wide terms that are commonly shared by two or more projects. The rest terms are project-specific, accounting for over 41\% of all inconsistent method headers. More than 790 terms are conflicting, which is 33\% of pure terms and 31\% of impure ones. For instance, one detected conflicting terms is \codefont{need}, which is only used by pure methods in project \codefont{Apache Jackrabbits}, but only used by impure methods in project \codefont{Apache Accumulo}. We observe similar results for type-use pattern analysis, in which project-specific rules account for all 100\% of identified inconsistent object names because similar type-usage patterns are rarely shared across different projects (0.1\%).

Our results indicate that naming is often project-specific. If projects use conflicting rules, existing hard-coded naming rules will miss them. Our results shows that corpus-wide rules miss over 41\% of inconsistent names.

\paragraph{Are inconsistent names correlated with bug fixes?}

Developers place a significant emphasis on good naming in software, because meaningful names can improve software readability and maintainability to facilitate programmer communication. However, no prior empirical study systematically evaluates whether inconsistent and confusing names are correlated with actual bug fixes in revision history. We therefore examine the correlation between actual defects and inconsistent names found by \niche.

To investigate if inconsistent names are correlated with bug fixes, we group methods into two sets: methods with inconsistent names either in header or body ($I$), and methods with bug fixes during the study period ($F$). We first check if inconsistent names are independent with Chi-Square test with p-value $<0.01$. We reject the null hypothesis and confirm that bug fixes and inconsistent names are correlated.  We then compute the conditional probability of bug fixes given inconsistent names $P(F|I)$ and compare it with the probability of bug fixes given no inconsistent name $P(F|\neg I)$. Similarly, we compute the conditional probability of inconsistent names given bug fixes $P(I|F)$ and compare that against the probability of inconsistent names given no bug fixes $P(I|\neg F)$.

The results indicate that inconsistent names are more likely to experience bug fixes than methods without: $P(F|I)=0.64$ vs.  $P(F|\neg I)=0.50$. Inconsistent names are more likely to appear in buggy methods than bug-free ones: $P(I|F)=0.11$ vs. $P(I|\neg F)=0.07$. We also perform this analysis at the file level and find a more significant difference:   $P(F|I)=0.75$ vs.  $P(F|\neg I)=0.45$ and $P(I|F)=0.24$ vs. $P(I|\neg F)=0.11$.

\begin{table}[@{}ht]
 \begin{minipage}{.5\linewidth}
\begin{center}
\vspace{-4mm}
\caption{ Inconsistent name methods}
\label{tab:avgIN}
\scriptsize{
\begin{tabular}{@{}l|rcrr@{}}  
\multirow{2}{*}{Group} &\multirow{2}{*}{\#Total}&Average&Average&Average \# \\ 
&&fix rate&\# fixes&other changes\\ \midrule
$|I|=0$ &232,406&17\%&0.34&1.93\\
$|I|=1$ &23,217&22\% &2.66&4.81\\
$|I|>1$ &106& 25\% &5.23&8.48\\ 
\end{tabular}
}
\vspace{-6mm}
\end{center}
\end{minipage}
 \begin{minipage}{.5\linewidth}
 \begin{center}
\vspace{-4mm}
\caption{Callers of inconsistent name methods}
\label{tab:avgInvoke}
\vspace{1mm}
\scriptsize{
\begin{tabular}{l|rcrr}  
\multirow{2}{*}{Group} &\multirow{2}{*}{\#Total}&Average&Average&Average \# \\ 
&&fix rate&\# fixes&other changes\\ \midrule
$|C|=0$ &196,726& 19\% & 0.45&2.07\\
$|C|=1$&57,796&25\% &0.88&2.58\\
$|C|>1$&1,207& 27\% &1.35&4.89\\ 
\end{tabular}
}
\vspace{-6mm}
\end{center}
 \end{minipage}
\end{table}

\input{graph-time}

Table~\ref{tab:avgIN} represents average bug fix rate ($\frac{\#fix_revision}{\#revision}$) for methods with no inconsistent names ($|I|=0$), one inconsistent name $|I|=1$, and multiple inconsistent names ($|I|>1$). Methods without inconsistent names have a lower fix rate than methods with one inconsistent name (17\% vs. 22\%), and than those with multiple inconsistent names (17\% vs. 25\%). the Mann-Whitney test illustrates that  the three method groups are significant different from  each other (p-value$<0.01$).

To support our hypothesis that inconsistent names are strongly correlated with defects, we investigate how the introduction and removal of inconsistent names affects a bug fix rate. Figure~\ref{fig:rateChange}  illustrates a bug fix before and after the addition or deletion of inconsistent names using a sliding time window.  We separate the methods into four groups: (1) C-I: methods that were consistent before and become inconsistent. (2)  I-C: methods that were inconsistent before and became consistent. (3) I-I: methods that stayed inconsistent.  (4) C-C: methods that stayed consistent. 
For the method group C-I, the average fix rate 0.5\% within 10 revisions before the introduction of inconsistent names is 0.50\%, while this rate within 10 revisions after the introduction of inconsistent names is 0.71\%. This indicates that more defects occur after introducing inconsistent names. We use Mann-Whitney test to check if the difference is significant, and use Cliff's delta effect size to evaluate how big the difference is. We observe a significant fix rate increase after introducing inconsistent names (p-value$<0.01$). Using a similar approach, we find that the fix rate decreases significantly after deleting inconsistent names.

To investigate whether the confusion caused by inconsistent names propagates to their callers, we compare the average bug fix rate for methods calling no inconsistent methods ($|C|=0$), one inconsistent name method ($|C|=1$), and multiple inconsistent name methods ($|C|>1$), as shown in Table~\ref{tab:avgInvoke}. The bug fix rate for each method group is 19\%, 25\%, and 28\%, indicating that the more inconsistent name methods are called, the more confusion may occur, making the caller methods more defect prone.

 These results indicate that naming inconsistency may correlate with defects, yet it is unknown whether developers find inconsistent names particularly problematic and remove them faster than other names. To answer this question, we calculate the lifespan for each identifier by identifying the first revision in which it is introduced and the last revision in which it is removed. If a name is never removed, we treat the latest revision as the ending revision. We compare the lifespan of inconsistent names with other names and use Mann-Whitney test and Cliff's delta effect size to measure if there is any difference and how significant the difference is. 
We separate methods, fields, parameters, and local variables since they are likely to have different lifespans. Our results indicates that inconsistent  names disappear significantly faster than other names.

\paragraph{Is naming inconsistency significant with respect to other factors?}  To understand whether and how much naming inconsistency plays a role in assessing defects among other software quality metrics such as code complexity, lines of code, and churn~\cite{nagappan:metricsICSE06, Menzies:metricsTSE07}, we conduct multivariate linear regression analysis and measure the impact of each metrics. Without loss of generality, we select 9 method-level code metrics from Nagappan et al.'s approach~\cite{nagappan:metricsICSE06}: code churn, LOC, the number of developers who edited each method, McCabe complexity~\cite{McCabe:complexity76}, fan out, fan in, the number of parameters, the number of field reads, and the number of field writes. 
Using Spearman rank correlation between the number of defects and individual software metrics, we reject three variables \{LOC, \# FieldWrite, \#Developers\} with $p>0.01$. To investigate how much the remaining factors influence defects, we use a forward and backward stepwise regression to reduce the number of variables in the model. The result illustrates that the metrics \textit{inconsistent name} has a positive coefficient in the model, indicating that the more inconsistent names, the more defects a program may have,

Finally, we measure the deviance for each factor using ANOVA (analysis of variance) to measure the impact of variables. The result indicates that though naming inconsistency is not the most significant factor correlated with defects, it contributes to assess software quality even among other confounding factors.

%The findings for the previous two questions illustrates correlation with defect not causation. We further investigate other software quality metrics that may affect defect rates, 
% To identify if inconsistent and confusing names are correlated with actual defects found in commit histories.

In summary, our analysis yields several insights: 1) Naming dialects are largely project-specific. More than 67\% of naming rules are project-specific and these project-specific rules account for 41\% of inconsistent methods names from purity analysis and 100\% of inconsistent  object names from type-use pattern analysis. 2) Methods with inconsistent names and methods that invoke them both experience more bug fixes than other methods and the bug fix rate increases after the introduction of inconsistent names. 3) Inconsistent names have shorted lifespans than other names, which indicates that inconsistent names are more likely to be renamed compared to other names. 4) Compared with other software quality metrics, naming inconsistency is not the dominant factor, but it does influence software quality.

### 2015-11-02 proposal/related.tex
abstract 11-2

\section{Related Work}

\paragraph{Corpus-wide Naming Rules}  Abebe et al.\/ investigate identifier quality  based on a catalog of Lexicon Bad Smells~\cite{abebe:wcre12}. 
Caprile and Tonella leverage pre-defined syntax and identifier dictionary to replace terms with their synonyms to ensure naming consistency~\cite{caprile:reconstruct}. Dei{\ss}enb{\"{o}}ck and Pizka proposed a formal model for concise and consistent naming, which requires a mapping from a concept domain to a lexical domain~\cite{ccnames:Pizka06}. Lawrie et al.\/ use hard-coded naming rules such as \textit{an identifier should not include another identifier in its name}~\cite{syntacticcc:SCAM06}.  Arnaoudova et al.\/ define a family of linguistic anti-patterns such as \textit{set* methods should not return an object} and investigate misunderstanding caused by anti-patterns~\cite{antipattern:CSMR13}. None of these approaches detect project-specific naming inconsistency.  
Allamanis et al. \/ build a tool called Naturalize to learn and enforce coding conventions~\cite{birdfse14:convension}. It uses n-gram based statistical natural language processing model to suggest natural identifier names and formatting conventions at the level of type names, method calls, and variable names. 
%  The only overlapping target in scope is the variable name recommendations reported by Naturalize. We run Naturalize on the same 39 projects using its default settings and compare variable name reports. We use a few examples to illustrate the difference between \niche and Naturalize. Naturalize misses inconsistent object names such as `\codefont{repStore}', which violates the commonly used name pattern (`\codefont{*FS}') found by type-use pattern analysis in \niche. On the other hand, Naturalizes suggests renaming `\codefont{local\_folder}' to `\codefont{localFolder}'. \niche does not produce such naming suggestion, as it focuses on checking name consistency based on the code's semantic functionality.
H{\o}st et al. \/ build a tool called Lancelot to find poor method names by comparing syntactic code features, such as `\textit{contains a loop}'~\cite{nameBug:ECOOP09} .  
%The only overlapping scope for Lancelot and \niche is the inconsistent method names found by \niche and the `\textit{method naming bugs}' from Lancelot. Lancelot misses inconsistent method names such as `\codefont{setSyncFlag}' which does not change the field value because it checks syntactic features only without considering the purity of a method. Lancelot reports  `\codefont{setExit}' method as a naming bug, since it returns the object itself (\codefont{return this}), but in this case, \niche classifies it as consistent because the method is impure. 
Buse and Weimer develop a readability metric for Java by training data from human annotators~\cite{buse:readability}. They find that their readability metric exhibits a significant level of correlation with static analysis warnings found by FindBug~\cite{FindBug:OOPSLA06}. Though their work connects the readability of identifier names to  static analysis warnings, they do not study the correlation between inconsistent names and bug fixes.

\paragraph{Defect Study}  Abebe et al.\/ find correlation between naming rule violations and  coupling metrics~\cite{abebe:wcre12,ckmetrics:oopsla91}. Butler et al.\/ find correlation between FindBug's static analysis warnings and violations of hard-coded rules~\cite{FindBug:OOPSLA06,butler:csmr10}. Since static analysis tools suffer from 30\% to 100\% false positive rates~\cite{kremenekWarn:fse04}, we cannot conclude whether naming inconsistency is correlated with actual defects. Boogerd et al.\/ find that only 10 out of 88 hard-coded naming rules have positive correlation with defect density~\cite{boogerd:icsm08}. We differ from prior studies by mining rules from a corpus and studying how these rule violations relate to actual defects. Our study also finds that the confusion and misunderstanding caused by inconsistent name may propagate to their callers and that the lifetime of inconsistent names is shorter than the rest.

%\paragraph{Mining Usage Patterns}

\paragraph{Feature Location} Poshyvanyk et al. \/ use information retrieval approach to locate a queried feature in source code~\cite{Denys:FCA12}. They  evaluate the similarity between documents and user query and cluster the source code based on formal concept analysis.  Portforlio~\cite{Portfolio:DenysICSE11} and Export~\cite{Export:DenysASE13} identify related functions by combining both latent structure similarity and lexical information similarity. Our feature location approach is similar to~\cite{Portfolio:DenysICSE11} yet we focus on suggesting structured implementation for the feature rather than identify feature location.
Rastkar et al. \/ summarize the structure of multiple instances of a crosscutting concern in natural language, yet they only extract structural facts in the level of method signature and class hierarchy~\cite{Murphy:nlConcern11}. We make it one step further to suggest structured feature implementation based on  user query.

\paragraph{Code Search} Our example clustering approach is similar to some prior works that extract representative examples for specific APIs or user query. 
MAPO~\cite{MAPO:ECOOP09} leverages frequent call sequences to cluster the usage of specific APIs and rank abstract usage patterns based on the context similarity. Buse et al\/\cite{Buse:apiICSE12} propose to generate abstract API usages by synthesizing code examples using symbolic execution for a particular API. Different from these works that generate abstract usage patterns for specific API or data type, SNIFF~\cite{sniff:Sen09} performs type-based intersection of code chunks based on the keywords in the free-form query and cluster the common part of the code chunks for concrete code examples. However, these works   only focus on providing code examples based on the popularity or textural relevance while developers have to manually resolve structural dependencies before reusing the examples.  MUSE~\cite{MUSE:MarcusICSE15} addresses this limitation using slicing to generate concrete usage examples and selects the most representative ones based on the popularity and readability while  Keivanloo et al\/\cite{spotWork:ICSE14} uses clone detection to cluster examples involving loops and conditions.  There exists a number of code example suggestion tools that recommend call chains~\cite{Mandelin:jungloid05, parseWeb:ASE07, Xsnippet:OOPSLA06}  or contexts~\cite{Holmes:structural05, Prompter:MSR14}. But none of  these tools presents code example in a structured manner and identify  common features for each code example cluster, which helps developers to reuse the code examples.

%only recommend code examples in the method level which make them insufficient for  reuse tasks across multiple classes.   We make it one step further to  identify  both common features and alternative features.

\paragraph{Code Reuse}  Although some approaches advocate refactoring code rather than reuse code~\cite{fowler:refactoring}, recent researches have found that these kind of `clone' cannot be easily refactored~\cite{Kim:cloneGenealogy05} and have to be modified to meeting requirements in new context~\cite{Selby:largeReuse05}.  Jigsaw~\cite{Cottrell:jigsaw08} supports small-scale integration of source code into target system  between the example and target context. Based on its ancestor~\cite{Cottrell:generalize07} that identifies structural correspondence based on AST similarity, it greedily matches each element between two contexts, transforms correspondent elements to the target context, and simply copies the source element to the target if it does not correspond with any element in the target. Unfortunately, developer has to provide source and target to enable a one-to-one transformation and resolve all dependencies when pasting code to the target.  Our approach overcomes these two limitations: we extract common functionalities from multiple examples and  identifies how related elements interact with main features.  Other works on code reuse include
Gilligan~\cite{Holmes:reuse07} and Procrustes~\cite{Holmes:ASE09} which try to address the problem of source code integration in the context of medium or large-scale reuse tasks. They automatically suggest program elements that are easy to reuse based on structural relevance and cost of reuse in the source context, and guide users to investigate and plan a non-trivial reuse task. They assume that developers have a perfect example at hand, and they can finish the reuse task by resolving all dependency conflicts and integrating the example to the desired context.  We don't have this assumption and our tool helps users identify the best-fit example. Our idea of leveraging multiple examples to discover commonality is similar to LASE~\cite{LASE:ICSE13}, which applies similar but not identical changes to multiple code locations based on context similarity.   Our approach works in a similar manner of Programing-by-Example in the context of code reuse task. LASE requires users to specify multiple input examples and search for the third one, while our approach uses free-form queries to obtain hundreds of examples and cluster them based on their common features.

%focuses on a task-based code reuse across different methods or even different classes, while LASE is confined to the systematic edit within a single method and requires users to specify all input examples.

%However, we note that it is not easy to identify a good example as an example is always interleaving with other auxiliary features that should not be integrated. We observe that it is equally difficult, if not more so, to distinguish the major functionality and auxiliary ones from multiple examples than to identify related elements in a pragmatic reuse plan. We target the problem to identify the major features across different reusable examples and leverage Procrustes to evaluate the cost of reuse when recommending the best-fit reusable plan.

### 2015-11-17 weeklyReport/appendix.tex
init 11-17

@@
-\begin{figure*}[!htb]
- \begin{minipage}{1\textwidth}
-\scriptsize 
-\begin{tabular}{@{}p{1\textwidth}} 
- \hline
+\input{example-purity}
 
-  \multicolumn{1}{c}{Result 7: PaparusCDTEditor} \\ \hline
-  \vspace{-4mm}
-\begin{Verbatim}[commandchars=\\\{\}, tabsize=2]
-public class PapyrusCDTEditor extends CEditor \{
- protected IAction gmfUndo, gmfRedo;
- protected IAction textUndo, textRedo;
- @Override
- public void createPartControl(Composite parent) \{
-  IActionBars actionBars = getEditorSite().getActionBars();
-  if((actionBars != null) && (gmfUndo == null)) \{
-   gmfUndo =  \uwave{actionBars.getGlobalActionHandler(ITextEditorActionConstants.UNDO)};
-    gmfRedo =  \uwave{actionBars.getGlobalActionHandler(ITextEditorActionConstants.REDO)};
-  \}
-  super.createPartControl(parent);
-  if(actionBars != null) \{
-   textUndo = actionBars.getGlobalActionHandler(ITextEditorActionConstants.UNDO);
-   textRedo = actionBars.getGlobalActionHandler(ITextEditorActionConstants.REDO);
-    \uwave{actionBars.setGlobalActionHandler(ITextEditorActionConstants.UNDO, gmfUndo)};
-    \uwave{actionBars.setGlobalActionHandler(ITextEditorActionConstants.REDO, gmfRedo)};
-   actionBars.updateActionBars();
-  \}
-  @Override
-  public ISourceViewer createSourceViewer(Composite parent, IVerticalRuler ruler, int styles) \{
-   final ISourceViewer viewer = super.createSourceViewer(parent, ruler, styles);
-   focusListener = new FocusListener() \{
-   public void focusLost(FocusEvent e) \{
-    if(isDirty()) \{
-     syncCpp.syncCDTtoModel();
-     Classifier classifier = (Classifier)papyrusTextInstance.getEditedObject();
-     doSave(new NullProgressMonitor());
-     SyncModelToCDT.syncModelToCDT(classifier);
-    \}
-     IActionBars actionBars = getEditorSite().getActionBars();
-     if(actionBars != null) \{
-      if((gmfUndo != null) && (gmfRedo != null)) \{
-       actionBars.setGlobalActionHandler(ITextEditorActionConstants.UNDO, gmfUndo);
-       actionBars.setGlobalActionHandler(ITextEditorActionConstants.REDO, gmfRedo);
-       actionBars.updateActionBars();
-     \} \} \}
-   public void focusGained(FocusEvent e) \{
-    IActionBars actionBars = getEditorSite().getActionBars();
-    if(actionBars != null) \{
-     if((textUndo != null) && (textRedo != null)) \{
-      actionBars.setGlobalActionHandler(ITextEditorActionConstants.UNDO, textUndo);
-      actionBars.setGlobalActionHandler(ITextEditorActionConstants.REDO, textRedo);
-      actionBars.updateActionBars();
-     \} \} \} \};
-  return viewer;
-\} \}
- \end{Verbatim}
-      \vspace{-4mm}
-     \\ \hline
-       \multicolumn{1}{c}{Result No.9,10: AspectEditorContributor} \\ \hline
-  \vspace{-4mm}
-\begin{Verbatim}[commandchars=\\\{\}, tabsize=2]
-public class AspectEditorContributor extends MultiPageEditorActionBarContributor \{
- private IEditorPart activeEditorPart;
- private AspectEditor aspectEditor;
- @Override
- public void setActivePage(IEditorPart part) \{
-  if (activeEditorPart == part)   return;
-  activeEditorPart = part;
-  IActionBars actionBars = getActionBars();
-  if (activeEditorPart != null && activeEditorPart instanceof ITextEditor) \{
-   IActionBars siteActionBars = ((IEditorSite)activeEditorPart.getEditorSite()).getActionBars();
-    \uwave{siteActionBars.setGlobalActionHandler(ITextEditorActionConstants.UNDO, getAction((ITextEditor)activeEditorPart, ITextEditorActionConstants.UNDO))};
-    \uwave{siteActionBars.setGlobalActionHandler(ITextEditorActionConstants.REDO, getAction((ITextEditor)activeEditorPart, ITextEditorActionConstants.REDO))};
-   siteActionBars.updateActionBars();              
-  \} else \{
-   if (part instanceof AspectEditor) \{  aspectEditor = (AspectEditor) part; \}
-   IWorkbenchPartSite site = aspectEditor.getSite();
-   if (site instanceof IEditorSite) \{
-    ITextEditor textEditor = aspectEditor.getMultipageEditor().getTextEditor();
-    IActionBars siteActionBars = ((IEditorSite) site).getActionBars();
-    siteActionBars.setGlobalActionHandler(ITextEditorActionConstants.UNDO, getAction(textEditor, ITextEditorActionConstants.UNDO));
-    siteActionBars.setGlobalActionHandler(ITextEditorActionConstants.REDO, getAction(textEditor, ITextEditorActionConstants.REDO));
-    siteActionBars.updateActionBars();              
- \} \}\}
- protected IAction getAction(ITextEditor editor, String actionID) \{
-   return (editor == null ? null : editor.getAction(actionID));
- \} \}
-   \end{Verbatim}
-      \vspace{-4mm}
-     \\ \hline
+\input{example-usage-new}
 
-\end{tabular} 
-\caption{Results from SearchCode CSE}
-\label{fig:undoEditor}
-\end{minipage}
-\end{figure*}
-
-\begin{figure*}[!htb]
- \begin{minipage}{1\textwidth}
-\scriptsize 
-\begin{tabular}{@{}p{1\textwidth}} 
- \hline 
-    \multicolumn{1}{c}{Result No 2,3.: AndroidTextEditor} \\ \hline
-  \vspace{-4mm}
-\begin{Verbatim}[commandchars=\\\{\}, tabsize=2]
-public abstract class AndroidTextEditor extends FormEditor implements IResourceChangeListener \{
- protected void createAndroidPages() \{
-  mIsCreatingPage = true;
-  createFormPages();
-  createTextEditor();
-  createUndoRedoActions();
-  postCreatePages();
-  mIsCreatingPage = false;
- \}
- private void createUndoRedoActions() \{
-  IActionBars bars = getEditorSite().getActionBars();
-  if (bars != null) \{
-    IAction action = mTextEditor.getAction(ActionFactory.UNDO.getId());
-    bars.setGlobalActionHandler(ActionFactory.UNDO.getId(), action);
-    action = mTextEditor.getAction(ActionFactory.REDO.getId());
-    bars.setGlobalActionHandler(ActionFactory.REDO.getId(), action);
-    bars.updateActionBars();
-  \}\}
- private void createTextEditor() \{
-   mTextEditor = new TextEditor();
-   int index = addPage(mTextEditor, getEditorInput());
-   mTextPageIndex = index;
-   setPageText(index, mTextEditor.getTitle());
-   IDocumentProvider provider = mTextEditor.getDocumentProvider();
-   mDocument = provider.getDocument(getEditorInput());
-   mDocument.addDocumentListener(new IDocumentListener() \{
-    public void documentChanged(DocumentEvent event) \{
-    onDocumentChanged(event);
- \}); \} \}
-\end{Verbatim}
-\vspace{-4mm}
- \\ \hline
-  \multicolumn{1}{c}{Result 4: DocumentUndoManagerImpl } \\ \hline
-  \vspace{-4mm}
-\begin{Verbatim}[commandchars=\\\{\}, tabsize=2]
-public class DocumentUndoManagerImpl implements DocumentUndoManager \{
- private static class UndoableTextChange extends AbstractOperation \{
- protected long fUndoModificationStamp = Document.UNKNOWN;
- protected long fRedoModificationStamp = Document.UNKNOWN;
- protected void reinitialize() \{
-   fUndoModificationStamp = Document.STAMP;
-   fRedoModificationStamp = Document.STAMP;
-  \}
- protected void undoTextChange() \{
-  try \{
-     if (fDocumentUndoManager.fDocument instanceof Document)
-         ((Document)fDocumentUndoManager.fDocument).replace(fStart, fText.length(), fPreservedText,fUndoModificationStamp);
-     else
-          fDocumentUndoManager.fDocument.replace(fStart, fText.length(), fPreservedText);
-            \} catch (BadLocationException x) \{
-   \} \}
- public boolean canUndo() \{
-   if (isValid()) \{
-    if (fDocumentUndoManager.fDocument instanceof Document) \{
-      long docStamp = ((Document)fDocumentUndoManager.fDocument).getModificationStamp();
-      boolean canUndo = docStamp == Document.STAMP ||  docStamp >= getRedoModificationStamp();
-      return canUndo;
-  \}
-  return false; 
-\}
-public IStatus undo() \{
-  if (isValid()) \{
-    fDocumentUndoManager.fireDocumentUndo(fStart, fPreservedText, fText, null, DocumentUndoEvent.ABOUT_TO_UNDO, false);
-    undoTextChange();
-    fDocumentUndoManager.resetProcessChangeState();
-    fDocumentUndoManager.fireDocumentUndo(fStart, fPreservedText, fText, null);
-    return Status.OK_STATUS;
-  \}
- return IOperationHistory.OPERATION_INVALID_STATUS;
- \}
- protected void redoTextChange() \{
-  try \{
-    if (fDocumentUndoManager.fDocument instanceof Document)
-       ((Document)fDocumentUndoManager.fDocument).replace(fStart, fEnd - fStart, fText, fRedoModificationStamp);
-   else
-     fDocumentUndoManager.fDocument.replace(fStart, fEnd - fStart, fText);
-   \} catch (BadLocationException x) \{
-  \}\}
-protected void updateTextChange() \{
-   fText = fDocumentUndoManager.fTextBuffer.toString();
-   fDocumentUndoManager.fTextBuffer.setLength(0);
-   fPreservedText = fDocumentUndoManager.fPreservedTextBuffer.toString();
-   fDocumentUndoManager.fPreservedTextBuffer.setLength(0);
-\}
- protected UndoableTextChange createCurrent() \{
-   if (fDocumentUndoManager.fFoldingIntoCompoundChange)
-     return new UndoableCompoundTextChange(fDocumentUndoManager);
-  return new UndoableTextChange(fDocumentUndoManager);
- \} \}
-  \end{Verbatim}
-      \vspace{-4mm}
-     \\ \hline
-\end{tabular} 
-\caption{Results from SearchCode CSE}
-\label{fig:undoEditor}
-\end{minipage}
-\end{figure*}
+\input{table-RQ2}

### 2015-11-17 weeklyReport/example-purity.tex
init 11-17

\begin{figure*}[!htb]
 \begin{minipage}{0.47\textwidth}
 \scriptsize 
 \begin{tabular}{p{1\textwidth}}
  \hline 
  \multicolumn{1}{c}{(A) An inconsistent name method and its caller.} \\ \hline
 %\midrule
 %\vspace*{-3mm}
 % performance improvement: https://github.com/apache/hbase/commit/ff2bcd476046c76d926639114efdb704fe287356#diff-53def65a3cf679a3f048ab71bcea9293
  /*org.apache.hadoop.hbase.master.Mocking.java:\href{https://github.com/apache/hbase/blob/390f32d79fd0c0464fcab008150ad182f4c0abef/hbase-server/src/test/java/org/apache/hadoop/hbase/master/Mocking.java}{390f32} */
 \begin{Verbatim}[commandchars=\\\{\}, tabsize=2]
1. static boolean{\bf \hl{verifyRegionState}}(ZooKeeperWatcher zkw, 
    EventType expectedState)\{
2.   zkw.sync(node);...
3.   return getEventType().equals(expectedState);
4. \}  
5. static void fakeRegionServerRegionOpenInZK(ZooKeeperWatcher w,...)\{
6.   while (! \uwave{verifyRegionState(w,...)}) \{
7.     Threads.sleep(1);...
8.  \} \}
 \end{Verbatim}
 \vspace*{-4mm}
 \\  \hline
 %\midrule
 \multicolumn{1}{c}{(B) A performance issue on the caller of the inconsistent name method.} \\ \hline
 %\midrule
 %https://issues.apache.org/jira/browse/HBASE-6109
 \vspace*{-1mm}
commit \href{https://github.com/apache/hbase/commit/ff2bcd#diff-53def65a3cf679a3f048ab71bcea9293}{ff2bcd}: HBASE-6109 Improve RIT performances.

HBASE-6109 issue description: lowering the number of synchronization
 \vspace*{-2mm}
 \begin{Verbatim}[commandchars=\\\{\}, tabsize=2]
 /*org.apache.hadoop.hbase.master.Mocking.java */
1. \color{blue}{static void \underline{\underline{waitForRegionPendingOpenInRIT }}(AssignmentManager am,}
  \color{blue}{String name) \{}
  // We used to do a check like this: Mocking.verifyRegionState(..)
2.  \color{blue}{ boolean wait = true;}
3.  \color{blue}{ while (wait) \{}
4.    \color{blue}{ RegionState state = am.getRegionsInTransition().get(name);}
5.    \color{blue}{ if (state != null && state.isPendingOpen())\{}
6.        \color{blue}{ wait = false;}
7.      \} else \{
8.       Thread.sleep(1);
9.   \} \}
10. static void fakeRegionServerRegionOpenInZK(ZooKeeperWatcher w,..) \{
11.  \color{blue}{\uwave{waitForRegionPendingOpenInRIT}(getAssignmentManager(),}
      \color{blue}{ getEncodedName());}
12. \}
 \end{Verbatim} 
 commit \href{https://github.com/apache/hbase/commit/17dff6#diff-53def65a3cf679a3f048ab71bcea9293}{17dff6}: (delete Mocking.java)

HBASE-11611 Clean up ZK-based region assignment.
 \begin{Verbatim}[commandchars=\\\{\}, tabsize=2]
13.\color{red}{- static boolean{\bf \hl{verifyRegionState}}(ZooKeeperWatcher zkw, }
  \color{red}{-   EventType expectedState)\{}
14.\color{red}{-   zkw.sync(node);...}
15.\color{red}{-   return getEventType().equals(expectedState);}
16.\color{red}{- \}  }
 \end{Verbatim} 
 \vspace{-4mm}
 \\  \hline
In line 2 of Part (A), the impure method \codefont{verifyRegionState} with a pure term \codefont{verify} invokes an impure method \codefont{ZooKeeperWatcher.sync()}. The  \codefont{verifyRegionState} is invoked in a \codefont{while} loop at line 6. This leads to a performance issue that the \codefont{sync} method will be called for many times. A developer fixed this performance issue by creating a new method called \codefont{waitForRegionPendingOpenInRIT}. This new method uses a boolean flag to represent the waiting state and invokes three pure methods \codefont{AssignmentManager.getRegionsInTransition()}, \codefont{RegionsInTransition.get()}, and \codefont{RegionState.isPendingOpen()} to check the waiting state. The inconsistent method name \codefont{verifyRegionState} was deleted in commit \href{https://github.com/apache/hbase/commit/17dff6#diff-53def65a3cf679a3f048ab71bcea9293}{17dff6}. \todo{Lisa: the correlation between bug fix and inconsistent name exists, yet describing in a direct-causal-relationship manner is misleading. This applies to the description of qualitative examples as well.}
 \end{tabular}
 \end{minipage}
 \hfill
  \begin{minipage}{0.47\textwidth}
\scriptsize 
\begin{tabular}{@{}p{1\textwidth}} 
 \hline 
 \multicolumn{1}{c}{(A) An inconsistently-named method and its caller} \\ \hline
 /* org.apache.accumulo.core.util.MetadataTable:\href{https://github.com/apache/accumulo/blob/69218e7e989b6f1d65afabce9c5b5ab0e3204141/core/src/main/java/org/apache/accumulo/core/util/MetadataTable.java}{69218e} */
    %bug fix: https://github.com/apache/accumulo/commit/8e4e6d 
\begin{Verbatim}[commandchars=\\\{\}, tabsize=2]
1. public static void{\bf \hl{getEntries}}(SortedSet<KeyExtent> tablets)
   throws AccumuloException\{...
2.  if (PREV_ROW_COLUMN.equals(...)) 			
3.  \{ tablets.add(new KeyExtent()); \}	
4.  validateEntries(tableId, tablets);		
5.  \}
6. public static void validateEntries(SortedSet<KeyExtent> tablets) 
   throws AccumuloException \{
7. if (tablets.size() == 0)		
8.   throw new AccumuloException("Problem with metadata table.");
9.  ...\}
  /* org.apache.accumulo.core.client.admin.TableOperationsImpl */
10. private void addSplits(String tableId)\{  
11.  SortedSet<KeyExtent> tablets = new TreeSet<KeyExtent>();
12.  while (true) \{
13.    try \{
14.      tablets.clear();
15.     \uwave{MetadataTable.getEntries(tablets);}
16. 	break;
17.  \} catch (Throwable t) \{
18.    UtilWaitThread.sleep(3000);...
19.  \}\}\}
\end{Verbatim}
\vspace{-4mm}
 \\ \hline
\multicolumn{1}{c}{(B) A refactoring on the method and its caller during a bug fix} \\ \hline
commit \href{https://github.com/apache/accumulo/commit/446a37a#diff-002fc1274cd98bf226ee8398551261a6}{446a37}: ACCUMULO-1481: refactor to consolidate metadata constants and structures in an organized way. 
    %bug fix: https://github.com/apache/accumulo/commit/446a37a9795f2df7
\begin{Verbatim}[commandchars=\\\{\}, tabsize=2]
 /* org.apache.accumulo.core.metadata.MetadataServicer */
 1.\color{blue}{ public static MetadataServicer \underline{\underline{forTableId}}(String tableId)  }
2.\color{blue}{   if (RootTable.ID.equals(tableId)) }
3.\color{blue}{     return new ServicerForRootTable(); ...}
4.\color{blue}{ \} }
/* org.apache.accumulo.core.metadata.ServicerForRootTable.java */
5.\color{blue}{ public void \underline{\underline{getTabletLocations}}(SortedMap<KeyExtent,String> tablets) \{}
6.\color{blue}{  tablets.put(RootTable.EXTENT, instance.getRootTabletLocation());}
7.\color{blue}{  \}}
/* org.apache.accumulo.core.client.admin.TableOperationsImpl */
8.\color{blue}{TreeMap<KeyExtent,String> tabletLocations = new TreeMap<KeyExtent,String>();}
9. public void addSplits(String tableId)\{  
10.  while (true) \{
11.   try \{ ...
12.  \color{blue}{ \uwave{MetadataServicer.forTableId(tableId)}}
       \color{blue}{ \uwave{ .getTabletLocations(tabletLocations);}}
13.   \} catch (Throwable t) \{
14.    UtilWaitThread.sleep(3000);...
15.  \} \}
\end{Verbatim}
\vspace{-4mm}
 \\ \hline

 In line 1 of Part (A), the impure method \codefont{getEntries} modifies \codefont{tablets} by appending a newly created \codefont{KeyEvent} instance to the list if the condition in line 2 holds. However, if the condition in line 2 fails, the method \codefont{validateEntries} will throw an exception in line 8, and this exception will force the program to sleep for 3 seconds in line 18. As illustrated by a later commit log in Part (B), a developer fixed this bug by refactoring the method \codefont{getEntries} and invoke \codefont{forTableId.getTabletLocations()} instead. \todo{Lisa: This example introduces another inconsistent name \codefont{getTabletLocations()}, that's why I prefer the first example.}
\end{tabular} 
%\caption{Inconsistent method name detected with purity analysis}
%\label{fig:purityExample}
\end{minipage}
%\end{figure}
 \caption{Inconsistent method name detected with purity analysis}
 \label{fig:purityExample}
% \begin{figure}[!htb]
 \end{figure*}

% In this section, we describe an example of inconsistent name found by \tool. As shown in List~\ref{lst:iNameExample}.

%  based on the similar usages of the instances of \codefont{FlushRequester} in line $10-14$, $27-32$, and $37-40$, we identify the field name anomaly of the object \codefont{FlushListener} declared in line 3, and the parameter name anomaly of the object   \codefont{FlushListener}.

% /* org.apache.hadoop.hbase.regionserver */
% public class HRegionServer {
%  private FlushRequester requester = null;
%  public void put(...) throws IOException {
%     if (requester == null) {
%       return;
%     }
%     if (!region.getRegionInfo().isMetaTable()) {
%         requester.request(this);
%       }...
% }}
% /* org.apache.hadoop.hbase.regionserver */
% class LogRoller extends Thread implements WALObserver {
%   private void scheduleFlush(final byte [] region) {...
%     FlushRequester requester = null;
%       if (requester != null) {
%         requester.request(r);...
%       }
% } }
% /* org.apache.hadoop.hbase.regionserver. SplitTransaction.java */
% class SplitTransaction {
%   HRegion createDaughterRegion(...,final FlushRequester flusher) {
%    FileSystem fs = this.parent.getFilesystem();
%    HRegion r = HRegion.newHRegion(..., flusher);
%    return r;
%   }}

### 2015-11-17 weeklyReport/example-usage-new.tex
init 11-17

\begin{figure*}[!htb]
\begin{minipage}{0.47\textwidth}
\scriptsize 
\begin{tabular}{p{1\textwidth}}
 \hline 
 \multicolumn{1}{c}{(A) A type-use pattern with a commonly used name} \\ \hline
%\midrule
/*org.apache.jackrabbit.core.config.RepositoryConfig.java:\href{https://github.com/apache/jackrabbit/blob/a6b82ed15de77f5e883740da725b21cdad059970/jackrabbit-core/src/main/java/org/apache/jackrabbit/core/config/RepositoryConfig.java}{a6b82e}*/
%\vspace*{-4mm}
\begin{Verbatim}[commandchars=\\\{\}, tabsize=2]
1. FileSystem virtualFS;
2. private WorkspaceConfig internalCreateWorkspaceConfig(...)\{
3.   try \{
4.     if (virtualFS != null) \{
5.       virtualFS.close();
6.      \}  \} catch (FileSystemException ignore) \{ \}
\end{Verbatim}
\vspace{-4mm}
\\  \hline
%\midrule
% 
\multicolumn{1}{c}{(B) A method using a field with inconsistent name} \\ \hline
%\vspace{-3mm}
/* org.apache.jackrabbit.core.RepositoryImpl:\href{https://github.com/apache/jackrabbit/blob/a6b82ed15de77f5e883740da725b21cdad059970/jackrabbit-core/src/main/java/org/apache/jackrabbit/core/RepositoryImpl.java}{a6b82e}*/
\begin{Verbatim}[commandchars=\\\{\}, tabsize=2]
1. FileSystem{\bf \hl{repStore}};
2. public void doShutdown() \{
3.   try \{
4.     \uwave{repStore.close()};
5.   \} catch (FileSystemException e) \{
6.        log.error("error while closing file system", e);
7.   \} \} 
\end{Verbatim} 
\vspace{-5mm}
\\  \hline
\multicolumn{1}{c}{(C) A bug fix on the field} \\ \hline
commit \href{https://github.com/apache/jackrabbit/commit/98ae1b3d1481d8713d0f4d8758ef9e19259a7270/?diff=split}{98ae1b}: JCR-1318: Repository Home locked not released despite RepositoryException being thrown.
%
%\vspace{-2mm}
\begin{Verbatim}[commandchars=\\\{\}, tabsize=2]
/* org.apache.jackrabbit.core.RepositoryImpl */
1. FileSystem{\bf \hl{repStore}};
2. public void doShutdown() \{
3.\color{blue}{+  \uwave{if (repStore != null)}} \{
4.  try \{
5.   \uwave{repStore.close()};
6.  \} catch (FileSystemException e) \{
7.    log.error("error while closing file system", e);
8.   \} \}
\end{Verbatim} 
\vspace{-5mm}
\\  \hline
\multicolumn{1}{c}{(D) The deletion of inconsistent name usage} \\ \hline
commit  \href{https://github.com/apache/jackrabbit/commit/f51ed4#diff-9751fd2ad72989dbc11c7caca47e907c}{f51ed4}: JCR-2640: Add repository file system to RepositoryContext. No more need for the separate metaDataStore fs. 
%https://github.com/apache/jackrabbit/commit/9cdb3cf89f11a1a201f758a1bd2f2c93e5718c59#diff-9751fd2ad72989dbc11c7caca47e907c
 % https://github.com/apache/jackrabbit/commit/9cdb3cf89f11a1a201f758a1bd2f2c93e5718c59#diff-9751fd2ad72989dbc11c7caca47e907c
%\vspace{-2mm}
\begin{Verbatim}[commandchars=\\\{\}, tabsize=2]
/* org.apache.jackrabbit.core.RepositoryImpl */
1.\color{red}{- FileSystem{\bf \hl{repStore}}};
2. public void doShutdown() \{
3.\color{red}{-  \uwave{if (repStore != null)} \{}
4.  try \{
5.\color{blue}{+  context.getFileSystem().close();}
6.  \} catch (FileSystemException e) \{
7.    log.error("error while closing file system", e);
8.   \} \}
9. public Thread newThread(Runnable r) \{
10.\color{blue}{+ FileSystem repStore = repConfig.getFileSystem();}
11.\color{blue}{+ context.setFileSystem(repStore);}
12. \}
\end{Verbatim} 
commit \href{https://github.com/apache/jackrabbit/commit/9cdb3c#diff-9751fd2ad72989dbc11c7caca47e907c}{9cdb3c}: (completely deletes this inconsistent name)

JCR-2640: Streamline namespace and node type registry creation
\begin{Verbatim}[commandchars=\\\{\}, tabsize=2]
13. public Thread newThread(Runnable r) \{
14.\color{red}{- FileSystem repStore = repConfig.getFileSystem();}
15.\color{red}{- context.setFileSystem(repStore);}
16.\color{blue}{+ context.setFileSystem(repConfig.getFileSystem());}
17. \}
\end{Verbatim} 
\vspace{-5mm}
\\  \hline
A \codefont{FileSystem} object receives a method call \codefont{FileSystem.close()} in a \codefont{try-catch} block. The majority of such objects with similar type-use pattern contains a term \codefont{FS} in their name except for \codefont{repStore} in Part (B). A developer fixed a bug in this method with an inconsistent name at line 3 in Part (C), and removed this inconsistent name from the type-use pattern in commit \href{https://github.com/apache/jackrabbit/commit/f51ed4#diff-9751fd2ad72989dbc11c7caca47e907c}{f51ed4}. This inconsistent name was completely deleted in commit \href{https://github.com/apache/jackrabbit/commit/9cdb3c#diff-9751fd2ad72989dbc11c7caca47e907c}{9cdb3c}. 
\end{tabular}
\end{minipage}
\hfill
\begin{minipage}{0.47\textwidth}
\scriptsize 
\begin{tabular}{p{1\textwidth}}
 \hline 
 \multicolumn{1}{c}{(A) A type-use pattern with a commonly used name} \\ \hline
/* org.apache.james.transport.mailets.Retry.java:\href{https://github.com/apache/james/blob/ed9bb43ec9f5b25f799e38c3a4b6e0d5053fc72f/mailets-function/src/main/java/org/apache/james/transport/mailets/Retry.java}{ed9bb4} */
%\vspace*{-4mm}
%snapshot link: https://github.com/apache/james/blob/ed9bb43ec9f5b25f799e38c3a4b6e0d5053fc72f/mailets-function/src/main/java/org/apache/james/transport/mailets/Retry.java
\begin{Verbatim}[commandchars=\\\{\}, tabsize=2]
1. private SpoolRepository retryRepository;
2. private MultipleDelayFilter delayFilter;
3.  public void run() \{
4.    Mail mail = retryRepository.accept(delayFilter);
5.    String key = mail.getName();
6.    if (retry(mail)) \{
7.   	retryRepository.remove(key);
8.     \} else \{
9.      retryRepository.store(mail);
10.    retryRepository.unlock(key);
11.    \}\}
\end{Verbatim}
\vspace{-4mm}
\\  \hline
%\midrule
\multicolumn{1}{c}{(B) A method using a field with inconsistent name } \\ \hline
%\vspace{-3mm}
/*org.apache.james.transport.mailets.RemoteDelivery.java:\href{https://github.com/apache/james/blob/ed9bb43ec9f5b25f799e38c3a4b6e0d5053fc72f/mailets-function/src/main/java/org/apache/james/transport/mailets/RemoteDelivery.java}{6aa468}*/
%snapshot link: https://github.com/apache/james/blob/ed9bb43ec9f5b25f799e38c3a4b6e0d5053fc72f/mailets-function/src/main/java/org/apache/james/transport/mailets/RemoteDelivery.java
\begin{Verbatim}[commandchars=\\\{\}, tabsize=2]
1. private SpoolRepository \hl{outgoing}; // The spool of outgoing mail
2. private MultipleDelayFilter delayFilter;
3. public void run() \{
4.  Mail mail = (Mail) \uwave{outgoing.accept(delayFilter)};
5.  String key = mail.getName();
6.  if (deliver(mail, session)) \{
7.   \uwave{outgoing.remove(key);}
8.    \} else \{
9.    \uwave{outgoing.store(mail);}
10.   \uwave{outgoing.unlock(key);}
11.  \}\}
\end{Verbatim} 
\vspace{-5mm}
\\  \hline
% refactoring: https://github.com/apache/james/commit/54cccd3a67dcd
\multicolumn{1}{c}{(C) A refactoring on the field} \\ \hline
commit \href{https://github.com/apache/james/commit/54cccd3a67dcd}{54cccd}: Minor changes to RemoteDelivery and Retry to make them more similar (I'd like to extract common code) (related to JAMES-874).
%\vspace{-2mm}
\begin{Verbatim}[commandchars=\\\{\}, tabsize=2]
/* org.apache.james.transport.mailets.RemoteDelivery.java */
// Repository used to store messages that will be delivered.
1. private SpoolRepository\textcolor{blue}{\underline{\underline{\bf workRepository}}}; 
2. private MultipleDelayFilter delayFilter;
3. public void run() \{
4.  Mail mail = (Mail)\textcolor{blue}{\bf \uwave{workRepository.accept(delayFilter)}};
5.  String key = mail.getName();
6.  if (deliver(mail, session)) \{
7.   \textcolor{blue}{\bf \uwave{workRepository.remove(key);}}
8.    \} else \{
9.   \textcolor{blue}{\bf \uwave{workRepository.store(mail);}}
10.  \textcolor{blue}{\bf \uwave{workRepository.unlock(key);}}
11.  \}\}
\end{Verbatim} 
\vspace{-5mm}
\\  \hline
Part (A) represents a type-use pattern for \codefont{SpoolRepository} object from line 4 to line 10. The objects in similar type-use patterns are commonly named as \codefont{*Repository} except for \codefont{outgoing} in Part (B).  This inconsistent object name was renamed as \codefont{workRepository} in commit \href{https://github.com/apache/james/commit/54cccd3a67dcd}{54cccd} to enforce naming inconsistency. \todo{Lisa: I prefer the first example as there is no bug fix related to this example, although the inconsistent name was renamed.}
\end{tabular}
%\caption{Inconsistent field identified by type-use pattern analysis}
%\label{fig:usageExample}
\end{minipage}
%\end{figure}
%\begin{figure}[!htb]

\caption{Inconsistent field identified by type-use pattern analysis}
\label{fig:usageExample}
\end{figure*}

### 2015-11-17 weeklyReport/example-usage-old.tex
init 11-17

\begin{figure}[!htb]
\begin{minipage}{0.47\textwidth}
\scriptsize 
\begin{tabular}{p{1\textwidth}}
 \hline 
 \multicolumn{1}{c}{(A) A type-use pattern with a commonly used name} \\ \hline
%\midrule
\vspace*{-4mm}
\begin{Verbatim}[commandchars=\\\{\}, tabsize=2]
/* org.apache.jackrabbit.core.mem.InMemPersistenceManager */
1. FileSystem blobFS;
2. public void close() \{
3.   if (blobFS != null) \{
4.    try \{
5.      blobFS.close();
6.    \} catch (FileSystemException e) \{
7.    \} 
8.    finally \{
9.     blobFS.releaseLock();
10.   \} \} \}
\end{Verbatim}
\vspace{-4mm}
\\  \hline
%\midrule
\multicolumn{1}{c}{(B) A method using a field with inconsistent name } \\ \hline
\vspace{-3mm}
\begin{Verbatim}[commandchars=\\\{\}, tabsize=2]
/* org.apache.jackrabbit.core.IRepositoryImpl */
1. FileSystem{\bf \hl{repStore}};
2. public void doShutdown() \{
3.  \uwave{if (repStore != null)} \{
4.   try \{
5.     \uwave{repStore.close()};
6.   \} catch (FileSystemException e) \{
7.        log.error("error while closing file system", e);
8.   \} \} \}
\end{Verbatim} 
\vspace{-5mm}
\\  \hline
\multicolumn{1}{c}{(C) A refactoring on the field} \\ \hline
Date: 2/16/2010

Change Log: repStore is a FS rather than a DataStore, lock does not release when shutdown repFS, rename FS for consistency. 
\vspace{-2mm}
\begin{Verbatim}[commandchars=\\\{\}, tabsize=2]
/* org.apache.jackrabbit.core.IRepositoryImpl */
1. FileSystem\color{blue}{\underline{\underline{\bf repFS}}};
2. public void doShutdown() \{
3.  \color{blue}{\uwave{if (repFS != null)}} \{
4.  try \{
5.   \color{blue}{\uwave{repFS.close()}};
6.  \} catch (FileSystemException e) \{
7.    log.error("error while closing file system", e);
8. \color{blue}{\bf \} finally \{ }
9.      \color{blue}{\bf \uwave{repFS.releaseLock()};}
10.  \} \} \}
\end{Verbatim} 
\vspace{-5mm}
\\  \hline
\end{tabular}
\caption{Inconsistent field identified by type-use pattern analysis}
\label{fig:usageExample}
\end{minipage}
\end{figure}

%%%%%%%Usage pattern example %%%%%%%
 \begin{figure}[!htb]
 \begin{minipage}{0.47\textwidth}
 \scriptsize 
 \begin{tabular}{p{1\textwidth}}\hline
   \multicolumn{1}{c}{(A) A type-use pattern with a commonly used name} \\ \hline
 %\midrule
 \vspace{-4mm}
 \begin{Verbatim}[commandchars=\\\{\}, tabsize=2]
 /* org.apache.hadoop.hbase.regionserver.LogRoller */
1. FlushRequester requester = null; ...
2. private void scheduleFlush(final byte[] region) \{...
3.   if (requester != null) \{
4.      requester.request(this);...
5.   \}
6. \} 
 \end{Verbatim}
 \vspace{-4mm}
\\ \hline
  \multicolumn{1}{c}{(B) A method with an inconsistent parameter and its caller} \\ \hline
 %\midrule
 \vspace{-4mm}
 \begin{Verbatim}[commandchars=\\\{\}, tabsize=2]
 /* org.apache.hadoop.hbase.regionserver.HRegion */
1. Context c = getContext();
2. public static HRegion newHRegion(...,
3.     FlushRequester \hl{flushListener}) \{  
4.   if (\uwave{flushListener} != null)  
5.     \uwave{flushListener}.request(this);
6.   return c.newInstance(..., \uwave{flushListener});  
7.\}
 /* org.apache.hadoop.hbase.util.HMerge */
8. protected HRegion merge(...)  \{
9.  HRegion r = HRegion.newHRegion(..., null);//\textcolor{red}{no FlushRequester}
10.  return r.openHRegion();
11.\} 
 \end{Verbatim}
 \vspace{-4mm}
 \\  \hline
 %\midrule
 \multicolumn{1}{c}{(C) A refactoring on the method and its caller} \\ \hline
 %\midrule
 Date: 8/31/2010

 Change Log: HBASE-2692 Unfinished renaming from CacheFlushListener to FlushRequester.
  \vspace{-2mm}
 \begin{Verbatim}[commandchars=\\\{\}, tabsize=2]
  /* org.apache.hadoop.hbase.regionserver.HRegion */
1. Context c = getContext();
2. public static HRegion newHRegion(..., 
3.     FlushRequester\textcolor{blue}{\underline{\underline{\bf flushRequester}}}) \{  
4.   if (\textcolor{blue}{\bf \uwave{flushRequester}} != null)  
5.     \textcolor{blue}{\bf \uwave{flushRequester}}.request(this);
6.   return c.newInstance(..., \textcolor{blue}{\bf \uwave{flushRequester}});  
7. \}
 \end{Verbatim} 
 %\vspace{-3mm}
 %\\  \hline
%\multicolumn{1}{c}{(C) Bug fix that is related to the inconsistent name} \\ \hline
%\midrule
Date: 9/8/2010

Change Log: FIX: Client can not send flush request.
\vspace{-2mm}
\begin{Verbatim}[commandchars=\\\{\}, tabsize=2]
 /* org.apache.hadoop.hbase.util.HMerge */
 8. FlushRequester requester = new FlushRequester();
 9. protect HRegion merge(...)  \{
10. \textcolor{blue}{\bf HRegion r = HRegion.newHRegion(..., requester);  }
11.  return r.openHRegion();
12. \} 
 \end{Verbatim} 
 \vspace{-4mm}
 \\  \hline
 \end{tabular}
 \caption{Inconsistent parameter name detected with type-use pattern analysis}
 \label{fig:usageExample}
 \end{minipage}
 \end{figure}

### 2015-11-17 weeklyReport/problem.tex
10-27 IR clustering
init 11-17

@@
 
-Problem: The code examples returned from code search engine or other code search tools are not structured.
+%\section{Problem 1}  
+\noindent{\bf{Proactively Recommending Code Examples to Reduce Integration Conflicts}}
+
+%Problem: The code examples returned from code search engine or other code search tools are not structured.
 
@@
 
-Input: a set of code examples returned from code search engine.
+%Input: a set of code examples returned from code search engine.
 
-Output: a list of code example clusters organized based on their structural similarity.
+%Output: a list of code example clusters based on their structural similarity.
 
@@
 
-%Developers frequently use source code examples as the basis for interacting with an  application programming interface (API) to obtain the needed functionality~\cite{CodeSearch:FSE15}.
+Developers frequently use source code examples as the basis for interacting with an  application programming interface (API) to obtain the needed functionality~\cite{CodeSearch:FSE15}.
 In this case, the source code example serves as the explicit origin for a reuse task which transforms a sequence of APIs with corresponding control structure to the target context~\cite{Frakes:reuseStatus05}.
-During the process of reuse task such as `add undo and redo actions in my Graphics Editor', developers often query for a set of examples considering the task, and integrate examples that match the task into their system~\cite{Parsons:cognitiveReuse04}.
+
+%During the process of reuse task such as `add undo and redo actions in my Graphics Editor', developers often query for a set of examples considering the task, and integrate examples that match the task into their system~\cite{Parsons:cognitiveReuse04}.
 
@@
 
+\noindent{\bf{Identify Duplicated Feature Requests}}
+
 %\item \textbf{Example Integration Phase.} Our approach investigates the user's contexts to recommend the best-fit reuse task  considering the number of matched structural facts in target context.

### 2015-11-17 weeklyReport/table-RQ2.tex
init 11-17

 \begin{figure*}[!htb]
 \begin{minipage}{0.47\textwidth}
% \begin{table}[ht]
%\begin{center}
%\vspace{-5mm}
%\caption{Sampled inconsistent names and corresponding fixes.} 
%\label{tab:sample}
%\vspace{1mm}
\scriptsize{
\begin{tabular}{@{}l|p{3cm}p{3cm}}
Type&\multicolumn{2}{c}{(addition, fix revision, deletion)}\\  \midrule
%Pure&(7fac9,859056,---),&(a19676,c74517,---),\\
%&(0ccc3c,d5a9a3,---),&(542c7c,1d8a1d,ca1c68),\\
%&(b89bba,7e1fd3,---),&(37352e,939926c,---),\\
%&(a19676,a11042,---),&(74d393,ec7719,933a6d),\\
%&(8e4e6d,446a37,446a37),&(062620,ff2bcd,17dff6)\\   \midrule
%%(390f32,c9b028,---)
%Impure&(002dd69,e17cec,---),&(270277,d18d34e,ca1c68),\\ 
%&(dc372a,7c2d77,---),&(0201be,---,---),\\ 
%&(cd7157,---,---),&(cd7157,---,---), \\
%& (1daa81,---,48339b),&(55391f,---,ca1c68), \\
%&(0c5734,---,---),&(4ba168,---,---)\\ \midrule
%Object&(cd7157,fc7c8f,---),&(245343,ed3433,---),\\
%&(cd7157,1c309f,---),&(a6b82e,f51ed4,---),\\
%&(cf9afa, 36f7c4,36f7c4),&(4c792b,507d9d,507d9d),\\
%&(6aa468,54cccd,54cccd),&(ff7a62,d8b712,---), \\
%&(242f30,b3ba69,---),&(e1da90,f52130,f52130)\\\midrule
%(cd7157,d4fb88,---),(509bce,---,---)\\ 
%&(a6b82e,0a8ede,---), &(0930a8,c3fb42,---),\\
%&(cd7157,96247e,---), &(cd7157,47dfcf,---), \\
Pure&(\href{https://github.com/apache/hadoop/commit/7fac946#diff-d97658c87c6ac1d194da12d149834a25}{7fac94},\href{https://github.com/apache/hadoop/commit/8590564dc56195cb2caa245e3ee1c06eca3938d3#diff-52728ad908d378250fa082c8a30113af}{859056},---),&(\href{https://github.com/apache/hadoop/commit/a196766ea07775f18ded69bd9e8d239f8cfd3ccc#diff-9400d498326ceaca4b310cd3415277ef}{a19676},\href{https://github.com/apache/hadoop/commit/c74517#diff-649c4e46d99ae8011ff0fa0c118d9726}{c74517},---),\\
&(\href{https://github.com/apache/hadoop/commit/0ccc3c441a27646d761dfc913f750e2666f9ecfb#diff-1c2cc53548a274cf6eff37f3ded5dbbb}{0ccc3c},\href{https://github.com/apache/hadoop/commit/d5a9a3#diff-3f9d4f0c9157be654273622926ae04b9}{d5a9a3},---),&(\href{https://github.com/apache/hadoop/commit/542c7ccdce2680a4d179a8d948b8cc18221eb2bc#diff-eed8766da92e69dd6acd3fb9edc421f0}{542c7c},\href{https://github.com/apache/hadoop/commit/1d8a1d#diff-53b4c7b6b46b3778ebfa5ecdcb35521f}{1d8a1d},\href{https://github.com/apache/hadoop/commit/ca1c683b}{ca1c68}),\\
&(\href{https://github.com/apache/hadoop/commit/b89bba0acb#diff-cac0a345696e1521d21f8cbfd633f90c}{b89bba},\href{https://github.com/apache/hadoop/commit/7e1fd3#diff-336c3fa4df86402ec7b5339c1dbac724}{7e1fd3},---),&(\href{https://github.com/apache/hadoop/commit/37352ebe4dcbd526aafc343cccb350cd154e0315#diff-3de8a0425c49269f274f46497111dc80}{37352e},\href{https://github.com/apache/hadoop/commit/939926c#diff-3de8a0425c49269f274f46497111dc80}{939926},---),\\
&(\href{https://github.com/apache/hadoop/commit/a196766ea07775f18ded69bd9e8d239f8cfd3ccc#diff-6bfd89034be79e2f37aae9f211605fff}{a19676},\href{https://github.com/apache/hadoop/commit/a11042#diff-f471412017f4f6728224615c8362da5f}{a11042},---),&(\href{https://github.com/apache/hadoop/commit/74d393382341939}{74d393},\href{https://github.com/apache/hadoop/commit/ec7719#diff-2bd0b9b3e70406484c416d876341fa61}{ec7719},\href{https://github.com/apache/hadoop/commit/933a6d2c}{933a6d}),\\
&(\href{https://github.com/apache/accumulo/commit/8e4e6d6420e47f64b9fd54d9b6f5bc5b0b158b8b#diff-002fc1274cd98bf226ee8398551261a6}{8e4e6d},\href{https://github.com/apache/accumulo/commit/446a37a#diff-002fc1274cd98bf226ee8398551261a6}{446a37},\href{https://github.com/apache/accumulo/commit/446a37a#diff-002fc1274cd98bf226ee8398551261a6}{446a37}),&(\href{https://github.com/apache/hbase/commit/062660e3f48b#diff-76fffa96c664ed27a2f880fd02da3962}{062660},\href{https://github.com/apache/hbase/commit/ff2bcd#diff-53def65a3cf679a3f048ab71bcea9293}{ff2bcd},\href{https://github.com/apache/hbase/commit/17dff6#diff-53def65a3cf679a3f048ab71bcea9293}{17dff6})\\ \midrule
Impure&(\href{https://github.com/apache/hadoop/commit/002dd6968b89ded6a77858ccb50c9b2df074c226#diff-489fac1eb320e92dd65b62f00b67f71c}{002dd6},\href{https://github.com/apache/hadoop/commit/e17cec#diff-489fac1eb320e92dd65b62f00b67f71c}{e17cec},---),&(\href{https://github.com/apache/hadoop/commit/270277b9307c8de9df523e94bfc46df423e62b53#diff-7f17e003fb54ff97abf2007fbd6cdc61}{270277},\href{https://github.com/apache/hadoop/commit/d18d34e93#diff-7f17e003fb54ff97abf2007fbd6cdc61}{d18d34},\href{https://github.com/apache/hadoop/commit/ca1c68}{ca1c68}),\\
&(\href{https://github.com/apache/hadoop/blob/dc372af412a5923f04feaad8925a16d89180bc8d/src/java/org/apache/hadoop/mapred/TaskRunner.java}{dc372a},\href{https://github.com/apache/hadoop/commit/7c2d77#diff-c0169961c9fbca7c0a7b3afb2049665a}{7c2d77},---),&(\href{https://github.com/apache/hadoop/commit/0201be46c298e94176ec6297e9d9cdba3afc2bbd#diff-685393e5e55e645ac340ea5bfd3b1cf1}{0201be},---,---),\\
&(\href{https://github.com/apache/hadoop/blob/3b85bd7c3391719624a261f061a67cc4356be477/hadoop-common-project/hadoop-common/src/main/java/org/apache/hadoop/fs/ftp/FTPFileSystem.java}{cd7157},---,---),&(\href{https://github.com/apache/hadoop/blob/3b85bd7c3391719624a261f061a67cc4356be477/hadoop-common-project/hadoop-common/src/main/java/org/apache/hadoop/fs/ChecksumFileSystem.java}{cd7157},---,---),\\
&( \href{https://github.com/apache/hadoop/commit/1daa81#diff-13924c43e3ff5852da014b5005422666}{1daa81},---,---),&( \href{https://github.com/apache/hadoop/commit/55391f#diff-b7bcf8118ef56aa71a37a08b9479afd5}{55391f},---, \href{https://github.com/apache/hadoop/commit/ca1c68}{ca1c68}),\\
&(\href{https://github.com/apache/hadoop/commit/0c5734e4aca873f405fbf994e5fe7061e31731c8#diff-8da26f813ae9e87bbf0fb9abb349acc2}{0c5734},---,---),&(\href{https://github.com/apache/hadoop/commit/4ba168e4873c30574d18541b53b8821f62bd2589#diff-fa311023e9175bac1e31055102b7331f}{4ba168},---,---)\\ \midrule
Object&(\href{https://github.com/apache/hadoop/commit/5128a9a453d}{5128a9},\href{https://github.com/apache/hadoop/commit/fc7c8f9#diff-34d704a739ee5bdbee9bb5cd1426972b}{fc7c8f},---),&(\href{https://github.com/apache/hadoop/commit/2453431f642db9d38058b0227fd7636c162020e0#diff-72f498fd913780670fc13711bc524734}{245343},\href{https://github.com/apache/hadoop/commit/ed3433072#diff-72f498fd913780670fc13711bc524734}{ed3433},---),\\
&(\href{https://github.com/apache/hadoop/commit/cd7157784e5e5ddc4e77144d042e54dd0d04bac1#diff-16cbdb68a1f1e17dcc9f848ee6084e0c}{cd7157},\href{https://github.com/apache/hadoop/commit/1c309f763be3dd2e3d7d1616d2c960ff80cf9b03#diff-16cbdb68a1f1e17dcc9f848ee6084e0c}{1c309f},---),&(\href{https://github.com/apache/jackrabbit/commit/a6b82e}{a6b82e},\href{https://github.com/apache/jackrabbit/commit/f51ed4d48a#diff-9751fd2ad72989dbc11c7caca47e907c}{f51ed4},\href{https://github.com/apache/jackrabbit/commit/9cdb3c#diff-9751fd2ad72989dbc11c7caca47e907c}{9cdb3c}),\\
&(\href{https://github.com/apache/hadoop/commit/3512203f6c54033db1d52118edf595e5b5e1335e#diff-ad9e40bbf27e54506a64a57c691acc01}{351220},\href{https://github.com/apache/hadoop/commit/36f7c4360#diff-1c2cc53548a274cf6eff37f3ded5dbbb}{36f7c4},\href{https://github.com/apache/hadoop/commit/36f7c4360#diff-1c2cc53548a274cf6eff37f3ded5dbbb}{36f7c4}),&(\href{https://github.com/apache/commons-vfs/commit/c5451d949d67c415863565dcb56a6b2608a3aad0#diff-6ac9cecfbc1506096ed3445c48318795}{73e505},\href{https://github.com/apache/commons-vfs/commit/507d9d2061d4ea8c4ed4c26a5aad4f18aa493e67?diff=unified#diff-5a9a853727565aea8ec4f5670cafa120}{507d9d},\href{https://github.com/apache/commons-vfs/commit/507d9d2061d4ea8c4ed4c26a5aad4f18aa493e67?diff=unified#diff-5a9a853727565aea8ec4f5670cafa120}{507d9d}),\\
&(\href{https://github.com/apache/james/commit/6aa468ab069ce094027839b0282c47971598f28a#diff-53334ca0c55bca9fd6821a895f6ec46b}{6aa468},\href{https://github.com/apache/james/commit/54cccd3#diff-53334ca0c55bca9fd6821a895f6ec46b}{54cccd},\href{https://github.com/apache/james/commit/54cccd3#diff-53334ca0c55bca9fd6821a895f6ec46b}{54cccd}),&(\href{https://github.com/apache/jackrabbit/commit/ff7a62c0a8768714f8c36e3f8f07d2f017eebbfe#diff-7df848bb75ab7d3df5738968da840306}{ff7a62},\href{https://github.com/apache/jackrabbit/commit/d8b712#diff-7df848bb75ab7d3df5738968da840306}{d8b712},---),\\
&(\href{https://github.com/apache/hbase/commit/e1da900df#diff-b9d8ad451ab3fd5f5ff8593268230822}{e1da90},\href{https://github.com/apache/hbase/commit/f52130953245d93489a9c700c3b00eedbe70fdb9/src/main/java/org/apache/hadoop/hbase/regionserver/HRegion.java}{f52130},\href{https://github.com/apache/hbase/commit/f52130953245d93489a9c700c3b00eedbe70fdb9/src/main/java/org/apache/hadoop/hbase/regionserver/HRegion.java}{f52130}),&(\href{https://github.com/apache/hadoop/commit/a196766ea07775f18ded69bd9e8d239f8cfd3ccc#diff-9400d498326ceaca4b310cd3415277ef}{a19676},\href{https://github.com/apache/hadoop/commit/d4fb8821#diff-649c4e46d99ae8011ff0fa0c118d9726}{d4fb88},---)\\ \midrule

\end{tabular} \newline
--- represents that the inconsistent name was not fixed or deleted. 
 }
  \begin{itemize} 
\item \textbf{Pure term in impure methods.} In project \codefont{Apache accumulo}, a pure term \codefont{get} was used in an impure method \codefont{getEntries} that mutates its parameter \codefont{tablets} in an \codefont{if} condition. If this condition fails, this \codefont{getEntries} method will throw an exception to its caller, forcing the program to sleep for 3 seconds. This bug was fixed in revision \href{https://github.com/apache/accumulo/commit/446a37a#diff-002fc1274cd98bf226ee8398551261a6}{446a37} with a refactoring. 
\item \textbf{Impure term in a pure method.} As shown in Part (A) on the right, in project \codefont{Apache hadoop}, an impure term \codefont{prepare} was used in a pure method \codefont{prepare} which simply returns \codefont{true}.  When developer tried to add a new feature for \codefont{HADOOP-489}, she encountered a \codefont{NullPointerException} for the \codefont{prepare} method. The developer fixed this bug in revision \href{https://github.com/apache/hadoop/commit/7c2d77#diff-c0169961c9fbca7c0a7b3afb2049665a}{7c2d77}  by implementing another \codefont{init} method and invokes this new method in \codefont{prepare} method. This fix changes  the method \codefont{prepare} to impure method.
% In project \codefont{Apache hadoop}, an impure term \codefont{start} was used in a pure method \codefont{startSkipping}. The method \codefont{startSkipping} checks if the bad records can be skipped and returns the checking result. This method experiences  a bug fix which sets a maximum boundary for skipped records in revision \codefont{d18d34}.
\item \textbf{Inconsistent object names in similar type use patterns.} In project \codefont{Apache hbase}, there was a field named \codefont{flushListener} with type \codefont{FlushRequester}, while other object names with similar type use patterns used \codefont{*Requester} as a name. This inconsistent name was introduced in revision \href{https://github.com/apache/hbase/commit/e1da900df#diff-b9d8ad451ab3fd5f5ff8593268230822}{e1da90} when user renamed the class \codefont{CacheFlushListener} to \codefont{FlushRequester} yet forgot to rename the object name consistently. This inconsistent name was renamed as \codefont{flushRequester} in fix revision \href{https://github.com/apache/hbase/commit/f52130953245d93489a9c700c3b00eedbe70fdb9/src/main/java/org/apache/hadoop/hbase/regionserver/HRegion.java}{f52130}. 
 \end{itemize} 
% \vspace{-2mm}
% \end{center}
%  \vspace{-4mm}
%\end{table}
  \end{minipage}
  \hfill
 \begin{minipage}{0.47\textwidth}
 \scriptsize 
 \begin{tabular}{p{1\textwidth}}
  \hline 
  %https://github.com/apache/hadoop/commit/d18d34e9390cca94360675879fb29650e998d6e2/?diff=unified#diff-7f17e003fb54ff97abf2007fbd6cdc61
 % HADOOP-3829: If the number of skipped records in the neighborhood of a bad record are not 
%acceptable to the user, then narrow down the skipped range to the user acceptable value. 
   \multicolumn{1}{c}{(C) A impure term used in pure method, and fix on it.} \\ \hline
commit  \href{https://github.com/apache/hadoop/commit/7c2d77#diff-c0169961c9fbca7c0a7b3afb2049665a}{7c2d77}: HADOOP-489. Separate user logs from system logs.

\href{https://issues.apache.org/jira/browse/HADOOP-489}{HADOOP-489 issue comment}: ``my tasks fail with a NullPointer:..org.apache.hadoop.mapred.TaskRunner.prepare()..''
 \vspace*{-3mm}
 \begin{Verbatim}[commandchars=\\\{\}, tabsize=2]
 /* org.apache.hadoop.mapred.TaskRunner.java */
1.\color{red}{ -  public boolean prepare() throws IOException \{return true;\}}
2.\color{blue}{+  public boolean prepare() throws IOException \{}
3.\color{blue}{+    taskLogWriter.init();         }
4.\color{blue}{+    return true;}
5.\color{blue}{+  \}}
  \end{Verbatim}
  \vspace*{-4mm}
 \\  \hline
   \multicolumn{1}{c}{(B) A refactoring on the field with inconsistent name} \\ \hline
commit \href{https://github.com/apache/hbase/commit/f52130953245d93489a9c700c3b00eedbe70fdb9/src/main/java/org/apache/hadoop/hbase/regionserver/HRegion.java}{f52130}: HBASE-2692 Master rewrite and cleanup for 0.90.

SubTask issue description: \href{https://issues.apache.org/jira/browse/HBASE-2695}{HBASE-2695} Before doing the more significant changes to HMaster, it would benefit greatly from some cleanup, commenting, and a bit of refactoring.
 \begin{Verbatim}[commandchars=\\\{\}, tabsize=2]
 /* org.apache.hadoop.hbase.regionserver.HRegion.java */
1.\color{red}{-  final FlushRequester flushListener;}
2.\color{blue}{+  final FlushRequester flushRequester;}
3.  private void requestFlush() \{ 
4.\color{red}{-    if (this.flushListener == null) \{ }
5.\color{blue}{+    if (this.flushRequester == null) }
6.    \{ return; \}
7.\color{red}{-    this.flushListener.request(this);}
8.\color{blue}{+   this.flushRequester.requestFlush(this);}
9.\}
 \end{Verbatim}
  \vspace*{-4mm}
 \\  \hline 
  \multicolumn{1}{c}{(C) An impure term used in pure method and a bug fix on it} \\ \hline
commit  \href{https://github.com/apache/hadoop/commit/d18d34e93#diff-7f17e003fb54ff97abf2007fbd6cdc61}{d18d34}: HADOOP-3829. Narrown down skipped records based on user acceptable value.
 %\midrule
 \vspace*{-3mm}
 \begin{Verbatim}[commandchars=\\\{\}, tabsize=2]
 /*org.apache.hadoop.mapred.TaskInProgress.java: */
1. private boolean{\bf \hl{ startSkipping()}} \{
2.\color{red}{-  if(SkipBadRecords.getEnabled(conf) && }
3.\color{blue}{+  if(maxSkipRecords>0 && }
4.     numTaskFailures >= SkipBadRecords.
          getAttemptsToStartSkipping(conf)) \{
5.       return true;
6.     \} 
7.  return false;\}
\end{Verbatim}
 \vspace*{-4mm}
 \\  \hline
 %\midrule
% \multicolumn{1}{c}{(D) A impure term used in pure method, no bug fix on it.} \\ \hline
% \vspace*{-3mm}
% \begin{Verbatim}[commandchars=\\\{\}, tabsize=2]
%1. private int maximumFpRemove(int[] h) \{
%2.    int maxIndex = Integer.MIN_VALUE;
%3.    double maxValue = Double.MIN_VALUE;
%4.    for (int i = 0; i < nbHash; i++) \{
%5.      double fpWeight = getWeight(fpVector[h[i]]);
%6.      if (fpWeight > maxValue) \{
%7.        maxValue = fpWeight;
%8.        maxIndex = h[i];
%9.    \} \}
%10. return maxIndex; \}
% \end{Verbatim}
%  \vspace*{-4mm}
% \\  \hline 
  \end{tabular}
 \end{minipage}
  \begin{minipage}{1\textwidth}
%  \scriptsize{
Pure term used in impure methods: 
\begin{enumerate}
\item heartbeatCheck() in HeartbeatManager.java: addition \href{https://github.com/apache/hadoop/commit/7fac946#diff-d97658c87c6ac1d194da12d149834a25}{7fac94} fix \href{https://github.com/apache/hadoop/commit/8590564dc56195cb2caa245e3ee1c06eca3938d3#diff-52728ad908d378250fa082c8a30113af}{859056} no deletion.
\item receivePacket() in BlockReceiver.java: addition \href{https://github.com/apache/hadoop/commit/a196766ea07775f18ded69bd9e8d239f8cfd3ccc#diff-9400d498326ceaca4b310cd3415277ef}{a19676} fix \href{https://github.com/apache/hadoop/commit/c74517#diff-649c4e46d99ae8011ff0fa0c118d9726}{c74517} no deletion.
\item getFileChecksum() in DFSClient.java: addition \href{https://github.com/apache/hadoop/commit/0ccc3c441a27646d761dfc913f750e2666f9ecfb#diff-1c2cc53548a274cf6eff37f3ded5dbbb}{0ccc3c}  fix \href{https://github.com/apache/hadoop/commit/d5a9a3#diff-3f9d4f0c9157be654273622926ae04b9}{d5a9a3} no deletion.
\item obtainNewReduceTask() in JobInProgress.java: addition \href{https://github.com/apache/hadoop/commit/542c7ccdce2680a4d179a8d948b8cc18221eb2bc#diff-eed8766da92e69dd6acd3fb9edc421f0}{542c7c}  fix \href{https://github.com/apache/hadoop/commit/1d8a1d#diff-53b4c7b6b46b3778ebfa5ecdcb35521f}{1d8a1d} deletion \href{https://github.com/apache/hadoop/commit/ca1c683b}{ca1c68}.
\item fetchOutputs() in ReduceTask.java: addition \href{https://github.com/apache/hadoop/commit/b89bba0acb#diff-cac0a345696e1521d21f8cbfd633f90c}{b89bba} fix \href{https://github.com/apache/hadoop/commit/7e1fd3#diff-336c3fa4df86402ec7b5339c1dbac724}{7e1fd3} no deletion.  %%bug fix 01ad5a4d30f5d
\item checkLocalizedPath() in TestTrackerDistributedCacheManager.java: addition \href{https://github.com/apache/hadoop/commit/37352ebe4dcbd526aafc343cccb350cd154e0315#diff-3de8a0425c49269f274f46497111dc80}{37352e} fix \href{https://github.com/apache/hadoop/commit/939926c#diff-3de8a0425c49269f274f46497111dc80}{939926} no deletion.
\item verifyDir() in TestDFSUpgradeFromImage.java: addition \href{https://github.com/apache/hadoop/commit/a196766ea07775f18ded69bd9e8d239f8cfd3ccc#diff-6bfd89034be79e2f37aae9f211605fff}{a19676}  fix \href{https://github.com/apache/hadoop/commit/a11042#diff-f471412017f4f6728224615c8362da5f}{a11042} no deletion.
\item mapOutputLost() in TaskTracker.java:  addition \href{https://github.com/apache/hadoop/commit/74d393382341939}{74d393} fix  \href{https://github.com/apache/hadoop/commit/ec7719#diff-2bd0b9b3e70406484c416d876341fa61}{ec7719} deletion \href{https://github.com/apache/hadoop/commit/933a6d2c}{933a6d}
\item getEntries() in MetadataTable.java: addition \href{https://github.com/apache/accumulo/commit/8e4e6d6420e47f64b9fd54d9b6f5bc5b0b158b8b#diff-002fc1274cd98bf226ee8398551261a6}{8e4e6d}  fix and deletion \href{https://github.com/apache/accumulo/commit/446a37a#diff-002fc1274cd98bf226ee8398551261a6}{446a37}.
\item verifyRegionState() in Mocking.java: addition \href{https://github.com/apache/hbase/commit/062660e3f48b#diff-76fffa96c664ed27a2f880fd02da3962}{062660}  fix \href{https://github.com/apache/hbase/commit/ff2bcd#diff-53def65a3cf679a3f048ab71bcea9293}{ff2bcd} deletion \href{https://github.com/apache/hbase/commit/17dff6#diff-53def65a3cf679a3f048ab71bcea9293}{17dff6}
%\item getMetaTableRowResultAsSplitRegion() in Mocking.java: addition \href{}{} fix  \href{https://github.com/apache/hbase/commit/c9b028862a61ee2a96fdef6b55c36b03939ceada#diff-53def65a3cf679a3f048ab71bcea9293}{c9b028} 
%\item.  estimate() in PiEstimator.java:  fix \href{https://github.com/apache/hadoop/blob/509bcea8cf858a911a5285fe3acd0d000855e28a/src/examples/org/apache/hadoop/examples/PiEstimator.java}{509bce}
\end{enumerate}
%}
 \end{minipage}
  \end{figure*}[!htb]
  \begin{figure*}[!htb]
  \begin{minipage}{1\textwidth}
Impure term used in pure methods:
\begin{enumerate}
\item handleKind() in JobClient.java:  addition \href{https://github.com/apache/hadoop/commit/002dd6968b89ded6a77858ccb50c9b2df074c226#diff-489fac1eb320e92dd65b62f00b67f71c}{002dd6} fix  \href{https://github.com/apache/hadoop/commit/e17cec#diff-489fac1eb320e92dd65b62f00b67f71c}{e17cec} no deletion.
\item  startSkipping() in TaskInProgress.java addition \href{https://github.com/apache/hadoop/commit/270277b9307c8de9df523e94bfc46df423e62b53#diff-7f17e003fb54ff97abf2007fbd6cdc61}{270277} fix  \href{https://github.com/apache/hadoop/commit/d18d34e93#diff-7f17e003fb54ff97abf2007fbd6cdc61}{d18d34} deletion \href{https://github.com/apache/hadoop/commit/ca1c68}{ca1c68}.
\item  prepare() in TaskRunner.java  addition \href{https://github.com/apache/hadoop/blob/dc372af412a5923f04feaad8925a16d89180bc8d/src/java/org/apache/hadoop/mapred/TaskRunner.java}{dc372a} fix (this inconsistent name is fixed by implementation change)   \href{https://github.com/apache/hadoop/commit/7c2d77#diff-c0169961c9fbca7c0a7b3afb2049665a}{7c2d77} no deletion
\item  open() in HarFileSystem.java addition \href{https://github.com/apache/hadoop/commit/0201be46c298e94176ec6297e9d9cdba3afc2bbd#diff-685393e5e55e645ac340ea5bfd3b1cf1}{0201be}  no fix no deletion.
% \href{https://github.com/apache/hadoop/commit/5128a9a453d64bfe1ed978cf9ffed27985eeef36#diff-c889130fbb61593f9344d4455243a5ba}{5128a9a} fix \href{https://github.com/apache/hadoop/blob/0201be46c298e94176ec6297e9d9cdba3afc2bbd/hadoop-common-project/hadoop-common/src/main/java/org/apache/hadoop/fs/HarFileSystem.java}{0201be}
\item  setWorkingDirectory() in FTPFileSystem.java. addition \href{https://github.com/apache/hadoop/blob/3b85bd7c3391719624a261f061a67cc4356be477/hadoop-common-project/hadoop-common/src/main/java/org/apache/hadoop/fs/ftp/FTPFileSystem.java}{cd7157}  no fix no deletion.
%fix \href{https://github.com/apache/hadoop/commit/e09ea0c06ee1caa5a9ebae0a8f0273dfe04d05e5#diff-ff793a007e42565e9d1844ce96940948}{e09ea0c0}.  latest version \href{https://github.com/apache/hadoop/blob/3b85bd7c3391719624a261f061a67cc4356be477/hadoop-common-project/hadoop-common/src/main/java/org/apache/hadoop/fs/ftp/FTPFileSystem.java}{cd7157}
\item  startLocalOutput() in ChecksumFileSystem.java addition \href{https://github.com/apache/hadoop/blob/3b85bd7c3391719624a261f061a67cc4356be477/hadoop-common-project/hadoop-common/src/main/java/org/apache/hadoop/fs/ChecksumFileSystem.java}{cd7157} no fix no deletion
\item  invertedMinMax() in PoolManager.java addition  \href{https://github.com/apache/hadoop/commit/1daa81#diff-13924c43e3ff5852da014b5005422666}{1daa81} no fix no deletion
\item  ranAll() in JvmManager.java  addition \href{https://github.com/apache/hadoop/commit/55391f#diff-b7bcf8118ef56aa71a37a08b9479afd5}{55391f} no fix deletion \href{https://github.com/apache/hadoop/commit/ca1c68}{ca1c68}
\item  abort() in UserGroupInformation.java addition \href{https://github.com/apache/hadoop/commit/0c5734e4aca873f405fbf994e5fe7061e31731c8#diff-8da26f813ae9e87bbf0fb9abb349acc2}{0c5734}  no fix no deletion
\item  maximumFpRemove() in RetouchedBloomFilter.java  addition \href{https://github.com/apache/hadoop/commit/4ba168e4873c30574d18541b53b8821f62bd2589#diff-fa311023e9175bac1e31055102b7331f}{4ba168} no fix no deletion
\end{enumerate}
Object
\begin{enumerate}
\item  SequenceFile.Writer data in MapFile.java addition \href{https://github.com/apache/hadoop/commit/5128a9a453d}{5128a9}   fix \href{https://github.com/apache/hadoop/commit/fc7c8f9#diff-34d704a739ee5bdbee9bb5cd1426972b}{fc7c8f} no deletion.
\item Process sim in PipeMapRed.java  addition \href{https://github.com/apache/hadoop/commit/2453431f642db9d38058b0227fd7636c162020e0#diff-72f498fd913780670fc13711bc524734}{245343}   fix  \href{https://github.com/apache/hadoop/commit/ed3433072#diff-72f498fd913780670fc13711bc524734}{ed3433} no deletion
\item  FSDataInputStream sums in ChecksumFileSystem.java  addition \href{https://github.com/apache/hadoop/commit/cd7157784e5e5ddc4e77144d042e54dd0d04bac1#diff-16cbdb68a1f1e17dcc9f848ee6084e0c}{cd7157}  fix \href{https://github.com/apache/hadoop/commit/1c309f763be3dd2e3d7d1616d2c960ff80cf9b03#diff-16cbdb68a1f1e17dcc9f848ee6084e0c}{1c309f}  no deletion
\item  FileSystem repStore in RepositoryImpl.java addition \href{https://github.com/apache/jackrabbit/commit/a6b82e}{a6b82e}  fix  \href{https://github.com/apache/jackrabbit/commit/f51ed4d48a#diff-9751fd2ad72989dbc11c7caca47e907c}{f51ed4} deletion in type-use pattern \href{https://github.com/apache/jackrabbit/commit/f51ed4#diff-9751fd2ad72989dbc11c7caca47e907c}{f51ed4} complete deletion \href{https://github.com/apache/jackrabbit/commit/9cdb3c#diff-9751fd2ad72989dbc11c7caca47e907c}{9cdb3c}
\item SortedMap<String, OutputStream> pendingCreates in DFSClient.java bug addition \href{https://github.com/apache/hadoop/commit/3512203f6c54033db1d52118edf595e5b5e1335e#diff-ad9e40bbf27e54506a64a57c691acc01}{351220}   fix and deletion \href{https://github.com/apache/hadoop/commit/36f7c4360#diff-1c2cc53548a274cf6eff37f3ded5dbbb}{36f7c4} 
\item  FileObject webdavTmp in WebdavFileObject.java addition  \href{https://github.com/apache/commons-vfs/commit/c5451d949d67c415863565dcb56a6b2608a3aad0#diff-6ac9cecfbc1506096ed3445c48318795}{73e505}  fix and deletion \href{https://github.com/apache/commons-vfs/commit/507d9d2061d4ea8c4ed4c26a5aad4f18aa493e67?diff=unified#diff-5a9a853727565aea8ec4f5670cafa120}{507d9d}  %deletion \href{https://github.com/apache/commons-vfs/commit/507d9d2061d4#diff-8adfff94d4a9ad884d8367d5d25e8864}{507d9d}
\item  SpoolRepository outgoing in RemoteDelivery.java addition \href{https://github.com/apache/james/commit/6aa468ab069ce094027839b0282c47971598f28a#diff-53334ca0c55bca9fd6821a895f6ec46b}{6aa468}  bug fix and deletion \href{https://github.com/apache/james/commit/54cccd3#diff-53334ca0c55bca9fd6821a895f6ec46b}{54cccd} 
\item  PersistenceManager target in PersistenceCopier.java addition \href{https://github.com/apache/jackrabbit/commit/ff7a62c0a8768714f8c36e3f8f07d2f017eebbfe#diff-7df848bb75ab7d3df5738968da840306}{ff7a62} fix  \href{https://github.com/apache/jackrabbit/commit/d8b712#diff-7df848bb75ab7d3df5738968da840306}{d8b712}  no deletion
\item  FlushRequester flushListener in HRegion.java addition \href{https://github.com/apache/hbase/commit/e1da900df#diff-b9d8ad451ab3fd5f5ff8593268230822}{e1da90}  fix and deletion \href{https://github.com/apache/hbase/commit/f52130953245d93489a9c700c3b00eedbe70fdb9/src/main/java/org/apache/hadoop/hbase/regionserver/HRegion.java}{f52130} 
\item  Daemon responder in BlockReceiver.java addition \href{https://github.com/apache/hadoop/commit/a196766ea07775f18ded69bd9e8d239f8cfd3ccc#diff-9400d498326ceaca4b310cd3415277ef}{a19676}  fix \href{https://github.com/apache/hadoop/commit/d4fb8821#diff-649c4e46d99ae8011ff0fa0c118d9726}{d4fb88}  no deletion 
\item  File repositoryHome in FileJournalTest.java addition \href{https://github.com/apache/jackrabbit/commit/242f30ca639d0830e5ffe8f38c310453210934dd#diff-0ec8ddbe8d780a64761634b465905590}{242f30}  fix \href{https://github.com/apache/jackrabbit/commit/b3ba69bce1#diff-0ec8ddbe8d780a64761634b465905590}{b3ba69}    no deletion
  \end{enumerate}
%}
  \end{minipage}
 % \caption{Inconsistent method name detected with purity analysis and type-use pattern}
% \label{fig:purityExample}
 \end{figure*}

% As a result, developers did not notice that \codefont{flashListener} was a \codefont{FlashRequester} and forgot to pass it to \codefont{request} method, {causing a bug where a user cannot send request via Requester}. This bug was fixed in revision \codefont{d4fb88}.

%%Pure: 
%1. heartbeatCheck() in HeartbeatManager.java: 859056 https://github.com/apache/hadoop/commit/8590564dc56195cb2caa245e3ee1c06eca3938d3#diff-52728ad908d378250fa082c8a30113af. 
%2. receivePacket() in BlockReceiver.java: c74517 https://github.com/apache/hadoop/commit/c74517#diff-649c4e46d99ae8011ff0fa0c118d9726
%3. getFileChecksum() in DFSClient.java: d5a9a3 https://github.com/apache/hadoop/commit/d5a9a3#diff-3f9d4f0c9157be654273622926ae04b9
%4. obtainNewReduceTask() in JobInProgress.java: 1d8a1d https://github.com/apache/hadoop/commit/1d8a1d#diff-53b4c7b6b46b3778ebfa5ecdcb35521f
%5. fetchOutputs() in ReduceTask.java: 7e1fd3 https://github.com/apache/hadoop/commit/7e1fd3#diff-336c3fa4df86402ec7b5339c1dbac724
%6. checkLocalizedPath() in TestTrackerDistributedCacheManager.java: 939926c https://github.com/apache/hadoop/commit/939926c#diff-3de8a0425c49269f274f46497111dc80
%7. verifyDir() in TestDFSUpgradeFromImage.java: a11042 https://github.com/apache/hadoop/commit/a11042#diff-f471412017f4f6728224615c8362da5f 
%8. mapOutputLost() in TaskTracker.java: ec7719 https://github.com/apache/hadoop/commit/ec7719#diff-2bd0b9b3e70406484c416d876341fa61
%9. getEntries() in MetadataTable.java: bug fix and deletion https://github.com/apache/accumulo/commit/446a37a#diff-002fc1274cd98bf226ee8398551261a6 additiond in https://github.com/apache/accumulo/commit/8e4e6d6420e47f64b9fd54d9b6f5bc5b0b158b8b#diff-002fc1274cd98bf226ee8398551261a6
%10. getMetaTableRowResultAsSplitRegion() in ZKAssign.java: c9b028  https://github.com/apache/hbase/commit/c9b028862a61ee2a96fdef6b55c36b03939ceada#diff-53def65a3cf679a3f048ab71bcea9293

%9.  estimate() in PiEstimator.java: 509bce https://github.com/apache/hadoop/blob/509bcea8cf858a911a5285fe3acd0d000855e28a/src/examples/org/apache/hadoop/examples/PiEstimator.java

%%Impure:
%1. handleKind() in JobClient.java e17cec: https://github.com/apache/hadoop/commit/e17cec#diff-489fac1eb320e92dd65b62f00b67f71c
%2. startSkipping() in TaskInProgress.java d18d34e93: https://github.com/apache/hadoop/commit/d18d34e93#diff-7f17e003fb54ff97abf2007fbd6cdc61
%3. prepare() in TaskRunner.java 7c2d77: https://github.com/apache/hadoop/commit/7c2d77#diff-c0169961c9fbca7c0a7b3afb2049665a
%4. open() in HarFileSystem.java no fix. https://github.com/apache/hadoop/blob/0201be46c298e94176ec6297e9d9cdba3afc2bbd/hadoop-common-project/hadoop-common/src/main/java/org/apache/hadoop/fs/HarFileSystem.java
%5. setWorkingDirectory() in FTPFileSystem.java. no fix. cd7157 latest version https://github.com/apache/hadoop/blob/3b85bd7c3391719624a261f061a67cc4356be477/hadoop-common-project/hadoop-common/src/main/java/org/apache/hadoop/fs/ftp/FTPFileSystem.java
%6. startLocalOutput() in ChecksumFileSystem.java cd71577 no fix latest version https://github.com/apache/hadoop/blob/3b85bd7c3391719624a261f061a67cc4356be477/hadoop-common-project/hadoop-common/src/main/java/org/apache/hadoop/fs/ChecksumFileSystem.java
%7. invertedMinMax() in PoolManager.java no fix. 1daa81. https://github.com/apache/hadoop/commit/1daa81#diff-13924c43e3ff5852da014b5005422666
%8. ranAll() in JvmManager.java 55391f:  https://github.com/apache/hadoop/commit/55391f#diff-b7bcf8118ef56aa71a37a08b9479afd5
%9. abort() in UserGroupInformation.java 0c5734e https://github.com/apache/hadoop/commit/0c5734e4aca873f405fbf994e5fe7061e31731c8#diff-8da26f813ae9e87bbf0fb9abb349acc2
%10. maximumFpRemove() in RetouchedBloomFilter.java 4ba168e48 no fix. https://github.com/apache/hadoop/commit/4ba168e4873c30574d18541b53b8821f62bd2589#diff-fa311023e9175bac1e31055102b7331f
%%Object
%1. SequenceFile.Writer data in MapFile.java fc7c8f9 bug fix https://github.com/apache/hadoop/commit/fc7c8f9#diff-34d704a739ee5bdbee9bb5cd1426972b
%2. Process sim in PipeMapRed.java bug fix ed3433072 https://github.com/apache/hadoop/commit/ed3433072#diff-72f498fd913780670fc13711bc524734 additiond in https://github.com/apache/hadoop/commit/2453431f642db9d38058b0227fd7636c162020e0#diff-72f498fd913780670fc13711bc524734
%3. FSDataInputStream sums in ChecksumFileSystem.java 1c309f bug fix https://github.com/apache/hadoop/commit/1c309f763be3dd2e3d7d1616d2c960ff80cf9b03#diff-16cbdb68a1f1e17dcc9f848ee6084e0c additiond in https://github.com/apache/hadoop/commit/cd7157784e5e5ddc4e77144d042e54dd0d04bac1#diff-16cbdb68a1f1e17dcc9f848ee6084e0c
%4. FileSystem repStore in RepositoryImpl.java bug fix  https://github.com/apache/jackrabbit/commit/f51ed4d48a#diff-9751fd2ad72989dbc11c7caca47e907c
%5. SortedMap<String, OutputStream> pendingCreates in DFSClient.java bug fix and deletion https://github.com/apache/hadoop/commit/36f7c4360#diff-1c2cc53548a274cf6eff37f3ded5dbbb
%6. FileObject webdavTmp in WebdavFileObject.java bug fix and deletion https://github.com/apache/commons-vfs/commit/507d9d2061d4ea8c4ed4c26a5aad4f18aa493e67?diff=unified#diff-5a9a853727565aea8ec4f5670cafa120
%7. SpoolRepository outgoing in RemoteDelivery.java bug fix and deletion https://github.com/apache/james/commit/54cccd3#diff-53334ca0c55bca9fd6821a895f6ec46b additiond in https://github.com/apache/james/commit/6aa468ab069ce094027839b0282c47971598f28a#diff-53334ca0c55bca9fd6821a895f6ec46b
%8. PersistenceManager target in PersistenceCopier.java  bug fix  https://github.com/apache/jackrabbit/commit/d8b712#diff-7df848bb75ab7d3df5738968da840306 additiond in https://github.com/apache/jackrabbit/commit/ff7a62c0a8768714f8c36e3f8f07d2f017eebbfe#diff-7df848bb75ab7d3df5738968da840306
%9. FlushRequester flushListener in HRegion.java bug fix and deletion https://github.com/apache/hbase/commit/f52130953245d93489a9c700c3b00eedbe70fdb9/src/main/java/org/apache/hadoop/hbase/regionserver/HRegion.java additiond in https://github.com/apache/hbase/commit/e1da900df#diff-b9d8ad451ab3fd5f5ff8593268230822 
%10. Daemon responder in BlockReceiver.java bug fix https://github.com/apache/hadoop/commit/d4fb8821#diff-649c4e46d99ae8011ff0fa0c118d9726 
% File repositoryHome in FileJournalTest.java bug fix https://github.com/apache/jackrabbit/commit/b3ba69bce1#diff-0ec8ddbe8d780a64761634b465905590 additiond in https://github.com/apache/jackrabbit/commit/242f30ca639d0830e5ffe8f38c310453210934dd#diff-0ec8ddbe8d780a64761634b465905590

### 2015-11-18 weeklyReport/problem.tex
11-17

@@
 %\section{Problem 1}  
-\noindent{\bf{Proactively Recommending Code Examples to Reduce Integration Conflicts}}
+\noindent{\bf{Problem 1: Proactively Recommending Code Examples to Reduce Integration Conflicts}}
 
@@
 In this case, the source code example serves as the explicit origin for a reuse task which transforms a sequence of APIs with corresponding control structure to the target context~\cite{Frakes:reuseStatus05}.
+Existing code search engines always return multiple examples that are found based on the relevance to the user query rather than the ability to fit for the target context.
+For any selected example  with a number of structural dependencies, developers have to rely on their intuition to determine which related elements should be transformed to the target context .
+
+we propose an approach to  recommend  code examples that implement a queried feature based on their integration cost to the target context.
+Instead of using the entire code example, we extract salient program elements that might provide the main queried functionality, integrate these salient elements to the user-defined location, and proactively add related elements into the context with user interaction to resolve integration conflicts.
+
+%We evaluate our approach with the 27 trackable features from feature location benchmark~\cite{denys:FLBenchmark13, Denys:BanchmarkQuery13}.
+This benchmark extracts queries from commit message based on information retrieval approach.
+We use the queries associated with features, and manually select 3 keywords from these queries.
+
+%identify common API calls that provide the main feature across different code examples from code search engine, and
+% integrate this reusable example to the target context with a set of related elements that are necessary to implement the main feature.
+We assume that the overlapping API calls are the main features that the user intends to reuse based on the user query, and the related elements should be transformed to the target together with main features if they are data dependent and control dependent on the common functionalities in a common way across different examples.
+Figure~\ref{fig:system} illustrates the process of our system.
+Given a free-form query from users, our tool invokes code search engine  to obtain a list of partial programs by recovering links between code elements and informal resources, clusters these examples and extracts common structural facts (e.g., jQuery logical facts) with corresponding control structures for each cluster, identifies a set of related elements that interact with main elements in a common way,  constructs reuse task with both main elements and related elements and ranks them based on user's context, and finally integrates the reuse task selected by users to the target context.
+
+%However, there is no guarantee that a selected example will be appropriate until the integration results are examined~\cite{Holmes:reuseStudy09}.
+First, there exist multiple examples that provide desired features for the task.
+Recent study [5] shows that it is unlikely to find a ?perfect?
+example that provides all desired features for the reuse task, and the desired features are always scattered in different example variants.
+Thus even with the help of code recommendation tools, developers still need to manually investigate multiple recommended code examples that are found based on the rel- evance to the user query rather than the ability to fit for the target context, in order to find the common API calls that provide expected features.
+Second,
 
@@
 
+There are a number of tracking system that helps the development process, such as Bugzilla, JIRA, and Pull Request mechanism in Github.
+Our preliminary study shows that only X\% of all issues of Z Apache projects reported in JIRA are unique, and Y\% of all pull requests are unique within 22 projects that actively use pull requests reported by~\cite{Devanbu:PullMSR15}.
+Our tool can also be used to recommend a potential fix based on reported bug report or description in natural language.
+
+We first extract four types of information from these issue descriptions and corresponding comments: issue description in natural language, execution trace/bug report, code snippet, and diff patch.
+
+We evaluate our approach using the dataset from JIRA issue tracking system, and pull request in Github. 
 %\item \textbf{Example Integration Phase.} Our approach investigates the user's contexts to recommend the best-fit reuse task  considering the number of matched structural facts in target context.

### 2016-01-19 weeklyReport/problem.tex
dependency hell

--- 2015-10-20 weeklyReport/problem.tex
@@
-\section{Problem Statement}
+\section{Problem}  
+To obtain necessary functionality, developers often use third-party libraries.
+Due to the complexity of current software systems, the dependency issue arises when the system depend on different and incompatible versions of the same library.
+This issue, called  `dependency hell'~\cite{wiki:hell} may break other dependencies or push the problem to another set of libraries.
+We use an example to illustrate how the `dependency hell' causes a build error, how it is localized, how it is fixed in the next session.
 
-Problem: The code examples returned from code search engine or other code search tools are not structured.
+%\noindent{\bf{Problem }}
 
-%Reuse tasks involve multiple related classes and methods, yet code search engines do not help developers recognize the latent structure among related classes/methods.
+\section{Example}
 
-%Hypothesis: We can find and rank related elements by following the structural dependencies of seed API elements in code.
+ \begin{figure}[!htb]
+ \includegraphics{akka.jpeg}
+ \end{figure}
+\noindent{\bf{What is the `dependency hell'?}}
 
-Input: a set of code examples returned from code search engine.
+\input{example}
 
-Output: a list of code example clusters organized based on their structural similarity.
+We illustrate the building error caused by `dependency hell' in a Maven project shown in Figure~\ref{fig:shifu}.
+As shown in part A, the parent project uses akka 2.1.1 to initialize \codefont{ActorRef} (underline) by creating a new \codefont{Props} object.
+The developer Alice is asked to implement a new sub-module named as SparkPlugin using Spark framework.
+Without knowing that Spark is dependent on akka-2.2.3, she implements the entire sub-module with Spark-1.0.0, writes the tests, and fully tests the single submodule before integrating with the parent project.
+However, she encounters the building error shown as part (C) (The complete building error is shown at~\cite{shifu}).
 
-%Sub questions: Do reuse tasks involve multiple related classes and methods? Can existing tools find reusable examples that involve multiple related classes and methods?
+\noindent{\bf{How to localize `dependency hell'?}}
 
-%To answer these two subquestions, I search for the evaluation dataset for existing feature location/concern mining tools~\cite{Denys:FCA12, Hill:FindConcept07, Hassan:concernHistory10, Breu:DynamicAspect04} shown in Table~\ref{tab:concern},    reuse tools~\cite{Holmes:reuse07, Holmes:ASE09} shown in Table~\ref{tab:reuse}, and code search tools using free-form query ~\cite{sniff:Sen09, Portfolio:DenysICSE11, Sourcerer:SC14, Gvero:ICSE15, spotWork:ICSE14} shown in Table~\ref{tab:freeform}.
-We find that most medium-scale or large-scale reuse tasks involve multiple methods and classes,  and the developer should implement multiple methods and classes to finish the reuse task.
-Existing  code completion tools can complete a single method which involves in multiple API calls, yet they assume that all related APIs or  objects used in their suggested code snippet already exist.
-We argue that this assumption might not hold for a non-trivial reuse task, because developers need to implement the salient API calls that provide the main functionality as well as other related elements based on the latent structure.
+Starting from the \codefont{NoSuchMethodException}, she investigates the \codefont{akka.remote.RemoteActorRefProvider.<init>}  in akka-2.2.3 as declared in Spark's pom.xml and finds the static \codefont{Props.create} method shown in part (D).
+Alice get confused on the \codefont{NoSuchMethodException} and she has to use step-by-step debugging.
+She finally notices that the maven build system mistakenly uses akka-2.1.1 inherited from parent project, rather than the akka-2.2.3 that is required for Spark library.
 
-%Developers frequently use source code examples as the basis for interacting with an  application programming interface (API) to obtain the needed functionality~\cite{CodeSearch:FSE15}.
-In this case, the source code example serves as the explicit origin for a reuse task which transforms a sequence of APIs with corresponding control structure to the target context~\cite{Frakes:reuseStatus05}.
-During the process of reuse task such as `add undo and redo actions in my Graphics Editor', developers often query for a set of examples considering the task, and integrate examples that match the task into their system~\cite{Parsons:cognitiveReuse04}.
+\noindent{\bf{How to fix `dependency hell'?}}
 
-%Both location and integration of reusable examples are not trivial.
-For the phase of location, existing tools that search for specific API usage examples~\cite{MAPO:ECOOP09, Buse:apiICSE12, Export:DenysASE13, Sourcerer:SC14} might not be able to support such reuse tasks that always involve in multiple classes and related methods.
-As a result, developers always query general search engines like Google or expert sites like StackOverflow to investigate potential tutorials for desired features.
-These search engines will return a list of informal documentations and users have to search for source code elements in these resources.
-Although some linking recovery  tools~\cite{PeterACE:ICSE13, RecoDoc:ICSE12} can help identify a partial program in the form of code snippet, they are not  sufficient to create a pragmatic reuse plan as the main functionality is always interleaving with auxiliary ones and  it is unlikely to find a `perfect' example that provides all desired features for the reuse task~\cite{Holmes:reuseStudy09}.
-Considering that a single example is not enough for a given task, developers need to investigate multiple example variants manually for the desired features (i.e., common API calls).
-For the phase of integration, developers should not only  measure structural and semantic similarity between the example and target context for the main API calls that provide desired features~\cite{Cottrell:jigsaw08}, but also determine which unnecessary code should be eliminated to save maintenance cost~\cite{Holmes:ASE09, Holmes:reuse07} and which related elements should be transformed with structural correspondence~\cite{Cottrell:generalize07} to the target context.
-Unfortunately, for any selected example in non-trivial system, the number of structural dependencies to follow is much too large to be completely covered by developers.
-The partial programs~\cite{partialProgram:OOPSLA08} extracted from the location phase make it even harder to  tease out irrelevant elements  without knowing a full scenario of precise type information and method implementation details.
-Moreover,  the location and integration phase can be iterative as there is no guarantee that a selected example will be appropriate until the integration results are examined~\cite{Holmes:reuseStudy09}.
+  Alice has several options to fix this bug as below:
+\begin{enumerate}
+\item change akka version in parent class to 2.2+, which is not feasible as the parent project heavily uses akka and it requires tremendous effort for upgrading.
+\item  exclude all transitive dependencies inherited from parent project with the feature provided by Maven 3.2.2+~\cite{maven:note}, aiming to resolve dependency hell~\cite{maven:hell}.
+This approach is not feasible as well because SparkPlugin itself relies on the parent projects and Alice has to re-import all dependencies that the submodule uses.
+\item include both akka versions and enforce Spark to use akka-2.2.3.
+This approach is similar to the well-known side-by-side  mechanism used in NIX package manager for Linux-based system~\cite{nix}.
+This might fix the build error, but Alice is concerned that compiling both versions might increase the building time of the entire system.
+\item exclude akka-2.1.1 from the dependency declaration of Spark-1.0.0. Alice decides to use this solution as it won't have ripple effect on the rest of the system.
+\end{enumerate}
 
-%To overcome these challenges, we propose to automatically identify common API calls that provide the main feature across different partial program examples from informal documentation, and integrate this reusable example to the target context with a set of related elements that are necessary to implement the main feature.
-We assume that the overlapping API calls are the main features that the user intends to reuse based on the user query, and the related elements should be transformed to the target together with main features if they are data dependent and control dependent on the common functionalities in a common way across different examples.
-Figure~\ref{fig:system} illustrates the process of our system.
-Given a free-form query from users, our tool invokes code search engine  to obtain a list of partial programs by recovering links between code elements and informal resources, clusters these examples and extracts common structural facts (e.g., jQuery logical facts) with corresponding control structures for each cluster, identifies a set of related elements that interact with main elements in a common way,  constructs reuse task with both main elements and related elements and ranks them based on user's context, and finally integrates the reuse task selected by users to the target context.
+%To ensure that there does not exist any other transitive dependency that causes dependency hell, she tries maven-enforcer plugin which have the rule to ban all transitive dependencies~\cite{maven:enforcer}, yet the plugin outputs more than 100 conflicts.
+Alice gives up to kill all conflicts as (1) It is costly to exclude all conflicts, (2) it makes the maven hard to maintain, and (3) most of them might not be harmful for the system.
 
-%Our tool also lists a set of variants from multiple source code examples so that users can select features they prefer to reuse, and transforms chosen features to the target context.
+Using this example, we illustrate that  it is not easy to  localize dependency hell without knowing the entire dependency graph and it can be error-prone when trying to fix the error.
 
-%\item \textbf{Example Integration Phase.} Our approach investigates the user's contexts to recommend the best-fit reuse task  considering the number of matched structural facts in target context.
-After user's selection, our approach integrates the reuse task to the target context by transforming the unmatched structural facts based on matched facts in the context.
+\section{Approach}
 
-% \begin{figure*}[!htb]
-%    \centering
-%\includegraphics[width=1\textwidth]{fig/system.pdf}
-%       \caption{System process overview}
-%        \label{fig:system}
-%   \end{figure*}
+%There are some well-known solutions to this problem, they either ask developers to manually exclude all the transitive dependencies for a dependency (Solution 2) or include multiple versions in a side-by-side manner (Solution 3).
+Neither of them are perfect as described in the previous session.
+
+We propose an approach to check compatibility on the interfaces that use different versions for the same libraries, which has the possibility to introduce `dependency hell'.
+Instead of strict backward compatibility checker for the entire class~\cite{Welsch:backward12}, we regard it as safe if the used API is compatible for the other version in the current usage context.
+We make this trade-off because developers often embrace changes, making multiple versions incompatible to each other~\cite{bogart:backward}.
+To save build time and space,  we include multiple versions of the files from the same library only if they are incompatible with each other, instead of maintaining multiple versions for the same library at the same time.
+To save time for analysis, we only consider the API calls when it has the possibility to generate `dependency hell', since there is no need to check the dependency issue if the libraries are consistent used in the system with a single version.

### 2016-01-25 weeklyReport/problem.tex
end of build error idea,switch to repair.1-21-16

@@
 This issue, called  `dependency hell'~\cite{wiki:hell} may break other dependencies or push the problem to another set of libraries.
+When developers try to introduce a new library or upgrade existing ones, then other applications on their system might suddenly break as the newly-introduced libraries are not backward-compatible to the existing libraries.
 We use an example to illustrate how the `dependency hell' causes a build error, how it is localized, how it is fixed in the next session.
@@
 
+\section{Related Work}
+
+When two versions of the same library occur, Maven selects the closest library  in the tree of dependencies by default~\cite{maven:depend} (e.g., if dependencies for A, B, and C are defined as A -> B -> C -> D 2.0 and A -> E -> D 1.0, then D 1.0 will be used when building A because the path from A to D through E is shorter).
+User is able to manually exclude or force Maven to use a specific version, but the correctness is not guaranteed~\cite{maven:note}.
+Maven Enforcer Plugin checks a set of build rules including a Ban-Transitive-Dependency rule that detects all transitive dependencies conflicts and force users to resolve all conflicts.
+The Enforcer Plugin only checks the \codefont{groupid}, \codefont{artifactid}, and \codefont{version} declared in the configuration file (\todo{Lisa: though I don't know if we need to check semantics or compatibility of different versions, I leave this limitation for future reference}), and it does not help developers fix the conflicts without breaking any other parts of the system.
+The majority of existing build systems model dependencies identical to Maven.
+Examples include Gradle, MSBuild, Make, and CloudMake.
+The features that make them different are unrelated to dependency management, but on syntax of build scripts and parallelization.
+
+Bazel is a new build system developed by Google that advertises parallelization and correctness~\cite{bazel:depend}.
+Bazel does not allow transitive dependency and only reads dependencies listed in from the root dependency declaration file.
+This means that if your project (A) depends on another project (B) which list a dependency on project C in its WORKSPACE file, both transitive dependencies from B and C should be added to the WORKSPACE file.
+This can balloon the file size, but hopefully limits the chances of having one library include C at version 1.0 and another include C at 2.0.
+But they also assume that users can provide correct configuration and select correct versions of libraries.
+
+Package managers in operating system also encounter similar dependency management problem.
+To deal with destructive upgrade and multi-distribution support in Linux products, Nix ~\cite{nix} provides a co-existing package management mechanism to store a source package in its own directory, instead of a global location that share across the entire system.
+However, this might not work in build system like Maven, as with transitive dependencies, the graph of included libraries can quickly grow quite large~\cite{maven:depend}.
+
 \section{Approach}
@@
 
-We propose an approach to check compatibility on the interfaces that use different versions for the same libraries, which has the possibility to introduce `dependency hell'.
+%We propose an approach to verify the safety of upgrading and
+
+%We propose an approach to check compatibility on the interfaces that use different versions for the same libraries, which has the possibility to introduce `dependency hell'.
 Instead of strict backward compatibility checker for the entire class~\cite{Welsch:backward12}, we regard it as safe if the used API is compatible for the other version in the current usage context.

### 2016-03-10 weeklyReport/problem.tex
repair algorithm

--- 2016-01-19 weeklyReport/problem.tex
@@
-\section{Problem}  
-To obtain necessary functionality, developers often use third-party libraries.
-Due to the complexity of current software systems, the dependency issue arises when the system depend on different and incompatible versions of the same library.
-This issue, called  `dependency hell'~\cite{wiki:hell} may break other dependencies or push the problem to another set of libraries.
-We use an example to illustrate how the `dependency hell' causes a build error, how it is localized, how it is fixed in the next session.
+\section{Program Repair}
 
-%\noindent{\bf{Problem }}
+\section{Improvement Idea}
 
-\section{Example}
+\noindent{\bf{Use NL to guide the search for program repair.
+}}  I manually check 105 defects/changes and their generated patches, I find that a) some plausible but not correct patches for defects are unrelated to bug descriptions in issue tracking system, b) there are a number of defects (30/69) that current auto-repair tools cannot generate any patches (neither plausible nor correct), but have the potential to be (partially) repaired with more 'specification' given by bug description.
+I argue that apart from passed and failed test cases, user is able to provide bug description in natural language that is also a special kind of specification to guide the search for the program repair.
 
- \begin{figure}[!htb]
- \includegraphics{akka.jpeg}
- \end{figure}
-\noindent{\bf{What is the `dependency hell'?}}
+For example, php-309453-309456 (commit 8deb11c, bug #54291), none of auto-repair tools generate any fix for this bug in the benchmark, these tools include SPR [1](see its generated patches), Prophet [2], GenProg [4], AE [5], Kali [3], RSRepair [6] based on the evaluation, (PAR is unknown) .
 
-\input{example}
+This bug is caused by a null pointer exception and developer fixes it with correct exception handling.
+The reason why none of these tools handle this defect is because, 1) SPR fails to use control-flow transformation schema to this two-statement fix due to large search space, 2) Prophet does not learn this fix based on other fix patches,  3) There is no similar fix statement around thus GenProg, AE, and RSRepair fail to find the repair, 4) it adds code thus Kali that relies on statement deletion cannot fix it.
+In summary, all of these tools rely sole on test suite or cross-application history, but fail to understand what kind of defect user finds and what kind of repair user prefer.
 
-We illustrate the building error caused by `dependency hell' in a Maven project shown in Figure~\ref{fig:shifu}.
-As shown in part A, the parent project uses akka 2.1.1 to initialize \codefont{ActorRef} (underline) by creating a new \codefont{Props} object.
-The developer Alice is asked to implement a new sub-module named as SparkPlugin using Spark framework.
-Without knowing that Spark is dependent on akka-2.2.3, she implements the entire sub-module with Spark-1.0.0, writes the tests, and fully tests the single submodule before integrating with the parent project.
-However, she encounters the building error shown as part (C) (The complete building error is shown at~\cite{shifu}).
+Bug #54291 Crash in spl_filesystem_object_get_path
+Description:
+------------
+The attached code crashes on PHP5.3 SVN. Since this is pretty sure only a null-pointer deref, reporting this as public (non-security related)...
+Actual result:
+--------------
+==2043== Invalid read of size 8
+==2043==    at 0x6586DB: spl_filesystem_object_get_path (spl_directory.c:168)
+...
+The underlined line causes an null-pointer exception: intern->u.dir.dirp is null. Developer added exception handling in their fix. 
+PHPAPI char* spl_filesystem_object_get_path(spl_filesystem_object *intern, int *len TSRMLS_DC) /* {{{ */
+{
+#ifdef HAVE_GLOB
+     if (intern->type == SPL_FS_DIR) {
+           if (php_stream_is(intern->u.dir.dirp ,&php_glob_stream_ops)) {
+                  return php_glob_stream_get_path(intern->u.dir.dirp, 0, len);
+                    }
+                     }
+#endif
+                      if (len) {
+                            *len = intern->_path_len;
+                             }
+                              return intern->_path;
+} /* }}} */
+static void spl_filesystem_dir_open(spl_filesystem_object* intern, char *path TSRMLS_DC){
+    if (EG(exception) || intern->u.dir.dirp == NULL) {  
+            intern->u.dir.entry.d_name[0] = '\0';      intern->u.dir.entry.d_name[0] = '\0';
+             +  if (!EG(exception)) {
+                  +   /* open failed w/out notice (turned to exception due to EH_THROW) */
+                   +   zend_throw_exception_ex(spl_ce_UnexpectedValueException, 0
+                    +    TSRMLS_CC, "Failed to open directory \"%s\"", path);
+                    +  } 
+                    I hypothesize that bug reports such as "Crash in spl_filesystem_object_get_path " should give us hint based on NL semantic parsing: <type>crash</type> in <place>spl_filesystem_object_get_path</place>
 
-\noindent{\bf{How to localize `dependency hell'?}}
+                    And this information should guide us to search for a better program repair.
 
-Starting from the \codefont{NoSuchMethodException}, she investigates the \codefont{akka.remote.RemoteActorRefProvider.<init>}  in akka-2.2.3 as declared in Spark's pom.xml and finds the static \codefont{Props.create} method shown in part (D).
-Alice get confused on the \codefont{NoSuchMethodException} and she has to use step-by-step debugging.
-She finally notices that the maven build system mistakenly uses akka-2.1.1 inherited from parent project, rather than the akka-2.2.3 that is required for Spark library.
-
-\noindent{\bf{How to fix `dependency hell'?}}
-
-  Alice has several options to fix this bug as below:
-\begin{enumerate}
-\item change akka version in parent class to 2.2+, which is not feasible as the parent project heavily uses akka and it requires tremendous effort for upgrading.
-\item  exclude all transitive dependencies inherited from parent project with the feature provided by Maven 3.2.2+~\cite{maven:note}, aiming to resolve dependency hell~\cite{maven:hell}.
-This approach is not feasible as well because SparkPlugin itself relies on the parent projects and Alice has to re-import all dependencies that the submodule uses.
-\item include both akka versions and enforce Spark to use akka-2.2.3.
-This approach is similar to the well-known side-by-side  mechanism used in NIX package manager for Linux-based system~\cite{nix}.
-This might fix the build error, but Alice is concerned that compiling both versions might increase the building time of the entire system.
-\item exclude akka-2.1.1 from the dependency declaration of Spark-1.0.0. Alice decides to use this solution as it won't have ripple effect on the rest of the system.
-\end{enumerate}
-
-%To ensure that there does not exist any other transitive dependency that causes dependency hell, she tries maven-enforcer plugin which have the rule to ban all transitive dependencies~\cite{maven:enforcer}, yet the plugin outputs more than 100 conflicts.
-Alice gives up to kill all conflicts as (1) It is costly to exclude all conflicts, (2) it makes the maven hard to maintain, and (3) most of them might not be harmful for the system.
-
-Using this example, we illustrate that  it is not easy to  localize dependency hell without knowing the entire dependency graph and it can be error-prone when trying to fix the error.
-
-\section{Approach}
-
-%There are some well-known solutions to this problem, they either ask developers to manually exclude all the transitive dependencies for a dependency (Solution 2) or include multiple versions in a side-by-side manner (Solution 3).
-Neither of them are perfect as described in the previous session.
-
-We propose an approach to check compatibility on the interfaces that use different versions for the same libraries, which has the possibility to introduce `dependency hell'.
-Instead of strict backward compatibility checker for the entire class~\cite{Welsch:backward12}, we regard it as safe if the used API is compatible for the other version in the current usage context.
-We make this trade-off because developers often embrace changes, making multiple versions incompatible to each other~\cite{bogart:backward}.
-To save build time and space,  we include multiple versions of the files from the same library only if they are incompatible with each other, instead of maintaining multiple versions for the same library at the same time.
-To save time for analysis, we only consider the API calls when it has the possibility to generate `dependency hell', since there is no need to check the dependency issue if the libraries are consistent used in the system with a single version.
+                    Q: Any prior works that use NL in program repair?
+                    A: From the best of my knowledge (and based on a latest Program Repair Bibliography [13]), we don't have any tools that try to understand the natural language meaning in bug report and use it in program repair.
+                    Q: Why NL -semantic parsing can provide more information that test cases?
+                    A: NL in API document has been used to generate specification [17], indicating that NL has the potential to generate specification.
+Bug report is different from API document, but the idea is similar.
+                    Q: Why choosing semantic praising ?
+                    A: NL-based Software Analysis has been applied to many applications [18], yet most of them are confined to understanding the POS tagging properties (such as verb, noun) [17], and forget to understand the semantic relationship between each entity, e.g., <type>crash</type> in <place>spl_filesystem_object_get_path</place>
+                    means that there is an error type--'crash' happened in the method spl_filesystem_object_get_path

### 2016-04-22 weeklyReport/approach.tex
evaluation

--- 2015-10-13 weeklyReport/approach.tex
@@
+%\input{dataset_table}
 \section{Approach}
 
-To identify methods that implement concerns, I build a prototype which invokes Code Search Engine (CSE) API and analyzes the results from CSE using partial program analysis~\cite{partialProgram:OOPSLA08}.
-I select SearchCode~\cite{SearchCode} because it is an open source code search engine with over 7000 projects from  Github, Bitbucket, Google Code, and Sourceforge, with complete API documentations.
-To identify queried features in the returned source code,  I use the mean of TF-IDF weight  for each query term as a weighting factor and select top k (k=5) methods that are related to the given query.
-This approach is similar to prior works that use  IR~\cite{Denys:FCA12} and NL analysis~\cite{Hill:FindConcept07} for feature location.
-I choose IR approach because other approaches require history or structural analysis that might not be feasible for partial program.
-TF-IDF =  $avg( \log (1 + f_{t,d}) \times  \log \frac {N} {n_t}), f_{t,d}$ is the frequency of term $t$ in method $d$, $N$ is the total number of methods, $n_t$ is the number of methods that have the term $t$.
+%The Resource Description Framework (RDF) [26] is the data-model for representing meta-data in the Semantic Web.
+The RDF data-model formalizes meta-data based on subject ?
+predicate ?
+object triples, so called RDF statements.
+
+\subsection{Evaluation Dataset}
+
+We collect K defects from student-written versions of Java Program with intricate faults in nested loops and recursive data structure.
+This section discusses how we construct the dataset, the subjects used in the experiment, and how we categorize the defects.
+
+\noindent{\textbf{Methodology.
+}}We collect K defects from high-level Data Structure course with an enrollment of 99 students (EE 422C, at UT Austin).
+For each of the 19 pop quizzes, students are given a specification and two JUnit test cases that their program should pass and they need to write a Java program that satisfies the specification and passes test cases in half an hour.
+The pop quizzes covers the topic described last week and students have one week to review the concept before the pop quizzes.
+During the quiz, students  are not allowed to use the Internet or any Integrated Development Environment.
+They need to write down code in paper based on the given material.
+The defects are collected and manually classified based on program equivalence.
+We manually isolate the defects such that each defect is different from correct program only with a range of input for a specific field.
+ We discard the defects that occur only once to eliminate random error.
+We then input these defects and test them against corresponding test suite generated by Korat, a symbolic execution tool that automatically generates all test cases within a given bound.
+Korat generates M test cases in total for 18 problems.
+
+\noindent{\textbf{Subjects.  }} The dataset consists of  four basic data structures and three sorting algorithms.  
+\begin{enumerate}
+\item BST: Binary Search Tree  is a special binary tree that the key in each node must be greater than all keys stored in the left sub-tree, and smaller than all keys in right sub-tree.
+We check insert operation and three traversal approaches: in-order, pre-order, and post-order.
+Our test suite covers all test cases up to seven nodes, which leads to all cases in binary search tree up to three layers.
+\item LL: Sorted Linked List  is a linear collection of data elements in ascendent order in which  nodes can point to the next node by means of a pointer. 
+%Our specification defines a sentinel header for the linked list whose next field points to itself for an empty linked list.
+If the linked list is not empty, the next field for the last element will point to the header.
+Students are asked to finish insert and reverse operations as well as a method that validates whether the list has loop or not.  Our test suite covers all test cases up to three nodes.  
+\item DLL: Doubly Linked List  is a linked data structure which consists of a set of sequentially linked nodes.
+Each node has next and previous field, pointing to its next node and previous node correspondingly.
+We adapt the implementation of \codefont{java.util.PriorityQueue} in \codefont{openjdk version 6-27}.
+%The list consists of a sentinel header.
+If the list is empty, both the header's next field and previous field point to header itself.
+Otherwise, the header's previous field points to the last elements in the list, and this last elements' next field points to the header.
+Our test suite covers all test cases up to three nodes.
+
+\item Heap: MinHeap is a specialized tree-based data structure whose parent node is always smaller than its children.
+Students are required to finish insert and remove operations.
+They are also required to implement sorting algorithm to convert an unsorted array to a MinHeap.
+Our test suite covers all test cases up to seven nodes.
+
+\item Sorting: We check three sorting algorithms: Bubble Sort, Quick Sort, and Merge Sort.
+Bubble Sort requires two loops while Quick Sort and Merge Sort requires recursive structure.
+We verify the program with up to five numbers.
+
+\end{enumerate}
+
+\noindent{\textbf{Categorization.
+}}  We categorize the defects into omission error (should assign a value but miss the assignment) and commission error (assign a value but assign another value).
+We further classify these errors into method-level and path-level  with respect to \todo{....
+If a field value should be changed but is not changed by applying a method, we regard it as a method-level omission error.
+Similarly, if a field value should be changed but is not changed within a given block, but it is correctly set for all the inputs that do not execute that block, we regard it as block-level omission error.
+}
+
+\subsection{Comparison with other Program Repair Tools}
+
+We manually convert defects to C and compare our efficacy with three existing program repair tools: GenProg, SPR, and Angelix.
+
+\begin{table*}[ht]
+\begin{center}
+\caption{Evaluation Dataset }
+\label{tab:evalSubject}
+\vspace{1mm}
+\scriptsize{
+\begin{tabular*}{1\textwidth}{@{}c|r|cc|cccc|cccc|cccc@{}} 
+&Subject		&LOC	&\# tests 	&\#bug	& ratio	&\tool&G/S/A	&\#Omission & ratio	&\tool&G/S/A	&\#Omission & ratio	&\tool&G/S/A		 \\\midrule
+%1&BST.insert	&31		&		& 		&		&		&2		&BST.post		&37		&		&		&\\ 
+%3&BST.in		&20		&  		&		&		&		&4		&BST.pre		&21		&		&		&\\
+% 5&LL.insert	&		&		&		&		&		&6		&LL.remove 	&		&		&		& \\ 
+%7&LL.reverse	&		&		& 		&		&		&8		&LL.hasLoop	&		&		&		& \\ 
+%9&DLL.hasLoop&		&		&		&		&		&10		& DLL.remove	&		&		&		& \\ 
+%11&DLL.addFirst&		&		&		&		&		&12		& DLL.addLast	&		&		&		& \\ 
+%13&Heap.insert	&		&		&		&		&		&14		&Heap.remove	&		&		&		& \\ 
+%15&Heap.sort	&		&		&		&		&		&16		&Sort.bubble	&		&		&		& \\ 
+%17&Sort.merge&		&		&		&		&		& 18		&Sort.quick	&		&		&		& \\ 
+\end{tabular*}
+ \label{tab:dataset}
+}
+ \end{center}
+\end{table*}

### 2016-05-13 tmp/intro.tex
intro

\section{Introduction}

%Programmers spend tremendous efforts dealing with bug fixing.

%
 Automatic program repair is the  process of modifying the program if it does not satisfy the specification in the form of constraints~\cite{divya:tacas11},  pre- and post- conditions~\cite{autofix:tse14}, or test suites~\cite{par:icse13, angelix:icse16}.  The output of the repair task is an alternative implementation that meets the specification. The last few years have seen a lot of progress in automatic program repair~\cite{genprog:tse12, Debroy:icst10, spr:fse15}.  These approaches try to correct the faulty program by mutating suspicious statements~\cite{Debroy:icst10},   applying evolutionary algorithm to search for repair candidates~\cite{genprog:tse12}, inferring conditional substitutions systematically~\cite{spr:fse15}, or leveraging  symbolic analysis and constraint solving to find a repair~\cite{semfix:icse13}. %Automatic program repair usually consists of two general phases: fault localization that identifies the root cause of faults and repair inference that generates desired functions. 
These tools, however,  
are confined to inferring new expressions for conditions~\cite{spr:fse15, nopol:cstva14} or reusing existing statements~\cite{genprog:tse12}. \todo{They have limited repairability to fix faults resulting from missing statements  that do not exist in the current context.} Due to the large search space of repair candidates,  it remains a challenge to synthesize a correct program repair efficiently at the statement level.

We present \tool, a program repair tool that addresses this challenge by translating a faulty program to a partial non-deterministic implementation and leveraging off-the-shelf program synthesizer to fill in the ``holes'' of the partial program. If there exists a replacement that  satisfies all test assertions,  the synthesizer will return this concrete substitution as a program repair.

To speed up our repair process, we rank suspicious program locations using the invocation order of  statements and  spectra-based fault localization technique~\cite{tarantula:ase05}.  We prioritize program locations that are called later during executions leading to failing test assertions. These ``later'' locations allow us   to reuse as much of the original implementation as possible and reduce the size of expressions given to subsequent expensive techniques.

For each suspicious location, \tool introduces  non-deterministic placeholders based on pre-defined  repair skeletons called ``repair hypotheses''.  The repair  hypothesis for an assignment is a partial statement with expression candidates  and  the assignment combinator ``\codefont{=}''.   We collect all  candidates of a specific type. These candidates are derived from visible variables with no more than a small size of field dereferences.    For example, using no more than two field dereferences, the expressions of the type \codefont{int} derived from the variable \codefont{LinkedList l}  are \{\codefont{l.size, l.head.element}\}.

Lastly, \todo{the non-deterministic  program with candidates  is verified by the Sketch synthesizer with the SAT solver~\cite{sketch:sttt13} against  the  given test suite. }   If there exists a concrete substitution for each ``hole'' such that the replaced program  satisfies all test assertions, \tool  returns this substitution as a ``correct'' repair with respect to the user-provided test suite. To fix bugs at multiple locations,  \tool incrementally  eliminates failing test assertions and generates new hypotheses based on the updated program.

We evaluate \tool on 35 faults from students' pop quizzes in  7 data structure subjects. To generate program repairs for faulty programs, we  use bounded exhaustive test suite generated by the  constraint-based test input generation tool---Korat~\cite{korat:issta02}.  
The experiment illustrates that  \tool is able to generate program repairs for  missing conditions and statements.  We also demonstrate that these faults are hard to fix using state-of-the-art program repair tools,  such as SPR~\cite{spr:fse15} and Genprog~\cite{genprog:tse12}.  SPR generates no correct fix while GenProg generates two correct fixes based on the exhaustive test suite. \tool successfully generates 30 correct fixes with the exhaustive test suite and 14 correct repairs with a subset of the exhaustive test suite. The results can be found at~\cite{git:compareRepo}.

In summary, we make the following contributions:

\begin{itemize}
\item \textbf{Fault Localization}.  We present a fault localization technique  considering both the invocation order and the spectra-based suspiciousness value~\cite{tarantula:ase05}. 
\todo{Our experiment shows that this approach is in practice sufficient to save calls to the synthesizer and prune  repair candidates. }

\item \textbf{Repair Hypothesis Generation}.  We introduce two  repair hypotheses to fix faulty assignments and if-conditions followed by return statements that return true or false. The placeholders in a hypothesis are replaced by expression candidates within a given bound.  Therefore, \tool is not confined to generating repairs at the expression level~\cite{nopol:cstva14, spr:fse15}, rather, it   creates new statements that do not exist in the current program.  It can also incrementally fix  faults at multiple locations based on the test suite.

\item \textbf{Comparison Results}. We demonstrate \tool's efficacy to repair faulty assignments and if-return statements  with a benchmark of 35 faults from students' data structure subjects. The result shows that for these small but complex programs,  \tool can effectively repair errors  due to  missing statements and faults in multiple locations. Our comparison with general-purpose repair tools  illustrates that these tools are not as sufficient as \tool in addressing these errors.

\end{itemize}

%The paper is organized as follows: We first present an motivating example to illustrate the problem in Section~\ref{sec:motivate}. In Section~\ref{sec:approach}, we describe  our approach that  prioritizes fault locations and generates repair hypotheses. We evaluate the repairability of \tool  and the effectiveness of the ranking strategy in Section~\ref{sec:eval}, followed by the description of other techniques of program repair and program synthesis in Section~\ref{sec:related}. We discuss the threads to validity in Section~\ref{sec:validity} and conclude in Section~\ref{sec:conclude}. 
% \codefont{Entry} that can be derived with visible 
%variables: \codefont{list.head, entry, entry.previous,} and \codefont{entry.next}.

### 2017-10-01 sketchAPI/paper/algorithm.tex
rename ase17

\begin{algorithm}[t!]
\small
\SetKwInOut{Input}{Input}
\SetKwInOut{Output}{Output} 
\SetKwProg{Prog}{Title}{ is}{end}
\SetKwProg{Fn}{Function}{ is}{end}
\SetKw{New}{new}
\SetKw{Throw}{throw}
\SetKw{Continue}{continue}
\SetKwIF{Trying}{Catch}{Catching}{try}{}{catch}{}{catch}{}%
%\SetKwIF{Try}{Catch}{try}{catch}{}%
\SetKwRepeat{Do}{do}{while}{}{}%
\Input {Maximum Length of the sequence $len$, Input arguments $args$}
\Output{ API Sequence candidate $sequence$ and the Return Value $returnVal$ }
\SetKwProg{Fn}{Function}{ is}{end}
\Fn{ genAPISequence (hole)  }{
rule $\leftarrow$ genConstraints(hole.len).choose()\label{line:chooseRule}\;
sequence  $\leftarrow  \varnothing$, args $\leftarrow$ hole.args\;
\For {int i=0; i$<$rule.stmt; i++}{
call $\leftarrow $ genCall(rule, hole, i)\label{line:genCall}\;
\Trying{}{ 
res $\leftarrow$ invoke(call, args)\;  
args $\leftarrow$  args $\cup$ res\;  }
\Catch{Exception e}{\Throw BacktrackException\label{line:genBacktrack};}
sequence $\leftarrow$ sequence  $\cup$  call\;
\Return $\langle$sequence, getReturnVal(rule, args)$\rangle$;
}}
\Fn{genCall(rule, hole, i)}{
\tcp{Generate API sketch}\
\If{hole.mtdCandidates ==  $\varnothing$}{
methods $\leftarrow$ fetchMethods(hole.sourceTypes)\label{line:fetchMethod}\;
\ForEach{ m $\in$ methods}{\If{violateConstraint(hole, rule, i)}{\Continue;}
%\If{cannotFitRequiredArgs(m, hole.args)}{\Continue;}
hole.mtdCandidates $\leftarrow $ hole.mtdCandidates $\cup$ m;
} 
}
\tcp{Complete expressions holes in methods}\
method $\leftarrow $ hole.mtdCandidates.choose()\;
call $\leftarrow$fillMethod(method, hole, i, rule).choose()~\label{line:fillExpr}\;
\Return call;
}
\Fn{ execute (hole)  }{
\If{hole.sequence==null}{\label{alg:candNull}
hole.len $\leftarrow$ hole.len $== -1 ?$ b: hole.len\label{line:holeLen}\;
$\langle$sequence, returnVal$\rangle  \leftarrow$ genSequence(hole)\;
hole.sequence $\leftarrow$ sequence\;
\Return returnVal;
}\Else{
\Return invokeAndReturn(hole);
}
}
\Fn{ genConstraints ($len$) \label{line:genrule} }{
\tcp{\#stmt, \#return, \#consume, \#repetition}
List$<$int[]$>$ rules $\leftarrow   \varnothing$\;
\For{int stmt=1; stmt$<$len; stmt++}{
\For{int rtn=stmt; rtn$>$0; rtn$--$}{\For{int vc=1; vc$<$stmt; vc++}{
\For{int rep=1; rep$<$stmt; rep++}{
rules $\leftarrow $ rules $\cup$ \{stmt, rtn, vc, rep\};
}}}}
sort(rules)\;
\Return rules;
}
\caption{API Candidate Generation}
\label{alm:genCandidate}
\end{algorithm}

### 2017-10-01 sketchAPI/paper/approach.tex
rename ase17

\section{Approach}\label{sec:approach}
\input{algorithm}

We describe our test-execution-driven sketching for API calls in this section. We first show how we generate API candidates for each hole based on our prioritization strategies, and then describe how we leverage execution-driven sketching to synthesize a desired API sequence.

\subsection{API Candidates Generation}

This section describes how we dynamically generate candidates for API sequences when the test execution first reaches the ``hole''.

\noindent{\textbf{Generating Candidates During the Test Execution. }}  Shown as Algorithm~\ref{alm:genCandidate},  given a maximum length of the method invocation and a set of input arguments provided by users, \tool first generates a list of prioritized constraints to divide the API generation search space into multiple smaller spaces which only generates API sequences satisfying specific constraints.  The procedure of constraint generation will be described in the Section~\ref{sec:prioritize}.  Based on these prioritized constraints, \tool assigns each constraint a unique identifier, which is its index in the constraint vector.  When \tool performs sketching, it dynamically selects a constraint identifier with non-deterministic \codefont{choose()} operator (line~\ref{line:chooseRule}) and generates API candidates based on the chosen constraint. \tool further incrementally selects  methods based on the number of API calls defined in the constraint ($rule.stmt$).  Once \tool selects a single method in the sequence, it tries to execute this  selected method using reflection. If this method can be executed without throwing runtime exceptions,  \tool records the return value (if the invoked method has any),  updates the argument list with the generated intermediate value, and inserts this method into the API sequence. If the execution encounters any runtime exception, \tool backtracks immediately, and selects the next candidate in the candidate vector (line~\ref{line:genBacktrack}). The detailed backtracking procedure will be described in the Section~\ref{sec:backtrack}. If an API sequence candidate is successfully generated, \tool updates the ``hole'' with the generated sequence, and provide the return value for the initial execution.

\noindent{\textbf{Single Method Generation. }}    To choose a single method invocation, \tool generates method candidates based on the given constraint and selects receiver objects and parameters for the method candidate with given arguments or intermediate values from previous method invocations. \tool first collects all  source types declared by users and fetches all methods of these types using reflection (line~\ref{line:fetchMethod}). Note that the method collection process can be rather expensive if given a large amount of source types, thus we only collect these methods once and reuse them for each re-execution.   These methods are further filtered by the given constraint. In addition, if there does not exist a given argument or intermediate value with the type of a parameter in the method \codefont{m}, this method will not be considered because one of its parameters cannot be completed by the given arguments or intermediate values generated from previous method invocations.

After \tool generates a vector of method candidates, it assigns each candidate a unique identifier as its index in the candidate vector and dynamically selects a  candidate identifier with non-deterministic \codefont{choose()} operator. \tool further recursively generates candidates (given arguments and intermediate values) for  receiver objects and parameters of this selected method, and non-deterministically selects candidates to complete the chosen method call (line~\ref{line:fillExpr}). \tool then returns this generated method call, validates its correctness by invoking it using reflection,  and incrementally inserts more invocations into the API sequence.

Following the same standard with other API synthesis tools~\cite{isil:sypet17,  codehint:icse14}, we only consider one method invocation for each statement, e.g., \tool only considers a method call \codefont{iterator.next()} for one statement, but will not consider method chains like  \codefont{iterator.next().toString()} when it synthesizes a single method invocation. The method chain will be represented as multiple API calls: \codefont{Object obj = iterator.next()} and \codefont{String str = obj.toString()}.  Similar to \spt,   \tool currently only supports variables as receiver objects and parameters, without considering  field dereferences derived from these variables (e.g., field dereferences like \codefont{node.val} while \codefont{node} is an element in a linked list and \codefont{val} is the integer value that the node contains). Note that the execution-driven sketching engine~\cite{sketch4j:spin17} we use as our backend supports the generation of field dereferences using a breath-first iteration and the reflection. We envision that the extension to support field dereferences can be straightforward by inserting these fields into candidate vectors of expressions used in the method.

\noindent{\textbf{Executing with Selected Candidates. }}  Once the ``hole'' has been initialized, the generated API sequence will be used consistently across all test cases. For instance, if there exists an API sequence ``hole'' inside a while-loop, \tool only generates candidates for the API sequence when the test execution first reaches the ``hole'' in the while-loop body, and the selected  sequences will be used across all executions of the while-loop. Yet if the while-condition is evaluated to \codefont{false}, the test execution will not reach the ``hole'' inside the while-loop body, thus no new search space will be generated.  Users may specify the maximum number of method invocations (line~\ref{line:holeLen}). By default, we set a pre-defined bound for the maximum number of statements as 4, and make this bound configurable for end users.

 \input{algorithm_sketch}
\subsection{Prioritization Strategies}\label{sec:prioritize}

This section describes how we generate prioritized constraints to divide the API generation problem to multiple subproblems that satisfy different constraints. Shown as 
the method \codefont{genConstraints()} starting from line~\ref{line:genrule} in Algorithm~\ref{alm:genCandidate}, \tool generates 4 elements that will be used to prioritize the API sequence candidates: the number of API invocations in the method sequence ($rule.stmt$),  the statement that generates the return object ($rule.rtn$), the maximum distance that intermediate values must be consumed ($rule.vc$), and the maximum number of repetitive APIs invoked in the method sequence ($rule.rep$).  We describe the effect of each constraint element as below.

 \noindent{\textbf{1) The number of API calls. }}  Intuitively, the search space of the API sequence increases if \tool wants to synthesize more methods for the ``hole''.  Therefore, we prioritize the candidates with the fewer API invocations and increase the bound of API calls  until we reach the given bound from users or the preset bound for the number of API calls.  %Given that we incrementally insert one method into the sequence at a time, the synthesized sequences from \tool are guaranteed to have the minimum number of APIs that satisfy all test assertions.

 \noindent{\textbf{2) The statement that generates the return object. }} % \tool assumes that the return value should come from the output value of a statement inside the API sequence. That is, \tool will not return the 
 Based on the insight that method invocations appears  later in the execution could use parameters generated before and these methods are more likely to generate the return value for the API sequence, we prioritize the statements that are called later during the test execution and add a constraint that the selected statement must generate a value with the return type. Particularly, Figure~\ref{fig:background} illustrates this idea that  the return value \codefont{res3} of the API sequence  is the output of the last API calls in the sequence.

 \noindent{\textbf{3) Maximum distance that values must be consumed. }}  Similar to other API completion tools~\cite{isil:sypet17, jungloid:pldi05}, \tool assumes that all arguments and intermediate values generated from previous method invocations must be consumed in later API calls. With the insight that arguments and intermediate values should be consumed as quickly as possible, we set up a constraint that all values must be used within a given bound of statements. For instance, shown as Figure~\ref{fig:background}, based a constraint that all values must be consumed in the next two statements, the statement that initialize a new \codefont{Vector2D} object \codefont{res3} must consume the intermediate values  (\codefont{res1} and \codefont{res2}) generated from the previous two statements. To eliminate duplication, we ensure that there exists at least one value that is used at the maximum value-consumption distance. That is, if the maximum value-consumption distance is set as 2, at least one  value is used at the second next statement, otherwise all objects will be consumed at the next statement and these candidates has been explored with $rule.vc = 1$.

 \noindent{\textbf{4) Maximum number of repetitive APIs. }} With the notion that developers hardly use the same API for multiple times in a method sequence, we restrict the number of repetitive APIs in a method sequence, and relax this bound by allowing multiple repetitive APIs.

Our prioritization strategies is based on several heuristics for API completion, which might not always expedite the exploration for correct solutions. We conduct a comprehensive  evaluation for our pruning strategies in Section~\ref{sec:strategyEval}. 
%In addition to the previous prioritization strategies, we prune the APIs if any of their parameters' type are not available in the set of arguments and intermediate values.  \tool backtracks immediately  because some of their parameters cannot be initialized, therefore, these methods cannot generate a correct solution for the API sequence.

\subsection{Execution-Driven Sketching}\label{sec:backtrack}

\tool leverages a recent developed execution-driven sketching engine called \sj~\cite{sketch4j:spin17}  to handle the backtrack search based on the re-execution. 
Algorithm~\ref{alm:sketch} illustrates the execution-driven synthesis procedure.  \tool performs the synthesis by executing given test cases. When the test execution reaches a ``hole'' at the first time, \tool initializes this ``hole'' by generating API sequence candidates based on the runtime information and continues executing the program based on the selected candidate. If this candidate throws a runtime exception or fails in a test assertion (line~\ref{line:backtrack}), \tool throws a \codefont{BacktrackException} and breaks from the current execution. This \codefont{BacktrackException} is caught at line~\ref{line:nextChoice}. \tool then increments candidate identifiers, and fetches the next candidate in the candidate vector.

\input{example_generic}
\subsection{Advanced Java Feature Support}

  Many Java libraries use parametric polymorphism.  Instead of  modeling generic types based on static analysis like \spt, \tool handles generic types using reflection based on the runtime information. Figure~\ref{fig:generic} illustrates our ability to synthesize APIs using variables with generic types. Using APIs from the \codefont{Closure} library~\cite{closure}, this program sketch under synthesis contains an if-else condition, and specifies that the if-condition expression, the if-body, and the else-body are all incomplete method invocations. There exists a  local variable named \codefont{type}  with the generic type \codefont{T}, and the variable is given as an argument for the ``hole''. Without knowing the specific type of \codefont{T}, users can specify the argument type of the given generic variable as \codefont{Object.class} shown as line 3. 
  Note that we ask users to provide the argument type because if the given argument is evaluated to be \codefont{null} at runtime, \tool will not be able to generate any methods using reflection on a \codefont{null} object. We ask users to provide argument type as \codefont{Object.class} rather than \codefont{type.getClass()} as the variable \codefont{type} can be \codefont{null} and this invocation will lead to a \codefont{NullPointerException} at runtime.

   Moreover, if users are not clear about the return type of the API sequence, they can set the return type as \codefont{null}, and \tool will consider all types  as well as the \codefont{void} type as the API sequence's return type.

    We reuse the test suite from the \codefont{Closure} open source project to synthesize this program sketch and highlight one test case at   Figure~\ref{fig:generic} (B).  Figure~\ref{fig:generic} (C) shows a solution found by \tool that passes all test cases. We manually check this solution and find that it is identical to the original implementation in the open source project.

In summary, \tool synthesizes API sequences based on the test execution and applies a set of prioritization strategies to expedite the exploration of correct solutions.

### 2017-10-01 sketchAPI/paper/conclusion.tex
rename ase17

\section{Conclusion}\label{sec:conclude}

We present \tool, a novel test-execution-driven approach to synthesize API sequences. Our approach dynamically generates candidates for API sequences during the test execution and backtracks whenever the candidate encounters any test failures or runtime exceptions. Our key novelty is to introduce effective prioritization strategies to divide the search space of APIs to multiple sub-places with prioritized constraints. %\tool explores the actual program behavior with an execution-driven synthesis engine. 
We evaluate \tool on a collection of straight-line programming tasks and a benchmark of non-straight-line subjects derived from open source projects. Our evaluation results indicates that \tool compares generally well with a state-of-the-art API synthesizer and \tool can synthesize the desired program in a practical manner using a few test cases in a reasonable amount of time. We also illustrate that \tool can synthesize APIs in if-conditions and while-loops, which can hardly be handled by existing API synthesis tools.

### 2017-10-01 sketchAPI/paper/evaluation.tex
rename ase17

\section{Evaluation}\label{sec:eval} 
\input{table_line}

We evaluate \tool with two benchmarks that consist of straight-line and non-straight-line subjects. We address the following research questions in the evaluation:

\begin{itemize}
\item How well does \tool perform on synthesizing straight-line code snippets involving Java APIs compared to the state-of-the-art API synthesizer?
\item How do the  prioritization strategies affect the search space and performance of the synthesis?
\item How effective is \tool to synthesize program fragments from open source projects with if-conditions and while-loops?
\end{itemize}

All performance experiments are conducted on a MacBook Pro with 2.7 GHz Inter core i5 processor and 8GB memory running OS X version 10.12.4. %The maximum heap memory is set as 2 Gigabytes.

\subsection{Synthesizing Straight-Line API sequences}
To evaluate \tool, we first curate a benchmark of 47 synthesis tasks for straight-line API sequences, and compare \tool's synthesis efficacy with \spt~\cite{isil:sypet17}, a SAT-based API synthesizer with reachability analysis,  using the same benchmark.  Within these 47 subjects, 30 of them are used in the original evaluation of \spt, 8 are derived from open source projects used in \spt evaluation, and the rest involves small synthesis tasks like array sorting. The 30 synthesis tasks used in \spt evaluation are collected from 4 open source projects based on {\it StackOverflow} online forum and Github repositories, and the corresponding test cases are manually created in an incremental manner until \spt can find a correct solution with respect to the original implementation. For the 17 newly-added subjects, we follow a similar approach to create test cases. As we cannot replicate the experiments using the same machine, we execute \spt under our experiment setting (with smaller memory compared to their machine) and report the comparison result. Therefore, the result might be different from that reported in their original paper. To ease the comparison, we set up a time limit as 30 minutes for our experiments, the same as the default setting of \spt.

\noindent{\textbf{Evaluation Results. }}  Table~\ref{table:line} reports the 47 subjects with brief descriptions, the numbers of provided test cases for the synthesis (\textit{\#Tests}), and the number of synthesized  APIs in the first solution (\textit{\#API}).   Column {\it Space} shows the search space of API sequence candidates with respect to the identified solution.  If \tool collects a total of $m$ methods from input types using reflection, the average number of parameters for these methods is $ap$, and the number of given arguments is $v$,  we calculate the search space of API sequence candidates as $\sum_{1}^{N} (m \times v^{ap})^i$ while $N$ is the number of synthesized APIs  in the correct solution. We define the search space as is because each argument in a method candidate can have a maximum of $v$ options, and we incrementally insert more APIs into the sequence, searching for a desired solution.   Note that it is just an estimated search space because API candidates are dynamically generated based on previous APIs and constraints, and not all candidates in the search space will be executed.  Column   \textit{\#Run} shows the number of executed program candidates when \tool finds the first solution that passes all test cases.  Column \textit{Time} represents the total performance time including program compilation and test execution when \tool finds the first solution.

\tool successfully synthesizes 39 subjects with an average of 52 seconds. We manually investigate the tasks that \tool could not generate a solution within one hour, and find that these outliers usually have a relatively large distance for the intermediate value consumption, thus \tool de-prioritizes these candidates and times out after the preset time limit. For instance, shown as Figure~\ref{fig:outlier}  (A), the input argument \codefont{arg1} is not consumed until the $6^{th}$ statements, indicating that the maximum distance of the value consumption is 6. Therefore, \tool fails to prioritize the correct solution and identify it within the time limit.  Regarding the performance of the API synthesis,   out of 34 subjects that both tools could generate desired code, \tool outperforms \spt in 25 subjects. %indicating that \tool performs generally faster than the start-of-the-art.

\input{example_outlier}

On the other hand,  \spt finds desired API sequences for 42 subjects with an average of 49 seconds. Figure~\ref{fig:outlier}  (B)  presents a subject that \spt fails to identify a correct solution within the time limit whereas \tool detects the solution in 7 seconds. We are not aware of the root cause of this failure as the source code of \spt is not publicly available.  In addition,  \spt throws out of memory exception in 3 synthesis tasks, indicating that constructing a large reachability graph using SAT solver can consume a large memory.   \tool does not require reachability analysis and the memory \tool uses for API synthesis is linear with respect to the number of method invocations under sketching.

In summary, \tool compares generally well with the state-of-the-art API synthesizer to sketch straight-line API sequences.

\subsection{Efficacy of Prioritization Strategies}\label{sec:strategyEval}

To evaluate if our prioritization strategies can expedite the search of the desired API sequence, we report the number performance time and the number of executed programs with and without prioritization strategies when \tool finds the first solution that satisfies all test cases.  The last 4 columns of Table~\ref{table:line} lists these 4 numbers for all 47 synthesis tasks in our benchmark.

Within the 38 synthesis tasks that \tool can find desired solutions both with and without prioritization strategies, \tool with prioritization outperforms 23 tasks.    
  We further use the Spearman test to measure if the number of executed program candidates is significant different with and without prioritization strategies and the $p<0.01$ indicates that our prioritization strategies significantly reduce the number of executed candidates. We manually inspect the subjects in which prioritization strategies perform poorly and highlight one example in Figure~\ref{fig:outlier} (B).   In this example, the return object comes from the first statement and the desired sequence contains two repetitive APIs, which contradicts with two heuristics applied in the prioritization strategies.

The experiment results also indicate that even without pruning strategies, our test-execution-driven sketching could identify a desired API sequence by executing only a very small portion of the total search space (less than $0.001\%$).

\input{table_sub}

\subsection{Sketching Non-Straight-Line Code Fragments}~\label{sec:branch}

We further illustrate \tool's ability to synthesize APIs in if-conditions and while-loops that could hardly be  handled by existing API synthesizers.  
We select 10 non-straight-line code fragments from the implementation of 3 widely-used open source Java projects: \codefont{JFreeChart}~\cite{chart}, \codefont{Apache-Math}~\cite{math}, and \codefont{Closure} compiler~\cite{closure} for Javascript.  To distinguish from straight-line API synthesis, we select these subjects based on the criteria that  1) they should contain method invocations in both conditions and bodies of the conditions/loops; 2) at least one test case in the test suite should covered both the conditions and the bodies of the conditions/loops. The first rule ensure that \tool will synthesize APIs in the conditions,  and the second rule makes sure that there exist at least two holes in a single test execution and at least two holes will be sketched. 
Different from the straight-line benchmark whose test cases are hand-made by the authors of \spt or by us with the purpose of using libraries, the test suites for non-straight-line benchmark are directly from the open source projects with the purpose of validating these tools, which are usually written in JUnit test framework. %In particular, the test cases in the \codefont{Closure} project are organized in a non-conventional way using scripts rather than standard JUnit test cases. Our test-execution-driven synthesis approach does not have any requirement on the format of test cases and can be applied to any projects that can be executed.

We manually create program sketches  and introduce ``holes'' for API sequences based on the original implementation. We execute all test cases that reach the ``holes'' to synthesize program sketches using API calls and   validate generated solutions against the entire test suite. %Finally, we manually inspect if the solutions are semantically equivalent to  the original programs. 
%Given that the subjects we select contain ``holes'' in both conditions and bodies of the conditions/loops, \tool will encounter at least two ``holes'' in  a single test execution, which is different from existing API completion tools.  We have tries to extend existing API synthesizers with test partition for synthesizing non-straight-line programs, and more details will be described in the Section~\ref{sec:discuss}.

\noindent{\textbf{Evaluation Results. }}   Table~\ref{table:branch}  lists these 10 non-straight-line subjects, including basic information of the open source projects (lines of code {\emph Loc} and the number of test cases {\emph \#Tests}), a brief summary of each synthesis task (Column {\it Description}),  and the number of test cases that reaches the ``holes'' (Column  {\it \#Test}). Column {\it \#Cond} represents the number of invocations in conditions, while {\it 2if} indicates that \tool synthesizes a total of 2 method invocations in all if-condition expressions. It can be an API chain of two methods in an if-condition, 2 chained if-conditions, or nested if-conditions. Similarly, we use {\it 1wh} to represent  a while-condition with one API call. The column {\it \#Stmt} represents the total number of invocations synthesized in the body of the conditions/loops, yet these invocations may scattered in different branches.  %We have shown two  non-straight-line subjects in  Figure~\ref{fig:motivate} (No.3) and Figure~\ref{fig:generic}  (No.6). % {\it 2if, 1wh} represents that \tool synthesizes 2 method invocations in if-conditions and  one API call in while-condition.

On average, \tool explores 67.2k program candidates before it finds a sequence of method calls that satisfies all test assertions  in a reasonable amount of time that 70\% of synthesis tasks can be done in 1 minute. We also see that \tool does not require many test cases to synthesize an API sequence. Particularly, some tasks with multiple holes in both while-condition and while-body can be synthesized using a single JUnit test case such as the subject No.3 shown in Figure~\ref{fig:motivate}. %Note that  we directly use the JUnit test cases from open source projects to synthesize the ``holes'' in open source projects, and we only report the number of API invocations that have been reached and synthesized by \tool.  \tool generates an implementation that performs the desired functionality in a reasonable amount of time as Y seconds on average to complete a synthesis task with an average search space of M million program candidates.

In summary, \tool could successfully synthesize multiple API calls with branches and loops based on several test cases, while existing API synthesizers could only handle straight-line code. %We further investigate the efficacy of \tool to synthesize straight-line code in the next section.

\noindent{\bf Threats to Validity.}  We use  test cases as the
correctness criteria, which can generate plausible solutions that pass
all test cases but are not equivalent to some hypothetical correct
ones.  It can be incomplete to use test cases as correctness
specification.  When we evaluate non-straight-line subjects, we reuse
the original test cases provided by the open source projects, which
are not created with the purpose of code synthesis\Comment{. Although
  benefiting from the reuse of existing JUnit test cases, \tool may
  inadvertently generate plausible sketching results, i.e., passing
  all test cases but is incorrect from the perspective of users}. In
our experiments, we manually inspect the first generated solution for
each subject to validate its correctness. %We also list our evaluation dataset at~\cite{hua:eval} for  cross validation.

%\noindent{\textbf{External Validity.}}  
We only compare \tool with one state-of-the-art API synthesizer; thus,
our comparison result might not extend to other such tools, e.g.,
\textsc{CodeHint}~\cite{codehint:icse14} and
\textsc{InSynth}~\cite{insynth:cav11}.  We note that \spt has been
shown to be a state-of-the-art tool in comparison with both
\textsc{CodeHint} and \textsc{InSynth} using the same 30 subjects.  We
also include these 30 subjects in our comparison and \tool could
successfully synthesize most of them.

 % \tool only uses given arguments as parameters and does not support features such as field dereferences. We envision that we could extend \tool to support field dereferences and enum types with reflection. % and insert them into the candidate vector for parameters.

  \vspace{-2mm}
\section{Discussion}~\label{sec:discuss}
  \vspace{-2mm}
% Test Partion SyPet extension
%May not be correct solution
%\noindent{\bf Extending SyPet to handle non-straight-line code synthesis.}

   The use of Petri nets in SyPet is effective, although
limited to synthesis of straight-line code.  It is possible in
principle to enhance SyPet to handle a broader class of synthesis
problems, e.g., those that \tool handles.  To illustrate, consider
using SyPet to synthesize parts of an ``if-else'' statement.  \Comment{

With the notion that the problem of API synthesis with if-else branches can be divided into some subproblem of straight-line API synthesis, we extend \spt, trying to support  non-straight-line API synthesis with test partition. 
}
Intuitively, the synthesis problem can be divided into three
subproblems of sketching the if-condition, the if-body, and the
else-body. Given that a test case can only exclusively execute either
the if-block or the else-block, we try to partition the given test suite
and synthesize these two blocks and the if-condition based on two
subsets of test cases. We enumerate all combinations of given test
cases, searching for an adequate test partition such that \spt could
generate API sequences for both the if-body and the else-body based on
these two subsets correspondingly. If the test partition can
successfully generate two method sequences for the if-body and the
else-body, we further collect test oracles for the if-condition with
respect to the tests, and let \spt synthesize an API sequence that
could generate this test partition using the if-condition. Based on
this idea of dividing the non-straight-line synthesis task to multiple
straight-line synthesis problems, we consider an extension of \spt to
synthesize chained if-conditions by splitting the test suite into a
few subsets.

To illustrate this extension based on test partitioning, consider the
method in Figure~\ref{fig:partition} that tries to classify the
triangle based on its three edges. The method \codefont{classify}
takes the lengths of three edges as input and returns the triangle's
classification as either acute, right angled, or obtuse.
Figure~\ref{fig:partition} (A) presents a method skeleton of
non-straight-line program with chained if-conditions. This method
skeleton is regarded as the test driver for the extension of \spt.  We
also manually provide more than 20 test cases for this synthesis task
to sketch 3 bodies and 2 if-conditions. Figure~\ref{fig:partition} (C)
shows a solution from the extension of \spt based on the test
partition.

We learn several lessons from extending an existing straight-line API synthesizer to support non-straight-line code. First,  it can be rather expensive to find an adequate test partition  that satisfies constraints from both condition bodies and if-conditions. Given 20 test cases, the possible partitions can be as large as $3^{20}$. Even though \spt successfully finds a desired API sequence for a subset of test cases, it might fail to sketch a condition with method invocations that could separate the test suite to these subsets. Second, this idea assumes that the synthesized APIs for the if-condition cannot change the current program state, i.e, they must be pure methods. Otherwise the idea of test-partition may fail due to the side effect of the if-condition. Lastly, the test-partition-based non-straight-line code synthesis can fail in synthesizing while-loops.

While the simple idea of dividing the non-straight-line API synthesis
problem to several straight-line API synthesis sub-problems based on
test partitioning may not allow SyPet to effectively handle
non-straight-line synthesis problems, Petri nets could still provide
valuable guidance during search.  We believe future work on
integrating Petri nets with \tool holds promise in further optimizing
\tool.

\Comment{On the other hand, however, \tool does not require any test partition and can easily support  API synthesis with if-conditions and while-loops based on test-execution-driven sketching. }

\input{example_partition}

%\noindent{\textbf{Internal Validity.}}

%We believe that the reachability analysis used in \spt is complementary to ours and has the potential to further prune the search space of API sequences.  
%\noindent{\textbf{Construct Validity.}} 
%For our benchmark of straight-line subjects, the API completion tasks  are  defined 
%
% test cases are  not provided 
%
% \tool may generate a different solution that also satisfies all test cases compared to the synthesized API sequence generated by \spt. We regard solutions that pass all test cases are regarded as correct solution, we regard 
%In our performance comparison experiment, we manually transform the Java program to Sketch language, which may have inadvertently introduced behavioral differences. We list all subjects and tests at~\cite{hua:eval} for cross-validation.

### 2017-10-01 sketchAPI/paper/example_background.tex
rename ase17

\begin{figure}[htb]
\footnotesize
      \begin{minipage}{0.5\textwidth}
      \begin{tabular}{@{}p{0.9\textwidth}}
 \\ \hline
  \multicolumn{1}{c}{(A) A method that contains an API sequence under synthesis } \\ \hline
  \begin{Verbatim}[commandchars=\\\{\}, tabsize=2]
//Compute the ith  eigenvalue of a matrix
1.Vector2D eigenvalue(RealMatrix arg0, int arg1) \{
2. //Synthesize a sequence of APIs 
   //for desired functionality
3.\}
 \end{Verbatim}  
  \\ \hline
  \multicolumn{1}{c}{(B) A given test case that specifies desired behavior  } \\ \hline
  \begin{Verbatim}[commandchars=\\\{\}, tabsize=2]
1.public static boolean test0() throws Throwable \{
2. double[][] mat = new double[][]\{\{0,-20\},\{10,10\}\};
3. RealMatrix matrix = new Array2DRowRealMatrix(mat);
4. Vector2D result = eigenvalue(matrix, 0);
5. Vector2D target = new Vector2D(5, 5*Math.sqrt(7));
6. return Math.abs(result.getX()-target.getX())<1e-6 
 \&\& Math.abs(result.getY()-target.getY())<1e-6;
7.\}
 \end{Verbatim}  
  \\ \hline
  \multicolumn{1}{c}{(C) Input Sketch for \tool  Written by Users} \\ \hline
  \begin{Verbatim}[commandchars=\\\{\}, tabsize=2]
1.Vector2D eigenvalue(RealMatrix arg0, int arg1) \{
2. TedSketch.INVOKE(0) /* Hole ID*/
3. .addParameter(RealMatrix.class, arg0)
4. .addParameter(int.class, arg1)
5. .setReturnType(Vector2D.class)
6. .addPackage("org.apache.commons.math3.linear")
7. .invoke();
8.\}
 \end{Verbatim}
        \\ \hline
  \multicolumn{1}{c}{(D) Input Configuration JSON File for \spt Written by Users} \\ \hline
  \begin{Verbatim}[commandchars=\\\{\}, tabsize=2]
1. \{ 
2.  "methodName": "eigenvalue",
3.  "srcTypes": [	"RealMatrix", "int"],
4.  "paramNames": ["arg0", "arg1"],
5.  "tgtType": "Vector2D",
6.  "packages": ["org.apache.commons.math3.linear"],
7.  "testPath": "TestSource.java"
8.\}
 \end{Verbatim}
   \\ \hline
  \multicolumn{1}{c}{(E) A solution generated by \tool based on the test suite  } \\ \hline
  \begin{Verbatim}[commandchars=\\\{\}, tabsize=2]
1.TedSketch.INVOKE(0)
2. EigenDecomposition res0 = new 
    EigenDecomposition(arg0);
3. double res1 = res0.getImagEigenvalue(arg1);
4. double res2 = res0.getRealEigenvalue(arg1);
5. Vector2D res3 = new Vector2D(res2, res1);
6.return res3;
 \end{Verbatim}  
 \\  \hline
 \end{tabular}
  \end{minipage}
   \caption{An synthesis example of straight-line API sequence}
 \label{fig:background}
 \end{figure}

### 2017-10-01 sketchAPI/paper/example_partition.tex
rename ase17

\begin{figure}[t!]
\footnotesize
      \begin{minipage}{0.5\textwidth}
      \begin{tabular}{@{}p{0.9\textwidth}}

   \\ \hline
  \multicolumn{1}{c}{(A) A code skeleton under synthesis as the input of \spt} \\ \hline
  \begin{Verbatim}[commandchars=\\\{\}, tabsize=2]
1.String classify(int a, int b, int c) \{ 
2. if(condition1(a, b, c)) \{
3.  return body1();
4. \} else if(condition2(a, b, c)) \{ 
5.  return body2();
6. \} else \{
7.  return body3();
8. \} \}
 \end{Verbatim}
   \\ \hline
  \multicolumn{1}{c}{(B) Sample test cases that define correct behavior} \\ \hline
  \begin{Verbatim}[commandchars=\\\{\}, tabsize=2]
public static boolean test1() throws Throwable \{
 return classify(78, 79, 80).equals("acute");
\}
public static boolean test2() throws Throwable \{
 return classify(12, 13, 5).equals("right");
\}
public static boolean test3() throws Throwable \{
 return classify(10, 15, 10).equals("obtuse");    
\}
 \end{Verbatim}  
      \\ \hline
  \multicolumn{1}{c}{(B) A solution from extended \spt  } \\ \hline
  \begin{Verbatim}[commandchars=\\\{\}, tabsize=2]
1. body3(a,b,c): Library.obtuse(a,b,c);
2. body2(a,b,c): Library.right(a,b,c);
3. body1(a,b,c): Library.acute(a,b,c);
4. condition2(a,b,c): Library.isRight(a,b,c);
5. condition1(a,b,c): Library.isAcute(a,b,c);
 \end{Verbatim}
 \\  \hline
 \end{tabular}
  \end{minipage}
   \caption{Example of \spt extension to synthesize non-straight-line APIs   }
 \label{fig:partition}

 \end{figure}

### 2017-10-01 sketchAPI/paper/intro.tex
rename ase17

\section{Introduction}

Reuse of existing code from class libraries is often difficult because it involves using unfamiliar APIs, and the  numerous combination of APIs makes the synthesis of API sequences even harder. There has been much research on helping developers explore APIs by mining existing code~\cite{strathcona:icse05, portfolio:icse13, jungloid:pldi05} based on probabilistic models~\cite{slang:pldi14, codehint:icse14}.  Some of them take  natural-language queries~\cite{sniff:fase09, freeQuery:oopsla15}   and synthesize a suitable code fragment that satisfies the query.   A recent work~\cite{isil:sypet17} uses SAT solver for graph-reachability analysis and synthesizes APIs based on the given test suite. Although the effectiveness of these techniques have been impressed, these techniques follow a similar generate-and-validate approach that generates all program candidates and validate them based on the correctness property, such as  partial specification~\cite{codehint:icse14} or test cases~\cite{isil:sypet17, testDriven:pldi14}. The key limitation for these two-phase synthesis techniques is that, without runtime information, the generation phase may construct a number of candidates  that are not feasible for a specific test execution. For instance, they may generate multiple APIs whose receiver objects are evaluated to be \codefont{null} or unreachable code fragments within an if-condition while the condition expression is evaluated to be \codefont{false}.

%%More limitation for G&V and more benefit needed here
With the insight that an integration of generation and validation could help develop an effective approach for API synthesis, we present \tool, a new synthesis approach for complex APIs based on test-execution-driven sketching. 
As input, \tool takes a sketch (partial program) with holes for an API sequence, and a test suite that characterizes the expected behavior of this partial program. \tool supports API holes in  Java syntax for both conditions and statements. It executes the test suite against the sketch and backtracks  when it encounters a runtime exception or a test failure. \tool terminates when all API combinations have been explored or a solution has been found that satisfies the given test suite.

 When the test execution reaches a ``hole'', \tool dynamically constructs candidates based on the runtime information, selects a candidate, continues executing this candidate, and validate this candidate using test execution. Yet if the test execution does not reach a ``hole'', e.g., the ``hole'' inside a while-loop while the while-condition is evaluated to be \codefont{false}, \tool will not create any new search space. \tool leverages a recent developed execution-driven sketching engine  called \sj~\cite{sketch4j:spin17}  as backend to handle backtracking search via re-execution~\cite{verisoft:97}.

To initialize the search for API synthesis, \tool generates API candidates for the ``holes'' based on input types using reflection. These candidates are put in a candidate vector and \tool assigns a unique identifier for each candidate using its index in the candidate vector.  When \tool performs synthesis, it dynamically selects a candidate identifier for each ``hole'' using non-deterministic \codefont{choose()}  operator and executes the program based on the candidate it selects.

The key novelty of our work is to introduce effective prioritization strategies to divide the search space into multiple sub-spaces with more constraints. The constraints are defined based on Java semantics and some heuristics for API synthesis. For instance, based on Java semantics,  if there does not exist any arguments or intermediate values with the same type of a parameter in the method, this method invocation is ignored as one of its parameters cannot be initialized. Moreover,  we introduce the notion of locality that arguments should be consumed as quickly as possible and the objects generated later in the sequence could use more information generated previously and thus are more likely to be used as return value. Leveraging the test-execution-driven sketching, \tool supports API synthesis for non-straight-line code fragments that have if-branches and while-loops.

%Given that prior works complete API sequence based on the requirement that synthesized methods should use all of its inputs and any intermediate values should be produced~\cite{jungloid:pldi05, codehint:icse14, isil:sypet17}, \tool introduces several simple pruning strategies to optimize the API completion.  For a sequence of APIs, \tool prunes semantic-equivalent API sequences based on simple program isomorphic analysis and  prunes API calls with  non-consumed intermediate values based on the pre-defined assumption.

%When \tool reaches a hole as the condition expression, it dynamically selects a method call that returns a \codefont{boolean} value, continues executing the program based on this selection, and backtracks if it encounters a runtime exception or test failures.

To evaluate \tool, we first performed experiments to investigate its efficacy of synthesizing straight-line APIs compared to \spt, a state-of-the-art API synthesis tool based on SAT solver and advanced reachability analysis. We then investigate if our prioritization strategies could effectively expedite  the exploration of correct solutions. Lastly, we demonstrate how \tool handle APIs with if-else-branches and while-loops.  Existing works  do not directly support API synthesis with branches. We extend \spt to handle non-straight-line code synthesis and discuss the lessons we learn with this extension.

 The experimental results show that \tool's synthesis efficacy compares well with \spt. In particular, out of 47 synthesis tasks, \tool completes 39 subjects in an average of 52 seconds, which is very close to the synthesis efficacy of \spt, 42 subjects in an average of 49 seconds.  Our experiments also  illustrate that our prioritization strategies effectively reduce the performance time in 61\% of subjects. Moreover, \tool completes 10 sketching tasks with if-condition and while-loops from open source projects in a reasonable amount of time. 70\% of these non-straight-line synthesis tasks are completed in one minute with 5 methods sketched on average.

 This paper makes the following contributions:

 \begin{itemize}
 \item \textbf{Test-execution-driven synthesis of API calls.}  We
   present a novel approach for synthesizing API calls based on
   test-execution-driven sketching. Given a partial program and a few
   test cases, \tool completes the partial program with API calls to
   conform to the expected behavior represented by the given test
   cases.
 \item \textbf{Pruning Strategies.  }  To enhance the efficacy of our
   approach, we introduce pruning strategies that reduce the search
   space of candidates based on the semantics of Java.  The
   experimental results show that our pruning strategies can
   significantly reduce the search space of API call synthesis.
 \item \textbf{API call synthesis with conditional branching and
   loops.  }  Our approach supports sketches that have conditional
   branches and while loops, and completes holes for conditions and
   statements using sequences of API calls.  \Comment{-driven
     sketching, \tool can successfully complete API call ``holes'' for
     conditions and statements.  To compare non-straight-line API
     synthesis with existing API completion tools, we extend \spt with
     test partition and demonstrate that \tool is more effective in
     synthesizing non-straight-line APIs than the extension of \spt.}
 \item \textbf{Experimental Evaluation.  }  We experimentally evaluate
   \tool and compare it with \spt, a recently developed
   state-of-the-art technique designed for synthesis of straight-line
   code. The results show that our approach can effectively handle
   non-trivial sketches with non-strainght-line code, and compares
   favorably with \spt for straight-line code.
  \end{itemize}

\Comment{
The rest of the paper is organized as followed: Section~\ref{sec:motivate} presents a motivating example to illustrate our  approach. Section~\ref{sec:approach} describes how we perform execution-driven sketching for API calls and how we prune the search space for efficient search, followed by the evaluation in Section~\ref{sec:eval}. We discuss related work in Section~\ref{sec:related} and conclude at Section~\ref{sec:conclude}.
}

### 2017-10-01 sketchAPI/paper/main.tex
rename ase17

\documentclass[10pt,conference]{IEEEtran}

\input{macros}

\begin{document}

\title{Test-Execution-Driven Sketching for Complex APIs}

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
%\author{\IEEEauthorblockN{,  Sarfraz Khurshid}
%\IEEEauthorblockA{The University of Texas at Austin\\
%Email: \{, khurshid\}@utexas.edu}}

% make the title area
\maketitle

\begin{abstract}

  We introduce the \tool framework for synthesizing code fragments
  with respect to test cases that specify expected program behavior.
  Given a skeletal implementation, aka a \emph{sketch}, that has
  \emph{holes}, i.e., placeholders for desired fragments, and a test
  suite as inputs, \tool outputs sequences of Java APIs that
  complete the holes such that all tests pass.  \tool is based on a
  \emph{test-execution-driven} approach that effectively explores
  potentially very large spaces of candidate programs.  \tool executes
  each given test and uses the test executions to guide the
  exploration and prune large parts of the space.  Our focus is
  synthesis of method call sequences over given libraries.  Our
  approach handles sketches with non-straight-line code, e.g.,
  while-loops and if-else statements.  We embody our approach in a prototype tool, and perform an
  experimental evaluation using a number of sketching tasks for
  complex APIs.  We also compare \tool with \spt, which is a recently
  developed state-of-the-art tool using Petri nets and SAT
  solving, but is designed to only synthesize straight-line code.  The
  experimental results show that \tool can efficiently complete
  non-trivial sketches with non-straight-line code, and can sometimes
  even outperform \spt for subjects with straight-line code.

  \Comment{
To achieve a task of interest, developers always need to combine complex APIs together. Most tools that help programmers find code fragments follow a generate-and-validate style that first generate search space based on pre-defined or mined templates and validate these candidates against  correctness properties.

To help programmers use APIs more easily, we present \tool,  a novel approach that dynamically generates program candidates for API sequences during the test execution and backtracks whenever the candidate encounters any test failures or runtime exceptions. We introduce effective pruning strategies to explore the actual program behavior with an execution-driven synthesis engine. Taken a partial program and a given test suite as the specification,  \tool completes the partial program with API sequences that satisfy all test cases. We further illustrate that based on execution-driven sketching, \tool could synthesize non-straight-line APIs with if-branches and while-loops.   Experimental results show that \tool compares well with another SAT-based API completion tool, SyPet, and moreover,  \tool could synthesize API sequences with if-branches and while-loops efficiently. 
}

\end{abstract}

% no keywords
\input{intro}
\input{motivate}
\input{approach}
\input{evaluation}
\input{related}
\input{conclusion}
%\IEEEpeerreviewmaketitle

% use section* for acknowledgment
%\section{Acknowledgment}

\bibliographystyle{IEEEtran}
\bibliography{synthesis,other}

% that's all folks
\end{document}

### 2017-10-01 sketchAPI/paper/motivate.tex
rename ase17

\section{Motivating Examples}\label{sec:motivate}
\input{example_background}
\input{example_motivate}
In this section, we define the problem of API synthesis and illustrate our approach using two examples of straight-line and non-straight-line code. Both examples use APIs from the \codefont{Apache-Math} library~\cite{math}.

\subsection{Problem Definition}

API synthesis is an approach that generates a sequence of method invocations to perform a desired functionality based on the given input types, arguments, and the output type of the API sequence. For \tool, the desired behavior is defined as the satisfaction of all test cases. That is,  the correctness of the sketched solution from \tool is with respect to the given test suite. We present a usage scenario of API synthesis in Figure~\ref{fig:background} (A) that tries to create an API sequence to compute the $i^{th}$  eigenvalue of a matrix. Several test cases are provided as correctness criteria and we highlight one of them in Figure~\ref{fig:background} (B).

To use \tool for API synthesis, users provide input arguments used in the method sequence, source types or libraries that specify the scope of the API exploration, and the output type of the API sequence, shown as Figure~\ref{fig:background} (C). 
To further illustrate the input arguments of existing API synthesis techniques, we show an input configuration file  for a state-of-the-art API synthesizer called \spt. Shown as Figure~\ref{fig:background} (D), \spt asks for similar information to identify correct sequences of method calls. Note that \spt is known as the state-of-the-art method synthesizer that compares favorably with other synthesis tools~\cite{codehint:icse14, insynth:cav11}.

API synthesis tools return a desired method sequence with respect to the test suite.  Figure~\ref{fig:background} (D) presents a synthesized method sequence from \tool that pass all test cases. This solution is semantically identical to the result from \spt using the same test suite.

\subsection{Non-Straight-Line Synthesis Example }

We further illustrate \tool's ability to  sketch API calls in non-straight-line code such as conditions and loops.

%Figure~\ref{fig:motivate} (A) presents a code 
%\codefont{ebeDivide} method derived from the \codefont{OpenMapRealVector} class in the Apache-Math project. This \codefont{ebeDivide} method performs an element-by-element division for each element in the vector. Assume that users want to implement this method, and they want to implement this method using  three local variables \codefont{v}, \codefont{res}, and \codefont{iter}, and a \codefont{while} loop to traverse the vector. The users leave the condition of the \codefont{while} loop and its body to be synthesized by \tool.

Figure~\ref{fig:motivate} (A)  shows a code skeleton (sketch) written by users. In this sketch, users specify the \codefont{while} condition (line 5) and the body of the \codefont{while} loop (line 6)  as ``holes'' that need to be synthesized. %Similar to other API completion tools~\cite{codehint:icse14, isil:sypet17}, users provide the input parameters and output type of the expected API sequence, and let API synthesis tool complete the method calls. 
Different from other API synthesis tools  that could only synthesize a single straight-line method sequence, \tool enables users to specify multiple holes in non-straight-line programs with if-conditions and while-loops. Using a suite of JUnit test cases, \tool tries to complete these holes via test execution. A JUnit test case is highlighted in Figure~\ref{fig:motivate} (B).

%Using 3 visible variables in this example, there are 59 visible methods that can be chosen for the a single API invocation.  Even if we only consider candidates with up to 4 statements for the \codefont{while} loop body and 1 statement for the \codefont{while} loop condition, the space of possible complete programs can be as large as 12.1 millions.

%We use the existing test suite from the \codefont{Apache-Math} project as the correctness criteria for the partial program, and set up a time out as 30 seconds to eliminate infinite loop. \codefont{Apache-Math} project  contains 3.6k JUnit test cases yet only one test case reaches the holes of this sketch.  For more efficient synthesis, we pick this test case to synthesize the partial program and validate the solution against the entire test suite.

\tool dynamically selects method candidates for the sketch when it executes given test cases.  When \tool first reaches the \codefont{while} condition hole (line 5), it generates all API candidates based on the given input types using reflection and non-deterministically selects a candidate  with respect to the given output type \codefont{boolean}. If the selected candidate returns \codefont{false} for the \codefont{while} loop condition, the ``hole'' inside the while loop will not be executed thus no new search space will be initialized. When \tool first reaches the ``hole'' inside the while-loop at line 6, it  selects a method invocation in a non-deterministically manner and incrementally adds more APIs to the sequence until it finds the first solution that satisfies all test cases. Users may specify the number of statements in the synthesized sequence; by default, we set the bound of the API calls as 4 and make it configurable.  \tool backtracks its search if the current method sequence encounters a runtime error or a test failure, and selects the next candidate for a new execution.

A naive search may explore a huge amount of program candidates. Considering hundreds of methods and multiple options for receiver objects and parameters of these methods, the search space for this problem can be as large as 9.4 billion.  \tool introduces effective prioritization strategies to divide the search space of API generation to multiple smaller spaces based on some heuristics such as the values generated later in the sequence are more likely to be used as the return object.

%prunes a number of such candidates based on the output type and a similar assumption with other API completion tools that all intermediate values should be consumed. \tool also prioritizes candidates based on a set of heuristics such as variable locality, etc.

Figure~\ref{fig:motivate} (C) presents a solution generated by \tool with one method invocation for the \codefont{while} condition and 4 statements for the  body of the while-loop. This  solution is semantically identical to the original implementation in the library based on manual inspection, In this example, \tool finds the corrrect solution in 50 seconds (including compilation and test execution time) after exploring 7.8k candidates.

### 2017-10-01 sketchAPI/paper/related.tex
rename ase17

\section{Related Work}\label{sec:related}

\tool is related to a number of works on API completion and program synthesis.

\noindent{\textbf{API completion.}}   \textsc{Prospector}~\cite{jungloid:pldi05} is one of the first works that introduces the notion of synthesizing   ``jungloid code snippets''. A \textit{jungloid} is a composition of single-argument methods with a single return type.  \textsc{Prospector} synthesizes method sequence based on the  \textit{jungloids} mined from existing code corpus. Similar to  \textsc{Prospector},  \textsc{CodeHint}~\cite{codehint:icse14} leverages empirical statistic models to prioritize runtime recommendation for the API completion. It allows users to set up breakpoints in Eclipse IDE, and rollbacks to the previous state whenever the select candidate encounters a runtime exception or test failure. In contrast to the tools with expensive state restoration, \tool simply backtracks till the beginning of the program and re-executes the next candidate.

\spt~\cite{isil:sypet17} further extends  \textsc{Prospector} by introducing Petri-net for reachability analysis based on SAT solvers. We believe their reachability analysis is complementary to ours, yet in this paper, we show that using a relatively simple test-execution-driven approach for API synthesis, \tool compares generally well with \spt and further supports non-straight-line code synthesis in real-world projects.

A line of other tools~\cite{mineAPI:msr13, tienAPI:icse14, portfolio:icse13, parseWeb:tao07} mine API usage pattern from the code repositories and  use empirical probabilistic models to guide the search towards methods that are more often used in practice. In particular,  \textsc{Slang}~\cite{slang:pldi14} predicts probabilities of API calls using statistical models based on machine learning,  while Strathcona~\cite{strathcona:icse05} assists developers in finding relevant API invocations from similar program contexts. Different from these techniques that train offline data corpus for API completion, \tool leverages runtime information for search space prioritization. We envision that  empirical statistical models can be helpful to our method sequence prioritization.

\noindent{\textbf{Program Synthesis.}}  Program synthesis has  achieved many success on synthesizing code in small well-defined domains such as bit-vector logic~\cite{oracle:icse10} and data structures~\cite{storyboard:fse11, demsky:issta06} based on test cases~\cite{testDriven:pldi14} or specifications~\cite{Kuncak:pldi10, cegis:13}. These tools transform partial programs~\cite{sketch:sttt13}, input-output examples~\cite{isil:pldi15, singh:pldi13}, or oracles~\cite{oracle:icse10, loop:pldi11} to decision procedures and SMT solvers, and have shown as very efficient in certain domains that have been fully modeled~\cite{insynth:cav11, verifySys:popl10}.  Other synthesis tools try to generate small code snippets.  Perelman et al.\/~\cite{typed:pldi12} infer partial expressions using type-directed completion and   \textsc{InSynth}~\cite{insynth:cav11}  handles high-order functions and polymorphism using theorem proving.  Yet both are confined to single-statement-generation rather than the method sequence.    Recent works leverages natural language queries~\cite{freeQuery:oopsla15, sniff:fase09, sumit:icse16} to infer expressions and simple method invocations, whereas \tool could synthesize code in a much large scope: multiple method invocations in if-conditions and while-loops using real-world Java libraries.

Our idea of asking users to provide a program skeleton with non-deterministic expressions has the same spirit of sketch-based synthesis~\cite{sketch:aplas09}.  The Sketch system~\cite{sketch:sttt13} asks programmers to write a program sketch containing ``holes'', and uses counter-example-guided inductive synthesis to complete the holes.  \textsc{Jsketch} brings the sketch-based synthesis to Java~\cite{jsketch:fse15}. Given a partial Java program written in the sketch syntax, \textsc{Jsketch} translates the Java program to SAT-based sketch synthesizer and transfers the synthesizer result back to executable Java code. Whereas it support a limited number of libraries.  Our synthesis approach based on  test-execution-driven is also similar to other test-driven synthesis techniques~\cite{verifySys:popl10, testDriven:pldi14}, yet we focus on a more complex scenario of synthesizing Java method invocations with if-conditions and while loops in open source projects.

### 2017-10-01 sketchAPI/paper/table_line.tex
rename ase17

\begin{table*}[!htb]
\footnotesize
\begin{center}
\caption{ Straight-Line Subjects}
\label{table:line}
\begin{tabular}{@{}c|l|r|rr|rr|rr|rrrrrrrrrrrr@{}}

\multirow{3}{*}{ID}&	\multirow{3}{*}{Description}&\multirow{3}{*}{\#Tests}&\multicolumn{2}{c|}{\spt}&\multicolumn{6}{c}{\tool} \\
&&&\multirow{2}{*}{\#API}& \multirow{2}{*}{Space} &\multirow{2}{*}{\#API}&\multirow{2}{*}{Space}&\multicolumn{2}{c|}{With Ranking}&\multicolumn{2}{c}{Without Ranking}\\ 
&&&&&& &Time(s)&\#Run&Time(s)&\#Run\\ \midrule
1&Compute the pseudo-inverse of a matrix&1&3&41&3&1.7b&6&1.8k&12&5.3k\\
2&Compute the inner product between two vectors&1&3&24&2&258.6m&2&124&3&134\\
3&Determine the roots of a polynomial equation&1&3&35&3&23.1t&109&9.0k&380&69.3k\\
4&Compute the singular value decomposition of a matrix&1&3&24&3&45.5b&3&286&8&993\\
5&Invert a square matrix&1&3&28&2&12.7m&2&135&3&217\\
6&Solve a system of linear equations&1&6&115&-& $10^{22}$&-&146.7k&-&959.7k\\
7&Compute the outer product between two vectors&1&4&37&2&258.6m&2&117&3&127\\
8&Predict a value from a sample by linear regression&2&3&244&3&18.1b&517&3.7k&4&3.8k\\
9&Compute the ith eigenvalue of a matrix&2&-&$\perp$&4&$10^{15}$&62&211.2k&339&850.3k\\
10&Scale a rectangle by a given ratio&1&4&36&3&502.0b&314&32.0m&710&18.3m\\
11&Shear a rectangle and get its bounds&1&4&36&3&502.0b&308&31.9m&133&13.1m\\
12&Rotate a rectangle about the origin by quadrants&1&4&17&3&32.2b&2&907&3&2.6k\\
13&Rotate 2-D shape by the specified angle about a point&2&4&33&-&$10^{15}$&-&19.7m&-&18.2m\\
14&Perform a translation on a rectangle&1&4&26&3&502.0b&308&32.2m&-&55.0m\\
15&Intersect a rectangle and an ellipse&1&3&11&2&10.1m&2&40&1&3\\
16&Compute number of days since a date&2&3&22&3&45.8b&37&80.8k&70&111.6k\\
17&Subtract two dates considering timezone&3&4&408&3&2.3t&56&150.4k&122&214.2k\\
18&Determine if a year is a leap year&3&4&68&3&45.8b&24&102.3k&3&1.2k\\
19&Return the day of a date string&2&3&11&3&2.5t&42&252.9k&43&57.7k\\
20&Find the number of days of a month in a date string&2&4&83&-& $10^{16}$&-&38.1m&-&5.6m\\
21&Find the day of the week of a date string&2&4&44&-& $10^{16}$&-&19.4m&-&5.4m\\
22&Compute age given date of birth&2&3&30&3&45.8b&63&158.6k&86&174.1k\\
23&Compute the offset for a specified line in a document&1&3&19&3&1.7t&5&1.2k&11&4.0k\\
24&Get a paragraph element given its offset in the a document&1&3&24&3&1.7t&4&1k&11&3.8k\\
25&Obtain the title of a webpage specified by a URL&1&3&110&3&1.1b&35&10.7k&35&19.2k\\
26&Return doctype of XML document generated by string&1&6&21&-& $10^{19}$&-&5.4m&-&5.6m\\
27&Generate an XML element from a string&1&6&24&-& $10^{19}$&-&3.8m&-&4.8m\\
28&Read XML document from a file&1&3&14&3&5.5b&4&3.9k&5&2.8k\\
29&Generate an XML from file and query it using XPath&1&6&78&-& $10^{26}$&-&3.2m&-&3.3m\\
30&Get the value of root attribute from a XML file&1&5&17&-&$10^{18}$&-&13.0m&-&13.8m\\ \midrule
31&Check if a point is inside a rectangle&8&5&66&1&3.1k&0.5&1&0.4&1\\
32&Check if a line segment intersects a rectangle.&8&-&$\perp$&2&63.1m&1&224&2&265\\
33&Compute number of minutes between two time&8&-&$\perp$&2&175.5m&1&183&1&350\\
34&Get number of seconds since the midnight of sometime&8&2&15&1&3.5k&1&2&0.7&2\\
35&Compute the transpose of a matrix&8&3&12&3&1.7b&1&88&1&401\\
36&Compute the sum of two matrices&8&4&14&4&911.1t&99&3.8k&1.4k&56.5k\\
37&Compute exclusive or between an area and a rectangle&2&-&-&2&10.1m&3&135&3&136\\
38&Create an element with given name&3&4&18&4&3.3t&5&6.5k&1&779\\ \midrule
39&Calculate absolute value of an integer&8&1&15&1&2.4k&0.5&5&0.1&10\\
40&Increment an integer and return its old value&8&4&5&3&1.9k&0.4&60&0.9&28\\
41&Increment an integer by 2 and return its old value&8&-&-&5&271.5k&7&115.9k&0.5&110\\
42&Get the class name of an object&8&2&30&2&5.9m&0.5&25&0.6&28\\
43&Get the first value of an integer array&8&2&4&2&210&1&14&0.8&8\\
44&Calculate minimum value between two integers&8&1&14&1&7.1k&0.5&49&0.5&49\\
45&Calculate minimum value between three integers&8&2&25&2&179.8m&1.1&3.8k&1&4.3k\\
46&Given an array set the last entry the value of first entry&8&4&154&5&579.2k&1&3.1k&2&16.4k\\
47&Sort an integer array&8&1&14&1&7.6k&0.8&1&1&1\\

  \end{tabular}

  \vspace{1mm}
 $\perp$ represents out of memory. - represents time out after 30 minutes. The first 30 subjects are from the evaluation benchmark of \spt, 31-38 are 8 subjects derived from the open source projects used in \spt evaluation, and the rest are small synthesis tasks such as absolute value calculation.
\end{center}
\end{table*}

### 2017-10-01 sketchAPI/paper/table_sub.tex
rename ase17

\begin{table*}
\footnotesize
\begin{center}
\caption{ Non-Straight-Line Subjects}
\label{table:branch}
\begin{tabular}{@{}c|c|l|rrrrrrrr@{}}
Project&ID&Description&\#Cond 	&\#Stmt&Space&\#Tests&\#Run&Time(s)\\ \midrule
Chart&1&\codefont{createAndAddEntity()}:  Created an entity for the axis&3if&6&5.5$\times10^{21}$&1&279&9\\
90k; 2.2k&2&\codefont{addBaseTimelineException()}:  Adds a segment &1wh&1&2.4k&2&2&11\\ \midrule
Math&3&\codefont{ebeDivide()}:  Element-by-element division in a vector&1wh&4&9.4b&1&7.8k&50\\
Loc: 85k&4&\codefont{add()}: Optimized method to add two RealVectors&2if, 1wh&6&8.4$\times10^{19}$&1&170.5k&51\\
\#Tests: 3.6k&5&\codefont{setEntry()}: Set entry in specified row and column&3if&2&9.3$\times10^{14}$&1&529&33\\  \midrule
&6&\codefont{visit()}:   sets properties as ineligible&1if&2&9k&57&1&3\\
Closure&7&\codefont{applyCollapses()}:  Collapse  variable declarations &1if, 1wh&2&12.5b&6&125.0k&220\\
Loc: 90k&8&\codefont{remove()}: Remove this node&1if&3&1.4$\times10^{11}$&10&172.4k&333\\
\#Tests: 7.8k&9&\codefont{flattenReferences()}:  Flattens to collapsible properties&2if&2&7.0m&23&9&6\\
&10&\codefont{removeVar()}:  remove var if it has been coalesced&3if&3&1.8$\times10^{14}$&28&195.1k&2.3k\\
  \end{tabular}
  \vspace{1mm}

  *if represents the total number of synthesized APIs in if-conditions, and *wh represents the total number of generated methods in while loops.
\end{center}
\end{table*}
